### 2016-05-19 ms.tex
Add files via upload

\documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{yfonts}

\usepackage{epsfig}  \usepackage{graphicx}   \usepackage{rotating}

%------- New commands

\newcommand{\lsim}{\lower0.6ex\vbox{\hbox{$ \buildrel{\textstyle <}\over{\sim}\ $}}}
\newcommand{\gsim}{\lower0.6ex\vbox{\hbox{$ \buildrel{\textstyle >}\over{\sim}\ $}}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

%------ Journals

\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}
\newcommand{\apjl}{Astrophys. J. Lett.}
\newcommand{\aj}{Astron. J.}
\newcommand{\aap}{Astron. Astrophys.}
\newcommand{\araa}{Ann. Rev. Astron. Astroph.}
\newcommand{\apjs}{Astrophys. J. Suppl. Ser.}
\newcommand{\physrep}{Phys. Rep.}
\newcommand{\jcap}{JCAP}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\apj}{ApJ}

\newcommand{\wprp}{w_{\mathrm{p}}}
\newcommand{\rp}{r_{\mathrm{p}}}

\bibliographystyle{mn2e}

%Title of paper---------------------------------------------------------

\title[Clustering Constraints on Assembly Bias]
{
Constraints on Assembly Bias from Galaxy Clustering
}

% Authors ------------------------------------------------------

\author[Zentner et al.]
{Andrew R. Zentner$^{1}$, Andrew P. Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
Antonio Villareal$^{1}$, Johannes Lange$^{3}$, Prince R. Nelson$^{4}$, Probably some others of unspecified origin\\ \\
$^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
$^2$Yale Center for Astronomy \& Astrophysics, Yale University, New Haven, CT\\
$^3$Department of Astronomy, Yale University, P.O. Box 208101, New Haven, CT\\
$^4$Paisley Park, Chanhassen, MN\\
}

\date{Today}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{}

\newtheorem{theorem}{Theorem}[section]

\begin{document}

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

We fit SDSS DR7 data with models that include assembly bias.

\end{abstract}

%---------------------------
\section{Introduction}
\label{section:introduction}
%---------------------------

%---------------------------
\section{Methods}
\label{section:methods}
%---------------------------

%---------------------------
\section{Results}
\label{section:results}
%---------------------------

We have performed parameter inference analyses in order to infer the underlying HOD of 
galaxies from the projected galaxy two-point function $\wprp(\rp)$ as described in the preceding 
section. In this section, we describe the primary results of these analyses. Our marginalized 
one-dimensional parameter constraints are given in Table~\ref{table:parameters}.

%-------------------------
\subsection{Standard Analysis}
\label{subsection:standard}
%-------------------------

Prior to discussing our results using models that include assembly bias, we present 
results of standard HOD analyses that include no model for assembly bias.

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{table*}
{\renewcommand{\arraystretch}{1.3}
\renewcommand{\tabcolsep}{0.2cm}
\begin{tabular}{l l c c c c c c c}
\hline 
\hline
Sample $M_r$ &  Authors & $\log (M_{\rm min})$ & $\sigma_{\log M}$ & $ \log (M_1)$ & $\alpha$ & $A_{\rm cen}$ & $A_{\rm sat}$ & $\chi^2/\mathrm{DoF}$\\ 
\hline
$-21$ & Zehavi+11 & $12.78 \pm 0.10$ & $0.68 \pm 0.15$ & $13.80 \pm 0.03$ & $1.15 \pm 0.06$ & $--$ & $--$ & 3.1\\
$-21$ & Zentner+16 & $12.92^{+0.07}_{-0.11}$ & $0.74^{+0.09}_{-0.16}$ & $13.93^{+0.04}_{-0.05}$ & $1.23^{+0.10}_{-0.12}$ & $--$ & $--$ & 1.59\\
$-21$ & Zentner+16 & $12.83^{+0.11}_{-0.09}$ & $0.60^{+0.15}_{-0.17}$ & $13.93^{+0.05}_{-0.08}$ & $1.16^{+0.12}_{-0.14}$ & $0.29^{+0.44}_{-0.35}$ & $0.08^{+0.49}_{-0.36}$ & 1.34 \vspace*{5pt}\\
%
$-20.5$ & Zehavi+11 & $12.14 \pm 0.03$ & $0.17 \pm 0.15$ & $13.44 \pm 0.03$ & $1.15 \pm 0.03$ & $--$ & $--$ & 2.7\\
$-20.5$ & Zentner+16 & $12.25^{+0.07}_{-0.03}$ & $0.23^{+0.17}_{-0.15}$ & $13.59^{+0.02}_{-0.02}$ & $1.20^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.90\\
$-20.5$ & Zentner+16 & $12.30^{+0.11}_{-0.07}$ & $0.42^{+0.20}_{-0.26}$ & $13.59^{+0.04}_{-0.04}$ & $1.15^{+0.05}_{-0.06}$ & $>0.0 (90\%)$ & $0.23^{+0.39}_{-0.31}$ & 1.71 \vspace*{5pt}\\
%
$-20$ & Zehavi+11 & $11.83 \pm 0.03$ & $0.25 \pm 0.11$ & $13.08 \pm 0.03$ & $1.00 \pm 0.05$ & $--$ & $--$ & 2.1\\
$-20$ & Zentner+16 & $11.95^{+0.11}_{-0.6}$ & $0.37^{+0.23}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.19\\
$-20$ & Zentner+16 & $12.23^{+0.33}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.20^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.28 (99\%) $ & $0.01^{+0.32}_{-0.26}$ & 1.16 \vspace*{5pt}\\
%$-20^d$ & Zentner+16 & $11.91^{+0.10}_{-0.03}$ & $0.26^{+0.25}_{-0.17}$ & $13.34^{+0.04}_{-0.05}$ & $1.25^{+0.05}_{-0.06}$ & $--$ & $--$ & 0.70 \\
%$-20^d$ & Zentner+16 & $12.00^{+0.29}_{-0.12}$ & $0.51^{+0.42}_{-0.32}$ & $13.31^{+0.06}_{-0.09}$ & $1.17^{+0.08}_{-0.09}$ & $0.76^{+0.18}_{-0.43}$ & $0.11^{+0.37}_{-0.34}$ & 0.30\vspace*{3pt}\\
$-19.5$ & Zehavi+11 & $11.57 \pm 0.04$ & $0.17 \pm 0.13$ & $12.87 \pm 0.03$ & $0.99 \pm 0.04$ & $--$ & $--$ & 1.00 \\
$-19.5$ & Zentner+16 & $11.76^{+0.33}_{-0.11}$ & $0.51^{+0.51}_{-0.29}$ & $13.05^{+0.04}_{-0.08}$ & $1.12^{+0.04}_{-0.07}$ & $--$ & $--$ & 1.24\\
$-19.5$ & Zentner+16 & $11.70^{+0.23}_{-0.08}$ & $0.42^{+0.42}_{-0.26}$ & $13.04^{+0.08}_{-0.13}$ & $1.07^{+0.07}_{-0.10}$ & $>-0.05 (84\%)$ & $>-0.14 (84\%)$ & 0.83 \vspace*{5pt}\\
%
$-19$ & Zehavi+11 & $11.45 \pm 0.04$ & $0.19 \pm 0.13$ & $12.64 \pm 0.04$ & $1.02 \pm 0.02$ & $--$ & $--$ & 1.8 \\
$-19$ & Zentner+16 & $11.72^{+0.33}_{-0.19}$ & $0.69^{+0.52}_{-0.46}$ & $12.78^{+0.04}_{-0.04}$ & $1.03^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.77\\
$-19$ & Zentner+16 & $11.62^{+0.33}_{-0.13}$ & $0.53^{+0.57}_{-0.35}$ & $12.83^{+0.06}_{-0.07}$ & $1.02^{+0.04}_{-0.04}$ & $0.35^{+0.45}_{-0.66}$ & $>0.02 (84\%)$ & 2.01\\
%$-19^d$ & Zentner+16 & $11.87^{+0.17}_{-0.27}$ & $1.10^{+0.30}_{-0.52}$ & $12.84^{+0.17}_{-0.23}$ & $1.11^{+0.15}_{-0.15}$ & $--$ & $--$ & 2.30 \\
%$-19^d$ & Zentner+16 & $11.75^{+0.24}_{-0.27}$ & $0.94^{+0.41}_{-0.55}$ & $12.99^{+0.14}_{-0.18}$ & $1.17^{+0.14}_{-0.14}$ & $-0.17^{+0.50}_{-0.47}$ & $$ & 1.70\\
\hline
\end{tabular}
\medskip
\caption{
Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$. If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then 
the model used to interpret the data does not include assembly bias.}
 }
 \label{table:parameters}
\end{table*}
%---------------------------------------------------------------------------------------------------------------------------------

\begin{figure*}
\begin{center}
\includegraphics[width=15.0cm]{Mr20_covar_triangle_1.pdf}
\caption{
Two-dimensional marginalized constraints on HOD parameters inferred from 
standard HOD fits to $\wprp(\rp)$ data for the $M_r<-20$ sample. The HOD parameter 
$\log (M_0)$ is extremely poorly constrained by the $\wprp(\rp)$ data and has been 
omitted from this panel. 
}
\label{fig:Mr20triangle}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=8.3cm]{Mr19samples.pdf}
\includegraphics[width=8.3cm]{Mr19ABsamples.pdf}
\caption{
{\bf Left:} The $M_r<-19$ threshold sample projected correlation function with diagonal elements of 
covariance (points with errorbars). The grey lines are 25 randomly-selected HOD models that yield 
$\Delta \chi^2 <1$ compared to the best-fitting model. {\bf Right:} Same as the left panel for decorated 
HOD models that contain parameters to describe the strength of assembly bias.
}
\label{fig:Mr19samples}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=8.3cm]{Mr20samples.pdf}
\includegraphics[width=8.3cm]{Mr20ABsamples.pdf}
\caption{
The same as Figure~\ref{fig:Mr19samples}, but for the $M_r<-20$ threshold sample.
}
\label{fig:Mr20samples}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=8.3cm]{Mr21samples.pdf}
\includegraphics[width=8.3cm]{Mr21ABsamples.pdf}
\caption{
The same as Figure~\ref{fig:Mr19samples}, but for the $M_r<-21$ threshold sample.
}
\label{fig:Mr20samples}
\end{center}
\end{figure*}

%-------------------------
\subsection{Analysis with Decorated HOD}
\label{subsection:ab}
%-------------------------

\begin{figure*}
\begin{center}
\includegraphics[width=15.0cm]{Mr19ABTri.pdf}
\caption{
Two-dimensional marginalized constraints on decorated HOD parameters inferred from fits 
to $\wprp(\rp)$ data for the $M_r<-19$ sample. The decorated HOD models include a 
two-parameter model for assembly bias. The HOD parameter $\log (M_0)$ is extremely 
poorly constrained by the data and has been suppressed for clarity. Likewise, as in 
Fig.~\ref{fig:Mr20triangle}, $\sigma_{\log M}$ and $\log (M_{\rm min})$ share a 
narrow degeneracy, so we have suppressed $\sigma_{\log M}$ in order to make 
constraints on other parameters more easily visible.
}
\label{fig:Mr19ABtriangle}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=15.0cm]{Mr20ABTri.pdf}
\caption{
The same as Figure~\ref{fig:Mr19ABtriangle}, but for the $M_r<-20$ sample.
}
\label{fig:Mr20ABtriangle}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=15.0cm]{Mr21ABTri.pdf}
\caption{
The same as Figure~\ref{fig:Mr19ABtriangle}, but for the $M_r<-21$ sample.
}
\label{fig:Mr21ABtriangle}
\end{center}
\end{figure*}

%------------------------------------------------

%------------------------------------------------
\end{document}
%------------------------------------------------

### 2016-05-23 ms.tex
Changed author Prince R. Nelson to P. Rogers Nelson

@@
 {Andrew R. Zentner$^{1}$, Andrew P. Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
-Antonio Villareal$^{1}$, Johannes Lange$^{3}$, Prince R. Nelson$^{4}$, Probably some others of unspecified origin\\ \\
+Antonio Villareal$^{1}$, Johannes Lange$^{3}$, P. Rogers Nelson$^{4}$, Probably some others of unspecified origin\\ \\
 $^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\

### 2016-05-25 ms.tex
Small updates to constraints table.

--- 2016-05-19 ms.tex
@@
 $-20.5$ & Zentner+16 & $12.25^{+0.07}_{-0.03}$ & $0.23^{+0.17}_{-0.15}$ & $13.59^{+0.02}_{-0.02}$ & $1.20^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.90\\
-$-20.5$ & Zentner+16 & $12.30^{+0.11}_{-0.07}$ & $0.42^{+0.20}_{-0.26}$ & $13.59^{+0.04}_{-0.04}$ & $1.15^{+0.05}_{-0.06}$ & $>0.0 (90\%)$ & $0.23^{+0.39}_{-0.31}$ & 1.71 \vspace*{5pt}\\
+$-20.5$ & Zentner+16 & $12.31^{+0.12}_{-0.08}$ & $0.44^{+0.20}_{-0.25}$ & $13.59^{+0.04}_{-0.04}$ & $1.15^{+0.05}_{-0.06}$ & $>0.03 (90\%)$ & $0.23^{+0.39}_{-0.31}$ & 1.71 \vspace*{5pt}\\
 %
@@
 $-19.5$ & Zentner+16 & $11.76^{+0.33}_{-0.11}$ & $0.51^{+0.51}_{-0.29}$ & $13.05^{+0.04}_{-0.08}$ & $1.12^{+0.04}_{-0.07}$ & $--$ & $--$ & 1.24\\
-$-19.5$ & Zentner+16 & $11.70^{+0.23}_{-0.08}$ & $0.42^{+0.42}_{-0.26}$ & $13.04^{+0.08}_{-0.13}$ & $1.07^{+0.07}_{-0.10}$ & $>-0.05 (84\%)$ & $>-0.14 (84\%)$ & 0.83 \vspace*{5pt}\\
+$-19.5$ & Zentner+16 & $11.80^{+0.36}_{-0.16}$ & $0.63^{+0.53}_{-0.37}$ & $13.04^{+0.09}_{-0.12}$ & $1.06^{+0.07}_{-0.10}$ & $>-0.01 (84\%)$ & $>-0.16 (84\%)$ & 0.69 \vspace*{5pt}\\
 %
@@
 \caption{
-Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$. If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then 
+Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as fits using a parameterized model of assembly bias. Assembly bias is quantified by the 
+parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary property that we assume to determine the galaxy HOD is halo formation time. 
+$A_{\rm cen,sat}=0$ means that there is no assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that halo formation time is maximally correlated (anticorrelated) 
+with halo formation time. Thus the parameters range over $-1 \le A_{\rm cen,sat} \le 1$. If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then 
 the model used to interpret the data does not include assembly bias.}

### 2016-05-25 ms.tex
Added information on priors, some text.

@@
 %---------------------------
+\subsection{Halotools Implementation of HOD Models}
+\label{subsection:halotools}
+%---------------------------
+
+%---------------------------
+\subsection{HOD with Assembly Bias: The Decorated HOD}
+\label{subsection:decorated}
+%---------------------------
+
+%---------------------------
+\subsection{Parameter Inference}
+\label{subsection:mcmc}
+%---------------------------
+
+To infer parameters for the HOD and Decorated HOD models described in the previous subsections, 
+we performed a Markov Chain Monte Carlo (MCMC) sampling of the posteriors using the 
+affine-invariant ensemble sampler of \citet{goodman_weare10} as implemented in the 
+{\tt emcee} software package \citep{foreman-mackey_etal13}. For most cases, we find that 
+$\sim 3-10 \times 10^{6}$ samples are necessary in order for our chains to converge.
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{table}
+\begin{center}
+{\renewcommand{\arraystretch}{1.3}
+\renewcommand{\tabcolsep}{0.2cm}
+\begin{tabular}{l c}
+\hline 
+\hline
+Parameter & Prior Interval\\ 
+\hline
+$\log (M_{\mathrm{min}})$ & [9.0,14.0] \\
+$\sigma_{\log M}$ & [0.01,1.5] \\
+$\log (M_0)$ & [9.0,14.0]\\
+$\log (M_1)$ & [10.7,15.0]\\
+$\alpha$ & [0.0,2.0]\\
+$A_{\mathrm{cen}}$ & [-1.0,1.0]\\
+$A_{\mathrm{sat}}$ & [-1.0,1.0]\\
+\hline
+\end{tabular}
+\medskip
+\caption{
+Ranges for the priors used in the parameter inference. All prior distributions are uniform over the 
+specified ranges.}
+ }
+ \label{table:priors}
+ \end{center}
+\end{table}
+%--------------------------------------------------------------------------------------------------------------------------------
+
+The most important detail of this analysis is the priors on the parameters. In all analyses 
+discussed in this paper, we adopt priors that are uniform distributions over the intervals 
+specified in Table~\ref{table:priors}. In the case of the assembly bias parameters 
+$A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$, the priors represent physical 
+boundaries. These parameters must satisfy $-1 \le A_{\mathrm{cen,sat}} \le 1$. 
+Physical considerations require parameter $\sigma_{\log M} > 0$. All other 
+priors have a negligible influence on the posterior aside from $\log M_0$. 
+We find that $\log M_0$ is often very poorly constrained by clustering data.
+
+%---------------------------
 \section{Results}
@@
 Prior to discussing our results using models that include assembly bias, we present 
-results of standard HOD analyses that include no model for assembly bias.
+results of standard HOD analyses that include no model for assembly bias. The results of 
+the standard HOD analyses and all other analyses are shown in the form of marginalized 
+constraints on individual parameters in Table~\ref{table:parameters}. We compare our parameter 
+constraints to the standard HOD analysis performed by \citet{zehavi_etal11} in Table~\ref{table:parameters} 
+as well.
 
@@
 
+\bibliography{ms.bib}
+
 %------------------------------------------------

### 2016-05-26 ms.tex
Began discussion of standard HOD fits.

@@
 
+\begin{equation}
+\label{eq:nsat}
+\langle N_{\rm sat}(M)\rangle = \left( \frac{M - M_0}{M_1} \right)^{\alpha}
+\end{equation}
+
 %---------------------------
@@
 constraints to the standard HOD analysis performed by \citet{zehavi_etal11} in Table~\ref{table:parameters} 
-as well.
+as well. An example of the inferred posteriors for the HOD parameters is shown in Figure~\ref{fig:Mr20triangle}. 
+The left-hand panels of Figure~\ref{fig:Mr19samples}, Figure~\ref{fig:Mr20samples}, and Figure~\ref{fig:Mr21samples} 
+show the projected correlation function data along with predictions for $\wprp(\rp)$ from 50 randomly-selected 
+models from the MCMC chains. Note that the significant covariance in the data makes it difficult to 
+determine the quality of fit from visual inspection of these figures.
+
+%--------------------------No AB Triangle Plot-----------------------------------------------------------------------------
+\begin{figure*}
+\begin{center}
+\includegraphics[width=15.0cm]{Mr20_covar_triangle_1.pdf}
+\caption{
+Two-dimensional marginalized constraints on HOD parameters inferred from 
+standard HOD fits to $\wprp(\rp)$ data for the $M_r<-20$ sample. The HOD parameter 
+$\log (M_0)$ is extremely poorly constrained by the $\wprp(\rp)$ data and has been 
+omitted. The inner contours contain $68\%$ of the posterior probability while the 
+outer contours contain $95\%$ of the probability. The panels along the diagonal 
+show the one-dimensional, marginalized posteriors on each of these parameters.
+}
+\label{fig:Mr20triangle}
+\end{center}
+\end{figure*}
+%----------------------------------------------------------------------------------------------------------------------------------
+
+The inferred parameters from our standard analyses differ in several ways from the \citet{zehavi_etal11} 
+analysis. Firstly, in our re-analysis of the projected clustering data, we generally find all mass scales to 
+be slightly higher than in the work of \citet{zehavi_etal11}. This difference is largely due to the slightly 
+different cosmologies adopted in this work. The most important difference are in the values of $\Omega_{\rm M}$, and $\sigma_8$.  
+\citet{zehavi_etal11} assumed $\Omega_{\rm M}=0.25$ and $\sigma_8=0.8$, 
+whereas in the present work, we use the BolshoiP simulation in which $\Omega_{\rm M}=0.307$ and $\sigma_8=0.82$. 
+Larger mass scales are necessary in an analysis with higher $\Omega_{\rm M}$ and $\sigma_8$ in order to maintain galaxy 
+number densities with larger halo number densities.
 
@@
 $-20.5$ & Zentner+16 & $12.25^{+0.07}_{-0.03}$ & $0.23^{+0.17}_{-0.15}$ & $13.59^{+0.02}_{-0.02}$ & $1.20^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.90\\
-$-20.5$ & Zentner+16 & $12.31^{+0.12}_{-0.08}$ & $0.44^{+0.20}_{-0.25}$ & $13.59^{+0.04}_{-0.04}$ & $1.15^{+0.05}_{-0.06}$ & $>0.03 (90\%)$ & $0.23^{+0.39}_{-0.31}$ & 1.71 \vspace*{5pt}\\
+$-20.5$ & Zentner+16 & $12.32^{+0.13}_{-0.08}$ & $0.45^{+0.21}_{-0.25}$ & $13.59^{+0.04}_{-0.04}$ & $1.14^{+0.05}_{-0.06}$ & $>0.08 (90\%)$ & $0.22^{+0.40}_{-0.31}$ & 1.40 \vspace*{5pt}\\
 %
@@
 \caption{
-Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as fits using a parameterized model of assembly bias. Assembly bias is quantified by the 
-parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary property that we assume to determine the galaxy HOD is halo formation time. 
-$A_{\rm cen,sat}=0$ means that there is no assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that halo formation time is maximally correlated (anticorrelated) 
-with halo formation time. Thus the parameters range over $-1 \le A_{\rm cen,sat} \le 1$. If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then 
-the model used to interpret the data does not include assembly bias.}
+Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as fits using a parameterized model of assembly bias. 
+Assembly bias is quantified by the parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary 
+property that we assume to determine the galaxy HOD is halo formation time. $A_{\rm cen,sat}=0$ means that there is no 
+assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that halo formation time is maximally 
+correlated (anticorrelated) with halo formation time. Thus the parameters range over $-1 \le A_{\rm cen,sat} \le 1$. 
+If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then the model used to interpret the data 
+does not include assembly bias.
+}
 }
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=15.0cm]{Mr20_covar_triangle_1.pdf}
-\caption{
-Two-dimensional marginalized constraints on HOD parameters inferred from 
-standard HOD fits to $\wprp(\rp)$ data for the $M_r<-20$ sample. The HOD parameter 
-$\log (M_0)$ is extremely poorly constrained by the $\wprp(\rp)$ data and has been 
-omitted from this panel. 
-}
-\label{fig:Mr20triangle}
-\end{center}
-\end{figure*}
-
+%----------------------------------------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 covariance (points with errorbars). The grey lines are 25 randomly-selected HOD models that yield 
-$\Delta \chi^2 <1$ compared to the best-fitting model. {\bf Right:} Same as the left panel for decorated 
-HOD models that contain parameters to describe the strength of assembly bias.
+$\Delta \chi^2 <1$ compared to the best-fitting model. {\bf Right:} Same as the left panel but using a 
+fit to a Decorated HOD model that contain parameters to describe the strength of assembly bias.
 }
@@
 \end{figure*}
+%---------------------------------------------------------------------------------------------------------------------------------
 
+%---------------------------------------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 }
-\label{fig:Mr20samples}
+\label{fig:Mr21samples}
 \end{center}
 \end{figure*}
+%---------------------------------------------------------------------------------------------------------------------------------
+
+A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
+find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
+we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
+\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
+with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
+$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
+results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
+\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
+$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
+it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
+value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
+that the tighter constraints quoted by \citet{zehavi_etal11} must be an error or must be driven by some 
+prior that is not clearly specified in their manuscript.
+
+The results of this subsection demonstrate that we achieve reasonable fits to projected galaxy clustering 
+data using direct HOD population of a high-resolution numerical simulation of structure formation. These results 
+also update existing constraints in the literature in two respects. First, we work within the best-fit Planck cosmology. 
+Second, we perform our parameter inference analysis using direct population of halos identified in a numerical 
+simulations. This greatly mitigates modeling uncertainties associated with nonlinear density field evolution, 
+scale-dependent halo bias, halo exclusion, or other effects that have been difficult to incorporate into 
+analytical halo models with high precision.
 
@@
 
+%------------------------------------------------
+\section{Conclusions}
+\label{section:conclusions}
+%------------------------------------------------
+
+%------------------------------------------------
 \bibliography{ms.bib}

### 2016-05-26 ms.tex
Minor structural changes to text.

@@
 we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
-\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
+\citet{zehavi_etal11}. As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
+share a relatively narrow degeneracy. This degeneracy is largely induced by the measured number density of 
+the sample. Increasing $\log (M_{\rm min})$ decreases galaxy number density, but this can be compensated by 
+an increase in $\sigma_{\log M}$, which places galaxies in a fraction of the considerably more numerous halos 
+with masses less than $M_{\rm min}$.
+
+We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
 with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
@@
 
+We turn now to a discussion of our parameter inference analysis of projected galaxy clustering 
+in Decorated HOD models that include a treatment of galaxy assembly bias. In this work, 
+we consider only the simplest model of galaxy assembly bias, introducing only two new 
+parameters, $A_{\rm cen}$ and $A_{\rm sat}$, that describe the strength of central galaxy 
+and satellite galaxy assembly bias respectively. These parameters are limited to values 
+of $-1 \le A_{\rm cen,sat} \le 1$, and $A_{\rm cen,sat}=0$ when there is no galaxy assembly bias. 
+In this work, we use halo concentration as our secondary halo property, so $A_{\rm cen,sat}=1$ 
+($A_{\rm cen,sat}=-1$) means that the mean number of galaxies per halo is maximally 
+correlated (anti-correlated) with halo concentration. The model and its implementation 
+in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above.
+
+The one-dimensional marginalized constraints on all parameters form these analyses 
+are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}. 
+In cases where the posterior on a parameter is monotonic within the physical parameter 
+range, we quote an upper or lower limit on the parameter.
+
+Examples of our fits are given in the right-hand panels of Figure~\ref{fig:Mr19samples}, 
+Figure~\ref{fig:Mr20samples}, and Figure~\ref{fig:Mr21samples}. The general trend that 
+can be gleaned from these figures is that introducing assembly bias improves the ability 
+of the predicted two-point functions to match the measured two-point functions across the 
+transition form the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$. 
+Visually, these differences appear to be small; however, Table~\ref{table:parameters} shows that 
+they are statistically important.
+
+%------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 Two-dimensional marginalized constraints on decorated HOD parameters inferred from fits 
-to $\wprp(\rp)$ data for the $M_r<-19$ sample. The decorated HOD models include a 
+to $\wprp(\rp)$ data for the $M_r<-19$ sample. The contours and histograms along the diagonal 
+panels are as in Fig.~\ref{fig:Mr20triangle}. The decorated HOD models include a 
 two-parameter model for assembly bias. The HOD parameter $\log (M_0)$ is extremely 
@@
 \end{figure*}
+%----------------------------------------------------------------------------------------------
 

### 2016-05-27 ms.tex
Started adding text to subsection:halotools

@@
 
+Important points:
+-supersedes previous analyses even for standard HOD.
+-cannot rule out assembly bias using galaxy clustering.
+-some samples favor assembly bias.
+
 \end{abstract}
@@
 %---------------------------
+
+For more than a decade, halo occupation modeling has been used to 
+interpret large-scale structure measurements and exploit these measurements 
+to constrain galaxy formation models and cosmology \citep[e.g.,][]{yang03,tinker05,zehavi05a,
+porciani06,vdBosch07,Zheng07,conroy_wechsler09,yang09b,zehavi_etal11,guo_etal11b,
+wake_etal11,yang11a,yang12,leauthaud_etal12,tinker_etal13,cacciato_etal13,
+more_etal13,guo_etal14,zu_mandelbaum15b}. The key assumptions underlying 
+halo occupation modeling are: (1) all galaxies reside in dark matter halos that are biased 
+tracers of the density field; and (2) galaxies occupy halos as a function of halo masses 
+only. It is now well known that halo bias depends upon halo properties other than mass
+\citep[e.g.][]{gao_etal05,wechsler06,gao_white07,zentner07,dalal_etal08,lacerna11}, 
+an effect called halo assembly bias. If galaxies occupy halos as a function of properties 
+other than halo mass, then standard halo occupation methods will be subject to a 
+systematic error due to galaxy assembly bias. Several of us have previously shown that 
+this error can be significant in an analysis of galaxy clustering and can bias inferences 
+about many aspects of galaxy evolution \citep{zentner_etal14}. Consequently, we have 
+also developed halo occupation models that enable galaxies to occupy halos in a manner 
+that depends upon several halo properties \citep{hearin_etal16}. In this paper, we 
+revisit the interpretation of luminosity-dependent galaxy clustering in the Sloan Digital Sky 
+Survey (SDSS) Data Release 7 (DR7) data, analyzed previously by \citet{zehavi_etal11}, in the context 
+both standard halo occupation models and these new models.
+
+Some history here, blah blah blah, Frank loves this stuff. Therefore, I'm sure this part of the introduction 
+will get quite lengthy.
+
+Our work is important for several reasons. Our work is a re-analysis of the SDSS DR7 data 
+the overcomes shortcomings of previous analyses. In particular, we use direct population of galaxies 
+in a cosmological simulation so that delicate issues present in analytic modeling, such as scale-dependent 
+halo bias, are treated exactly.  The simulation we use is based on the latest Planck cosmological parameters, 
+updating previous work. Furthermore, many important differences between this work and the previous 
+work of \citet{zehavi_etal11} were caused by insufficiently large Monte Carlo Markov Chain (MCMC) sampling 
+by \citet[][Z. Zheng \& I. Zehavi, Private Communication]{zehavi_etal11}. Therefore, our analysis 
+{\em supersedes previous analyses even in the case of standard halo occupation models}.
+
+Furthermore, our work demonstrates explicitly that significant assembly bias in 
+$M_r$-selected samples from SDSS DR7 cannot be ruled out based on a standard 
+analysis of galaxy clustering only. In fact, we find that several samples {\em 
+favor galaxy assembly bias to a degree that is statistically significant}. As demonstrated by 
+\citet{zentner_etal14}, this conclusion could have important consequences for the 
+interpretation of both extant and forthcoming data.
+
+Our paper is organized as follows. In Section~\ref{section:methods}, we discuss our implementation 
+of halo occupation models and our assumptions in our parameter inference analysis. We present 
+results for both standard halo occupation analysis and analysis in the context of models with 
+galaxy assembly bias in Section~\ref{section:results}. We summarize our results and draw 
+conclusions in Section~\ref{section:conclusions}.
 
@@
 
+To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
+In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}.
+In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for comprehensive documentation on all aspects of the {\tt Halotools} framework.
+
+\subsubsection{Occupation statistics}
+
+\subsubsection{Galaxy profiles}
+
 \begin{equation}
@@
 
+We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).
+
 %---------------------------
@@
 %---------------------------
+
+Short summary of \citet{hearin_etal16}.
 
@@
 show the one-dimensional, marginalized posteriors on each of these parameters. 
+The values above each panel on the diagonal show the 
+median value for the parameter in our chains along with the 
+16$^{\rm th}$ and 84$^{\rm th}$ percentiles. 
 }
@@
 be slightly higher than in the work of \citet{zehavi_etal11}. This difference is largely due to the slightly 
-different cosmologies adopted in this work. The most important difference are in the values of $\Omega_{\rm M}$, and $\sigma_8$.  
+different cosmologies adopted in this work. The most important difference 
+are in the values of $\Omega_{\rm M}$, and $\sigma_8$.  
 \citet{zehavi_etal11} assumed $\Omega_{\rm M}=0.25$ and $\sigma_8=0.8$, 
 whereas in the present work, we use the BolshoiP simulation in which $\Omega_{\rm M}=0.307$ and $\sigma_8=0.82$. 
-Larger mass scales are necessary in an analysis with higher $\Omega_{\rm M}$ and $\sigma_8$ in order to maintain galaxy 
-number densities with larger halo number densities.
+Slightly larger mass scales are necessary in an analysis with higher $\Omega_{\rm M}$ and $\sigma_8$ in order 
+to maintain galaxy number densities with larger halo number densities.
 
@@
 \caption{
-Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as fits using a parameterized model of assembly bias. 
+Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as 
+fits using a parameterized model of assembly bias. 
 Assembly bias is quantified by the parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary 
@@
 If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then the model used to interpret the data 
-does not include assembly bias.
+does not include assembly bias. In our analyses, quoted parameter values with errors correspond to the median 
+value of the parameter and the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles. In cases for which the posterior 
+is monotonic within the physical parameter space, we show one-sided percentiles.
 }
@@
 we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
-\citet{zehavi_etal11}. As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
-share a relatively narrow degeneracy. This degeneracy is largely induced by the measured number density of 
-the sample. Increasing $\log (M_{\rm min})$ decreases galaxy number density, but this can be compensated by 
-an increase in $\sigma_{\log M}$, which places galaxies in a fraction of the considerably more numerous halos 
-with masses less than $M_{\rm min}$.
-
-We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
+\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
 with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
@@
 value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
-that the tighter constraints quoted by \citet{zehavi_etal11} must be an error or must be driven by some 
-prior that is not clearly specified in their manuscript.
+that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.
+
+We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
+that the number of MCMC samples they included in their analysis was 
+insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
+on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
+(Z. Zheng \& I. Zehavi, Private Communication). The analysis of \citet{zehavi_etal11} 
+used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
+Additionally, we have recreated qualitatively similar behavior by considering only small subsets of all of our 
+full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
+of the discrepancies between our work and that of \citet{zehavi_etal11}.
+
+Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
+analyses. The parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
+correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
+average and $\alpha$ is the power-law index describing the dependence of average satellite 
+number on halo mass. Increasing $M_1$ decreases the number of satellites in large halos 
+by placing satellites preferentially in halos of larger mass. An increase in $\alpha$ can partly 
+compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
+grows with halo mass, leading to a larger number of satellites in high-mass halos.
+
+As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
+share a relatively narrow degeneracy as well. This degeneracy is largely induced by the 
+measured number density of the sample. Increasing $\log (M_{\rm min})$ decreases galaxy 
+number density, but this can be compensated by an increase in $\sigma_{\log M}$, which 
+places galaxies in a fraction of the considerably more numerous halos with masses less 
+than $M_{\rm min}$. The consequence is that $\log (M_{\rm min})$ and $\sigma_{\log M}$ are 
+degenerate with each other such that most of the posterior probability lies in a narrow band 
+along which $\log (M_{\rm min})$ and $\sigma_{\log M}$ are positively correlated, as shown in 
+Fig.~\ref{fig:Mr20triangle}. In the following plots, we suppress the parameter $\sigma_{\log M}$,  
+in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is 
+determined by this simple degeneracy with $\log (M_{\rm min})$.
 
@@
 data using direct HOD population of a high-resolution numerical simulation of structure formation. These results 
-also update existing constraints in the literature in two respects. First, we work within the best-fit Planck cosmology. 
-Second, we perform our parameter inference analysis using direct population of halos identified in a numerical 
-simulations. This greatly mitigates modeling uncertainties associated with nonlinear density field evolution, 
-scale-dependent halo bias, halo exclusion, or other effects that have been difficult to incorporate into 
-analytical halo models with high precision.
+also update and supersede existing constraints in the literature in at least three respects. First, we work within the 
+best-fit Planck cosmology. Second, we perform our parameter inference analysis using direct population of halos 
+identified in a numerical simulation of cosmological structure formation (BolshioP). This greatly mitigates modeling 
+uncertainties associated with nonlinear density field evolution, scale-dependent halo bias, halo exclusion, 
+or other effects that have been difficult to incorporate into analytical halo models with high precision. Third, 
+we have explored the posteriors of the parameters with significantly more samples (roughly two orders of magnitude), 
+thereby mitigating errors on inferred parameters and their errors induced by insufficient sampling of the 
+posterior.
 
@@
 correlated (anti-correlated) with halo concentration. The model and its implementation 
-in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above.
-
-The one-dimensional marginalized constraints on all parameters form these analyses 
-are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}. 
-In cases where the posterior on a parameter is monotonic within the physical parameter 
-range, we quote an upper or lower limit on the parameter.
+in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above and 
+in \citet{hearin_etal16}.
 
@@
 transition form the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$. 
+This is most apparent for the $M_r < -20$ threshold sample shown in Fig.~\ref{fig:Mr20samples}. 
 Visually, these differences appear to be small; however, Table~\ref{table:parameters} shows that 
 they are statistically important.
+
+The one-dimensional marginalized constraints on all parameters from these analyses 
+are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}. 
+In cases where the posterior on a parameter is monotonic within the physical parameter 
+range, we quote an upper or lower limit on the parameter. One- and two-dimensional 
+visualizations of the posteriors from our analysis are shown in Figure~\ref{fig:Mr19ABtriangle}, 
+Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle}.
 
@@
 
+%---------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 \end{figure*}
+%---------------------------------------------------------------------------------------------------
 
+%=-------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 \end{figure*}
+%----------------------------------------------------------------------------------------------------
+
+Table~\ref{table:parameters} and Figures~\ref{fig:Mr19ABtriangle}-\ref{fig:Mr21triangle} 
+all make several simple, generic points. Introducing additional parameter 
+freedom associated with galaxy assembly bias generally increases the viable parameter 
+space, even for the subset of standard HOD parameters. This is exactly what is 
+expected from the introduction of additional parameter freedom.
+
+Focusing attention on the parameters describing galaxy assembly bias, it is 
+evident that these parameters are often quite poorly constrained by galaxy 
+clustering data. This implies that galaxy clustering of the precision of SDSS DR7 
+measurements cannot rule out, or strongly restrict galaxy assembly bias in most 
+cases.
+
+Beyond those generic conclusions, a few specific cases of worthy of further examination. 
+Consider the $M_r < -20$ sample. The inferred value of $A_{\rm cen} > 0.28$ at 99\% 
+confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer 
+galaxies to reside in halos of larger concentration at fixed halo mass.
+
+Changes in Bayesian Information Criterion, for inclusion in some sort of table. Strong evidence 
+is usually considered to be a difference $>5$.
+
+Delta BIC 19: 4.37
+
+Delta BIC 19.5: 0.26
+
+Delta BIC 20: 4.56
+
+Delta BIC 20.5: 1.33
+
+Delta BIC 21: -0.54
 

### 2016-06-02 ms.tex
Added some basic introduction. Added private communication from Zheng and Zehavi.

@@
 
-To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
-In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}.
-In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for comprehensive documentation on all aspects of the {\tt Halotools} framework.
-
-\subsubsection{Occupation statistics}
-
-\subsubsection{Galaxy profiles}
-
 \begin{equation}
@@
 show the one-dimensional, marginalized posteriors on each of these parameters.
-The values above each panel on the diagonal show the 
-median value for the parameter in our chains along with the 
-16$^{\rm th}$ and 84$^{\rm th}$ percentiles. 
 }
@@
 \caption{
-Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as 
-fits using a parameterized model of assembly bias. 
+Results of standard HOD fits to SDSS DR7 $w_{\rm p}(r_{\rm p})$ as well as fits using a parameterized model of assembly bias. 
 Assembly bias is quantified by the parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary 
@@
 If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then the model used to interpret the data 
-does not include assembly bias. In our analyses, quoted parameter values with errors correspond to the median 
-value of the parameter and the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles. In cases for which the posterior 
-is monotonic within the physical parameter space, we show one-sided percentiles.
+does not include assembly bias.
 }
@@
 value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
-that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.
-
-We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
-that the number of MCMC samples they included in their analysis was 
+that the tighter constraints quoted by \citet{zehavi_etal11} must be an error. We have confirmed with a subset of 
+the authors of \citet{zehavi_etal11} that the number of MCMC samples they included in their analysis was 
 insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
@@
 of the discrepancies between our work and that of \citet{zehavi_etal11}.
-
-Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
-analyses. The parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
-correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
-average and $\alpha$ is the power-law index describing the dependence of average satellite 
-number on halo mass. Increasing $M_1$ decreases the number of satellites in large halos 
-by placing satellites preferentially in halos of larger mass. An increase in $\alpha$ can partly 
-compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
-grows with halo mass, leading to a larger number of satellites in high-mass halos.
-
-As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
-share a relatively narrow degeneracy as well. This degeneracy is largely induced by the 
-measured number density of the sample. Increasing $\log (M_{\rm min})$ decreases galaxy 
-number density, but this can be compensated by an increase in $\sigma_{\log M}$, which 
-places galaxies in a fraction of the considerably more numerous halos with masses less 
-than $M_{\rm min}$. The consequence is that $\log (M_{\rm min})$ and $\sigma_{\log M}$ are 
-degenerate with each other such that most of the posterior probability lies in a narrow band 
-along which $\log (M_{\rm min})$ and $\sigma_{\log M}$ are positively correlated, as shown in 
-Fig.~\ref{fig:Mr20triangle}. In the following plots, we suppress the parameter $\sigma_{\log M}$,  
-in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is 
-determined by this simple degeneracy with $\log (M_{\rm min})$.
 
@@
 correlated (anti-correlated) with halo concentration. The model and its implementation 
-in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above and 
-in \citet{hearin_etal16}.
+in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above.
+
+The one-dimensional marginalized constraints on all parameters form these analyses 
+are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}. 
+In cases where the posterior on a parameter is monotonic within the physical parameter 
+range, we quote an upper or lower limit on the parameter.
 
@@
 transition form the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$. 
-This is most apparent for the $M_r < -20$ threshold sample shown in Fig.~\ref{fig:Mr20samples}. 
 Visually, these differences appear to be small; however, Table~\ref{table:parameters} shows that 
 they are statistically important.
-
-The one-dimensional marginalized constraints on all parameters from these analyses 
-are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}. 
-In cases where the posterior on a parameter is monotonic within the physical parameter 
-range, we quote an upper or lower limit on the parameter. One- and two-dimensional 
-visualizations of the posteriors from our analysis are shown in Figure~\ref{fig:Mr19ABtriangle}, 
-Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle}.
 
@@
 
-%---------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 \end{figure*}
-%---------------------------------------------------------------------------------------------------
 
-%=-------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 \end{figure*}
-%----------------------------------------------------------------------------------------------------
-
-Table~\ref{table:parameters} and Figures~\ref{fig:Mr19ABtriangle}-\ref{fig:Mr21triangle} 
-all make several simple, generic points. Introducing additional parameter 
-freedom associated with galaxy assembly bias generally increases the viable parameter 
-space, even for the subset of standard HOD parameters. This is exactly what is 
-expected from the introduction of additional parameter freedom.
-
-Focusing attention on the parameters describing galaxy assembly bias, it is 
-evident that these parameters are often quite poorly constrained by galaxy 
-clustering data. This implies that galaxy clustering of the precision of SDSS DR7 
-measurements cannot rule out, or strongly restrict galaxy assembly bias in most 
-cases.
-
-Beyond those generic conclusions, a few specific cases of worthy of further examination. 
-Consider the $M_r < -20$ sample. The inferred value of $A_{\rm cen} > 0.28$ at 99\% 
-confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer 
-galaxies to reside in halos of larger concentration at fixed halo mass.
-
-Changes in Bayesian Information Criterion, for inclusion in some sort of table. Strong evidence 
-is usually considered to be a difference $>5$.
-
-Delta BIC 19: 4.37
-
-Delta BIC 19.5: 0.26
-
-Delta BIC 20: 4.56
-
-Delta BIC 20.5: 1.33
-
-Delta BIC 21: -0.54
 

### 2016-06-02 ms.tex
Began discussion of AB results.

--- 2016-05-27 ms.tex
@@
 %---------------------------
-
-To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
-In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}.
-In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for comprehensive documentation on all aspects of the {\tt Halotools} framework.
-
-\subsubsection{Occupation statistics}
-
-\subsubsection{Galaxy profiles}
 

### 2016-06-02 ms.tex
Added equation for central occupation

--- 2016-05-27 ms.tex
@@
 \newcommand{\eeq}{\end{equation}}
+
+\newcommand{\mvir}{M_{\rm vir}}
+\newcommand{\ncen}{N_{\rm cen}}
+\newcommand{\nsat}{N_{\rm sat}}
 
@@
 In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}.
-In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for comprehensive documentation on all aspects of the {\tt Halotools} framework.
+In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.
 
@@
 
-\subsubsection{Galaxy profiles}
+In standard HOD models, there are two types of galaxies: centrals and satellites.
+The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively.
+$P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy.
+So the occupation statistics of central galaxies is specified by its first moment, which we model as
+
+\begin{equation}
+\label{eq:ncen}
+\langle N_{\mathrm{cen}} \rangle_{M} =
+        \frac{1}{2}\left( 1 +
+        \mathrm{erf}\left( \frac{\log_{10}M -
+        \log_{10}M_{min}}{\sigma_{\log_{10}M}} \right) \right)
+\end{equation}
 
@@
 \end{equation}
+
+\subsubsection{Galaxy profiles}
 

### 2016-06-03 ms.tex
Added some discussion of how Halotools implements the standard HOD

@@
 \newcommand{\mvir}{M_{\rm vir}}
+\newcommand{\rvir}{R_{\rm vir}}
 \newcommand{\ncen}{N_{\rm cen}}
@@
 
+\subsubsection{Simulation}
+We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).
+
 \subsubsection{Occupation statistics}
@@
 \label{eq:ncen}
-\langle N_{\mathrm{cen}} \rangle_{M} =
+\langle N_{\mathrm{cen}} \rangle(M) =
         \frac{1}{2}\left( 1 +
@@
 \end{equation}
+For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ a central galaxy is assigned to each halo whose random number is less than the corresponding value of $\langle N_{\mathrm{cen}} \rangle(M);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(M)$ are left devoid of centrals.
 
+We model the distribution $P(\nsat|\mvir)$ to be a Poisson distribution with first moment given by a power law, 
 \begin{equation}
 \label{eq:nsat}
-\langle N_{\rm sat}(M)\rangle = \left( \frac{M - M_0}{M_1} \right)^{\alpha}
+\langle N_{\rm sat}\rangle(M) = \left( \frac{M - M_0}{M_1} \right)^{\alpha}. 
 \end{equation}
@@
 
-We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).
+Central galaxies in the standard HOD models reside at the halo center, moving with the same velocity as the host halo peculiar velocity.
+We model the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ of the halo center, with a spherically symmetric NFW profile \citep{nfw97}.
+The concentration $c$ of each halo's satellite galaxy profile is taken to be the same as the concentration of the dark matter particles in the halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, because halos with very large values for the concentration tend to be poorly described by an NFW profile, for example due to a recent merger.}
+
+We model the velocities of satellite galaxies to be a Gaussian whose first moment is the host halo velocity and whose second moment is the solution to the isotropic Jeans equation for an NFW profile \citep{more09b},
+\begin{equation}
+\sigma^{2}_{r}(\tilde{r}|c) = V_{\rm vir}^{2}\frac{c^{2}\tilde{r}(1 + c\tilde{r})^{2}}{g(c)}\int_{c\tilde{r}}^{\infty}{\rm d}y\frac{g(y)}{y^{3}(1 + y)^{2}}, 
+\end{equation}
+where $\tilde{r} = r/\rvir$ and $g(y) = \rm{ln}(1+y) - y / (1+y).$
 

### 2016-06-03 ms.tex

@@
 To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
-In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}.
+In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal16}.
 In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.
@@
 \subsubsection{Simulation}
-We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).
+We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters). yadda yadda yadda.
 
@@
 $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy.
-So the occupation statistics of central galaxies is specified by its first moment, which we model as
+So occupation statistics of central galaxies are specified by the first moment, which we model as
 

### 2016-06-03 ms.tex
Added Bayesion Information Values.

@@
 used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
-Additionally, we have recreated qualitatively similar behavior by considering only small subsets of all of our 
+Additionally, we have recreated qualitatively similar behavior by considering only small subsets of our 
 full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
@@
 freedom associated with galaxy assembly bias generally increases the viable parameter 
-space, even for the subset of standard HOD parameters. This is exactly what is 
+space, even for the subset of standard HOD parameters. Constraints on the 
+standard HOD parameters are generally less restrictive. This is exactly what is 
 expected from the introduction of additional parameter freedom.
@@
 evident that these parameters are often quite poorly constrained by galaxy 
-clustering data. This implies that galaxy clustering of the precision of SDSS DR7 
-measurements cannot rule out, or strongly restrict galaxy assembly bias in most 
-cases.
+clustering data. This is important as it implies that galaxy clustering of the precision 
+of SDSS DR7 measurements cannot rule out, or strongly restrict galaxy assembly 
+bias in many cases. Nonetheless, it is apparent that the presence of assembly bias 
+can alter the inferred HOD, or more generally, the inferred relationship between 
+galaxies and halo mass. This is most evident for the $M_r < -20$ threshold sample, 
+for which there are significant differences in the inferred values of all baseline HOD 
+parameters between models with and without galaxy assembly bias. Other threshold 
+samples exhibit significant changes particularly for $\alpha$, and to a lesser degree 
+for $\log (M_{\rm min})$ and $\sigma_{\log M}$.
 
-Beyond those generic conclusions, a few specific cases of worthy of further examination. 
+Beyond those generic conclusions, a few specific cases are worthy of further examination. 
 Consider the $M_r < -20$ sample. The inferred value of $A_{\rm cen} > 0.28$ at 99\% 
 confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer 
-galaxies to reside in halos of larger concentration at fixed halo mass.
+galaxies to reside in halos of larger concentration at fixed halo mass. This particular threshold 
+sample is the most significant outlier in this regard. Nevertheless, there are hints of assembly 
+bias in other samples. Satellite galaxies show a marginal preference for occupying halos of 
+higher concentration in the $M_r < -19$ threshold sample. The $M_r < -19$ sample exhibits 
+weak preference for a positive correlation of galaxy occupation with halo concentration at fixed 
+mass for both satellite galaxies and central galaxies. Continuing upward with luminosity, 
+the $M_r < -20.5$ sample exhibits a significant preference for central galaxy assembly bias. 
+Lastly, there is no preference for either central galaxy or satellite galaxy assembly bias 
+for the $M_r < -21$ threshold sample, for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$ 
+are consistent with zero will within 1$\sigma$. These data suggest that assembly bias 
+may be present in the real universe.
 
-Changes in Bayesian Information Criterion, for inclusion in some sort of table. Strong evidence 
-is usually considered to be a difference $>5$.
-
-Delta BIC 19: 4.37
-
-Delta BIC 19.5: 0.26
-
-Delta BIC 20: 4.56
-
-Delta BIC 20.5: 1.33
-
-Delta BIC 21: -0.54
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{table}
+\begin{center}
+{\renewcommand{\arraystretch}{1.3}
+\renewcommand{\tabcolsep}{0.2cm}
+\begin{tabular}{c c}
+\hline 
+\hline
+$M_r$ Threshold & $\Delta \mathrm{BIC}$ \\ 
+\hline
+-21 & -0.54 \\
+-20.5 & 1.33 \\
+-20 & 4.56\\
+-19.5 & 0.26\\
+-19 & 4.37\\
+\hline
+\end{tabular}
+\medskip
+\caption{
+Change to the Bayesian Information Criterion, $\Delta \mathrm{BIC}$, 
+after introducing additional parametric freedom to accommodate galaxy 
+assembly bias. Sign convention is such that positive values favor models including 
+assembly bias, negative values favor standard HOD models with no assembly bias parameters. Changes in 
+the Bayesian Information Criterion $\vert \Delta \mathrm{BIC}\vert \ge 5$ strongly favor one model 
+over another.
+}
+ }
+ \label{table:priors}
+ \end{center}
+\end{table}
+%--------------------------------------------------------------------------------------------------------------------------------
 

### 2016-06-04 ms.tex
Added Simulation section

@@
 \usepackage[dvipsnames]{xcolor}
-%\usepackage{hyperref}
+\usepackage{hyperref}
 \usepackage{yfonts}
@@
 \subsubsection{Simulation}
-We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters). yadda yadda yadda.
+All of our analyses are based on the Bolshioi-Planck simulation \citep{riebe_etal11}. 
+Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ and with a box size of $250$ ${\rm Mpc}/h$ and a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.
+
+We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}.
+In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius density contrast given in \citet{bryan_norman98}.
+When populating this catalog with mock galaxies, we only use present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.
 
@@
 The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively.
-$P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy.
-So occupation statistics of central galaxies are specified by the first moment, which we model as
+$P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo has only either zero or one central galaxy.
+So occupation statistics of central galaxies are specified by the first moment of $P(\ncen|\mvir)$, which we model as
 
@@
 \label{eq:ncen}
-\langle N_{\mathrm{cen}} \rangle(M) =
+\langle N_{\mathrm{cen}} \rangle(\mvir) =
         \frac{1}{2}\left( 1 +
-        \mathrm{erf}\left( \frac{\log_{10}M -
-        \log_{10}M_{min}}{\sigma_{\log_{10}M}} \right) \right)
+        \mathrm{erf}\left( \frac{\log_{10}\mvir -
+        \log_{10}M_{\rm min}}{\sigma_{\log_{10}M}} \right) \right)
 \end{equation}
-For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ a central galaxy is assigned to each halo whose random number is less than the corresponding value of $\langle N_{\mathrm{cen}} \rangle(M);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(M)$ are left devoid of centrals.
+For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \rangle(\mvir);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(\mvir)$ are left devoid of centrals.
 
@@
 \label{eq:nsat}
-\langle N_{\rm sat}\rangle(M) = \left( \frac{M - M_0}{M_1} \right)^{\alpha}. 
+\langle N_{\rm sat}\rangle(\mvir) = \left( \frac{\mvir - M_0}{M_1} \right)^{\alpha}. 
 \end{equation}
@@
 \end{equation}
-where $\tilde{r} = r/\rvir$ and $g(y) = \rm{ln}(1+y) - y / (1+y).$
+where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$
 
@@
 %------------------------------------------------
+\section{Acknowledgements}
+\label{section:acknowledgements}
+%------------------------------------------------
+
+The authors gratefully acknowledge the Gauss Centre for Supercomputing e.V.
+(www.gauss-centre.eu) and the Partnership for Advanced Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the MultiDark simulation project by providing computing time on the GCS Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ, www.lrz.de).
+The Bolshoi simulations have been performed within the Bolshoi project of the University of California High-Performance AstroComputing Center (UC-HiPACC) and were run at the NASA Ames Research Center.
+
+%------------------------------------------------
 \bibliography{ms.bib}

### 2016-06-06 ms.tex
Made minor additions to methods section.

@@
 \newcommand{\nsat}{N_{\rm sat}}
+\newcommand{\ngal}{N_{\rm gal}}
+\newcommand{\abias}{\mathcal{A}_{\rm bias}}
 
@@
 Important points:
+
 -supersedes previous analyses even for standard HOD.
+
 -cannot rule out assembly bias using galaxy clustering.
+
 -some samples favor assembly bias.
@@
 
-For more than a decade, halo occupation modeling has been used to 
-interpret large-scale structure measurements and exploit these measurements 
+Halo occupation modeling has frequently 
+been used to interpret large-scale structure measurements and exploit these measurements 
 to constrain galaxy formation models and cosmology \citep[e.g.,][]{yang03,tinker05,zehavi05a,
@@
 halo occupation modeling are: (1) all galaxies reside in dark matter halos that are biased 
-tracers of the density field; and (2) galaxies occupy halos as a function of halo masses 
+tracers of the density field; and (2) galaxies occupy halos as a function of halo mass 
 only. It is now well known that halo bias depends upon halo properties other than mass
 \citep[e.g.][]{gao_etal05,wechsler06,gao_white07,zentner07,dalal_etal08,lacerna11}, 
-an effect called halo assembly bias. If galaxies occupy halos as a function of properties 
-other than halo mass, then standard halo occupation methods will be subject to a 
-systematic error due to galaxy assembly bias. Several of us have previously shown that 
+an effect called {\em halo assembly bias}. If galaxies occupy halos as a function of properties 
+that affect halo clustering, other than mass, then standard halo occupation methods will be subject to a 
+systematic error due to {\em galaxy assembly bias}. Several of us have previously shown that 
 this error can be significant in an analysis of galaxy clustering and can bias inferences 
 about many aspects of galaxy evolution \citep{zentner_etal14}. Consequently, we have 
-also developed halo occupation models that enable galaxies to occupy halos in a manner 
+developed halo occupation models that enable galaxies to occupy halos in a manner 
 that depends upon several halo properties \citep{hearin_etal16}. In this paper, we 
@@
 $M_r$-selected samples from SDSS DR7 cannot be ruled out based on a standard 
-analysis of galaxy clustering only. In fact, we find that several samples {\em 
-favor galaxy assembly bias to a degree that is statistically significant}. As demonstrated by 
-\citet{zentner_etal14}, this conclusion could have important consequences for the 
-interpretation of both extant and forthcoming data.
+analysis of galaxy clustering alone. In fact, we find that the clustering of galaxies in 
+several luminosity threshold samples 
+{\em favors galaxy assembly bias to a degree that is statistically significant}. 
+As suggested by the previous work of \citet{zentner_etal14}, 
+this conclusion could have important consequences for the 
+interpretation of both extant and forthcoming galaxy survey data.
 
@@
 To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}. 
-In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal16}.
-In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.
+We explore halo occupation distribution models (HOD) models in this work 
+\citep[e.g.][]{seljak00,ma_fry00,scoccimarro01a,berlind02}, though other 
+techniques that can be used to interpret such data, such as the conditional luminosity function 
+\citep[CLF, e.g.,][]{yang03,vdBosch13}, exist. In this section, we review the ``standard" HOD 
+model used in the present work which assumes that there is no galaxy assembly bias. We refer to 
+such a model as ``standard" because all HOD analyses of galaxy clustering to date have assumed no 
+galaxy assembly bias. In the following section, we describe 
+the Decorated HOD model described in \citet{hearin_etal16}. In both cases, we will only 
+review the salient features of our methodology briefly; 
+interested readers can always refer to {\tt halotools.readthedocs.io} and 
+\citet{hearin_etal16} for further details.
 
 \subsubsection{Simulation}
+
 All of our analyses are based on the Bolshioi-Planck simulation \citep{riebe_etal11}. 
-Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ and with a box size of $250$ ${\rm Mpc}/h$ and a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.
+Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ within a cubic box
+$250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ 
+Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.
 
-We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}.
-In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius density contrast given in \citet{bryan_norman98}.
-When populating this catalog with mock galaxies, we only use present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.
+We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter 
+halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}.
+In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot
+of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius 
+density contrast given in \citet{bryan_norman98}. When populating this catalog with mock galaxies, we only use 
+present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.
 
@@
 
-In standard HOD models, there are two types of galaxies: centrals and satellites.
-The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively.
-$P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo has only either zero or one central galaxy.
-So occupation statistics of central galaxies are specified by the first moment of $P(\ncen|\mvir)$, which we model as
-
+In standard HOD models, central galaxies and satellite galaxies are treated separately, so 
+the model is specified by two probability distributions, one for each type of galaxy. 
+The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ 
+the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, 
+respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo has only 
+either zero or one central galaxy. Consequently, the occupation statistics of central galaxies are 
+specified by the first moment of $P(\ncen|\mvir)$, which we model as 
+%
 \begin{equation}
@@
         \frac{1}{2}\left( 1 +
-        \mathrm{erf}\left( \frac{\log_{10}\mvir -
-        \log_{10}M_{\rm min}}{\sigma_{\log_{10}M}} \right) \right)
+        \mathrm{erf}\left( \frac{\log (\mvir) -
+        \log (M_{\rm min})}{\sigma_{\log M}} \right) \right)
 \end{equation}
+%
 For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \rangle(\mvir);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(\mvir)$ are left devoid of centrals.
+The parameter $\log (M_{\rm min})$ specifies the halo mass at which the halo has a 50\% probability of hosting a 
+central galaxy, while the parameter $\sigma_{\log M}$ specifies the rate at which $\langle N_{\mathrm{cen}} \rangle (\mvir)$ 
+transitions from zero to unity, with smaller values of $\sigma_{\log M}$ corresponding to a more rapid transition.
 
-We model the distribution $P(\nsat|\mvir)$ to be a Poisson distribution with first moment given by a power law, 
+We model the distribution $P(\nsat|\mvir)$ as a Poisson distribution with first moment given by a power law, 
+%
 \begin{equation}
@@
 \end{equation}
+%
+The parameter $M_0$ allows the power-law to be truncated more rapidly at low masses and we 
+set $\langle N_{\rm sat}\rangle (\mvir) = 0$ for $\mvir < M_0$.
+
+The five parameters of the standard HOD models are varied in standard analyses are $\log (M_{\rm min})$, 
+$\sigma_{\log M}$, $\alpha$, $\log (M_1)$, and $\log (M_0)$, though, as we show below, central galaxies usually 
+outnumber satellite galaxies in by a factor of several, so $\log (M_{\rm min})$ and $\sigma_{\log M}$ usually 
+vary along a narrow degeneracy that fixes the total galaxy number density to the observed value. There are 
+many particular choices that can be made for the functional forms of $\langle N_{\rm cen}\rangle (\mvir)$ and 
+$\langle N_{\rm sat}\rangle (\mvir)$. We have made choices that mimic the standard SDSS DR7 analysis of 
+\citet{zehavi_etal11}, to expedite comparisons with their results.
 
@@
 
-Central galaxies in the standard HOD models reside at the halo center, moving with the same velocity as the host halo peculiar velocity.
-We model the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ of the halo center, with a spherically symmetric NFW profile \citep{nfw97}.
-The concentration $c$ of each halo's satellite galaxy profile is taken to be the same as the concentration of the dark matter particles in the halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, because halos with very large values for the concentration tend to be poorly described by an NFW profile, for example due to a recent merger.}
+Central galaxies in the standard HOD models reside at the halo center, 
+moving with the same velocity as the host halo peculiar velocity. We model 
+the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ 
+of the halo center, with a spherically symmetric NFW profile \citep{nfw97}. 
+The concentration $c$ of each halo's satellite galaxy profile is taken to be 
+the same as the concentration of the dark matter particles in the 
+halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, 
+because halos with very large values for the concentration tend to be poorly 
+described by an NFW profile, for example due to a recent merger.}
 
-We model the velocities of satellite galaxies to be a Gaussian whose first moment is the host halo velocity and whose second moment is the solution to the isotropic Jeans equation for an NFW profile \citep{more09b},
+We model the velocities of satellite galaxies as a Gaussian whose 
+first moment is the host halo velocity and whose second moment is the 
+solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
 \begin{equation}
@@
 where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$ 
+In this way, we model the influence of redshift-space distortions on our predicted 
+two-point functions.
 
@@
 
-Short summary of \citet{hearin_etal16}.
+In addition to the standard occupation statistics described in the previous section, 
+in this paper we also use the decorated HOD formalism to connect galaxies t
+o dark matter halos in a manner that has simultaneous dependence on both $\mvir$ and halo concentration. 
+Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our ``baseline" first occupation moments. 
+At fixed $\mvir,$ halos are divided into one of two categories, those of high- and low-concentration, 
+depending on whether the concentration of the halo places it above or below the rank-order percentile 
+$f_{\rm split},$ which we keep fixed to $f_{\rm split}=0.5$ throughout the paper for simplicity. 
+High-concentration halos have a different first occupation moment relative to low-concentration 
+halos of the same mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq \langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the first moment of high- and low-concentration halos is modulated by $\abias,$ the novel parameter of the decorated HOD governing assembly bias.
+Values of $\abias=\pm1$ correspond to the maximum strength of assembly bias allowable by the constraint that the model preserves the marginalized first moment, $\langle\ngal|\mvir\rangle;$ thus regardless of the value of $\abias,$ in the decorated HOD the marginalized first moment of centrals and satellites are {\em unchanged from the baseline value defined by Equations \ref{eq:ncen} and \ref{eq:nsat}}.
+Decorated HOD models all have the same HODs, when averaged over all halos at fixed mass, as standard HOD models. The only 
+change in Decorated HOD models is whether or not an additional property also modulates halo occupation at fixed halo mass. A 
+value of $\abias = 0$ indicates no galaxy assembly bias whatsoever. We refer the reader to \citet{hearin_etal16} for 
+further details about the decorated HOD.
+
+In the present work, we fix our model to the simplest class of galaxy assembly bias models, though a recipe for 
+generalizing to more complicated models can be found in \citet{hearin_etal16}. In particular, we split halos into 
+two populations as specified in the previous paragraph. We then populate halos with satellite galaxies specified 
+by an assembly bias parameter $-1 \le A_{\rm sat} \le 1$ and central galaxies with a distinct assembly bias 
+parameter $-1 \le A_{\rm cen} \le 1$. These two additional parameters are varied in our analyses that include 
+assembly bias, making the number of parameters that vary in these analyses seven. As we show below, 
+these additional parameters are in many instances poorly constrained by clustering data of the quality of 
+SDSS DR7 alone, so exploring more complex models of assembly bias does not yet seem justified.
 

### 2016-06-06 ms.tex
Finished first draft of abstract

--- 2016-06-04 ms.tex
@@
 \newcommand{\rp}{r_{\mathrm{p}}}
-
+\newcommand{\magr}{M_r}
 \bibliographystyle{mn2e}
@@
 %%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+% ARZ: Important points:
+% -supersedes previous analyses even for standard HOD.
+% -cannot rule out assembly bias using galaxy clustering.
+% -some samples favor assembly bias.
 \begin{abstract}
-
-We fit SDSS DR7 data with models that include assembly bias.
-
-Important points:
--supersedes previous analyses even for standard HOD.
--cannot rule out assembly bias using galaxy clustering.
--some samples favor assembly bias.
-
+We constrain the newly-introduced Decorated HOD model using SDSS DR7 measurements of projected galaxy clustering, $\wprp,$ and number density, $n_{\rm d},$ made from r-band luminosity-threshold samples.
+The Decorated HOD is a model for the galaxy--halo connection that augments the traditional Halo Occupation Distribution (HOD) by allowing for the possibility of {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo properties besides virial mass $\mvir$ alone.
+We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples.
+We find no evidence for assembly bias in the $\magr<-21$ sample, and only moderately significant levels of satellite assembly bias at any luminosity.
+Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements.
 \end{abstract}
@@
 
-Short summary of \citet{hearin_etal16}.
+In addition to the standard occupation statistics described in the previous section, in this paper we also use the decorated HOD formalism to connect galaxies to dark matter halos in a manner that has simultaneous dependence on both $\mvir$ and halo concentration.
+Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our ``baseline" first occupation moments.
+At fixed $\mvir,$ halos are divided into one of two categories, those of high- and low-concentration, depending on whether the concentration of the halo places it above or below the rank-order percentile $f_{\rm split},$ which we keep fixed to $f_{\rm split}=0.5$ throughout the paper.
+High-concentration halos have a different first occupation moment relative to low-concentration halos of the same mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq \langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the first moment of high- and low-concentration halos is modulated by $\abias,$ the novel parameter of the decorated HOD governing assembly bias.
+Values of $\abias=\pm1$ correspond to the maximum strength of assembly bias allowable by the constraint that the model preserves the marginalized first moment, $\langle\ngal|\mvir\rangle;$ thus regardless of the value of $\abias,$ in the decorated HOD the marginalized first moment of centrals and satellites are unchanged from the baseline value defined by Equations \ref{eq:ncen} and \ref{eq:nsat}.
+We refer the reader to \citet{hearin_etal16} for further details about the decorated HOD.
 

### 2016-06-06 ms.tex
Minor edits to abstract based on comments from ARZ

@@
 We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples.
-We find no evidence for assembly bias in the $\magr<-21$ sample, and only moderately significant levels of satellite assembly bias at any luminosity.
+Satellite assembly bias only becomes significant for the faintest sample we study, $\magr<-19.$ We find no evidence for assembly bias in the $\magr<-21$ sample.
 Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements.

### 2016-06-06 ms.tex

--- 2016-06-06 ms.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+% ARZ: Important points:
+% -supersedes previous analyses even for standard HOD.
+% -cannot rule out assembly bias using galaxy clustering.
+% -some samples favor assembly bias.
 \begin{abstract}
-
-We fit SDSS DR7 data with models that include assembly bias.
-
-Important points:
-
--supersedes previous analyses even for standard HOD.
-
--cannot rule out assembly bias using galaxy clustering.
-
--some samples favor assembly bias.
-
+We constrain the newly-introduced Decorated HOD model using SDSS DR7 measurements of projected galaxy clustering, $\wprp,$ and number density, $n_{\rm d},$ made from r-band luminosity-threshold samples.
+The Decorated HOD is a model for the galaxy--halo connection that augments the traditional Halo Occupation Distribution (HOD) by allowing for the possibility of {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo properties besides virial mass $\mvir$ alone.
+We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples.
+Satellite assembly bias only becomes significant for the faintest sample we study, $\magr<-19.$ We find no evidence for assembly bias in the $\magr<-21$ sample.
+Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements.
 \end{abstract}

### 2016-06-06 ms.tex
Clarified description of redshift-space distortions

@@
 
-We model the velocities of satellite galaxies as a Gaussian whose 
-first moment is the host halo velocity and whose second moment is the 
+We model the radial velocity distribution of satellite galaxies as a Gaussian with 
+first moment equal to the host halo velocity and second moment equal to the 
 solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
@@
 where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$ 
-In this way, we model the influence of redshift-space distortions on our predicted 
-two-point functions.
+We assume that velocities are isotropic, setting peculiar velocities in the simulation $z$-dimension  
+equal to random draws from the above distribution. We place mock galaxies 
+into redshift-space by replacing each galaxy's $z$-coordinate with $z \rightarrow z + V_{\rm z}/H_0.$
 

### 2016-06-06 ms.tex
Minor improvements to text in section 3.1

@@
 Assembly bias is quantified by the parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary 
-property that we assume to determine the galaxy HOD is halo formation time. $A_{\rm cen,sat}=0$ means that there is no 
-assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that halo formation time is maximally 
-correlated (anticorrelated) with halo formation time. Thus the parameters range over $-1 \le A_{\rm cen,sat} \le 1$. 
-If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then the model used to interpret the data 
+property that we assume to determine the galaxy HOD is halo concentration. $A_{\rm cen,sat}=0$ means that there is no 
+assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that galaxy abundance is maximally 
+correlated (anticorrelated) with halo concentration at fixed $\mvir.$ Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 
+If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified in the table, then the model used to interpret the data 
 does not include assembly bias. In our analyses, quoted parameter values with errors correspond to the median 
@@
 it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
-value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
-that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.
+value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. 
+Therefore, on these intuitive grounds alone it seems likely that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.
 
-We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
+Additionally, we have confirmed with a subset of the authors of \citet{zehavi_etal11} 
 that the number of MCMC samples they included in their analysis was 
@@
 on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
-(Z. Zheng \& I. Zehavi, Private Communication). The analysis of \citet{zehavi_etal11} 
+(Z. Zheng \& I. Zehavi, private communication). The analysis of \citet{zehavi_etal11} 
 used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
@@
 correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
-average and $\alpha$ is the power-law index describing the dependence of average satellite 
-number on halo mass. Increasing $M_1$ decreases the number of satellites in large halos 
-by placing satellites preferentially in halos of larger mass. An increase in $\alpha$ can partly 
+average, and $\alpha$ is the power-law index describing the dependence of average satellite 
+number on halo mass. Increasing $M_1$ {\em decreases} the number of satellites in massive halos 
+by increasing the mass scale where the power law abundance becomes operative. An increase in $\alpha$ can partly 
 compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
-grows with halo mass, leading to a larger number of satellites in high-mass halos.
+grows with halo mass.
 

### 2016-06-06 ms.tex
Added some text to conclusions

@@
 \newcommand{\magr}{M_r}
+
+\newcommand{\bit}{\begin{itemize}}
+\newcommand{\eit}{\end{itemize}}
+\newcommand{\ben}{\begin{enumerate}}
+\newcommand{\een}{\end{enumerate}}
+
 \bibliographystyle{mn2e}
@@
 
+We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering,  $\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}.
+Our work is especially novel in that we provide the first quantitative constraints on assembly bias derived from the Decorated HOD, an extension to the traditional HOD introduced in \citet{hearin_etal16} developed for exactly this purpose.
+We enumerate our most important conclusions below. 
+\ben
+\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
+\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we sample. 
+\een
+As $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, it is likely that further improvements on assembly bias constraints at low-redshift will require additional observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
+
 %------------------------------------------------

### 2016-06-06 ms.tex
Finished first draft of bullet-point summary of conclusions

@@
 %------------------------------------------------
-
-%------------------------------------------------
 \section{Conclusions}
@@
 \item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
-\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we sample. 
+\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we study.
+Both the $\magr<-20, -20.5$ samples prefer relatively strong central galaxy assembly bias, while at lower luminosities, the $\magr<-19$ sample favors satellite assembly bias.
+\item Galaxy assembly bias generally weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $\abias^{\rm cens}=0$ and $\abias^{\rm sats}=0.$ This consistent with the predictions made in \citet{hearin_etal16} on purely theoretical grounds that galaxy assembly bias should generically weaken with increasing galaxy mass.
+\item Our posteriors and best-fit parameters summarized in Table \ref{table:parameters} supersede the values published in \citet{zehavi_etal11}, as direct-mock-population together with the Decorated HOD allows us to account for highly significant systematics that have heretofore been neglected from all HOD fits to SDSS data.
+We note that our findings update the original \citet{zehavi_etal11} results {\em even for our fits in which assembly bias has been fixed to zero}, since the original results derive from unconverged MCMC chains that do not sufficiently sample the HOD model posteriors.
 \een
-As $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, it is likely that further improvements on assembly bias constraints at low-redshift will require additional observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
+We conclude by noting that since $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, it is likely that further improvements on assembly bias constraints at low-redshift will require additional observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
 

### 2016-06-06 ms.tex
Added subsection describing how we predict wp from point data, resolving Issue #7.

@@
 where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$ 
-We assume that velocities are isotropic, setting peculiar velocities in the simulation $z$-dimension  
-equal to random draws from the above distribution. We place mock galaxies 
-into redshift-space by replacing each galaxy's $z$-coordinate with $z \rightarrow z + V_{\rm z}/H_0.$
+We assume that velocities are isotropic, setting the peculiar velocities in each Cartesian direction 
+according to random draws from the above radial velocity distribution.
+
+\subsubsection{Predictions for observables}
+
+After populating a halo catalog with mock galaxies, we calculate the comoving number density of our mock galaxy sample as $n_{\rm g} = N_{\rm gal} / L_{\rm box}^3.$ We apply the distant-observer approximation and use the simulation z-axis as the line-of-sight direction, and the distance between points in the $xy$-plane to define the projected distance $\rp.$ We place mock galaxies into redshift-space by replacing each galaxy's $z$-coordinate with $z \rightarrow z + V_{\rm z}/H_0.$ We count pairs of points in each of our $\rp$ bins, rejecting pairs with $z-$distance exceeding $\pi_{\rm max}=60$ ${\rm Mpc/h.}$ We employ the \citet{landyszalay93} estimator to turn pair counts into a $\wprp$ prediction, as described in detail in {\tt halotools.readthedocs.io}.
 
@@
 Both the $\magr<-20, -20.5$ samples prefer relatively strong central galaxy assembly bias, while at lower luminosities, the $\magr<-19$ sample favors satellite assembly bias.
-\item Galaxy assembly bias generally weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $\abias^{\rm cens}=0$ and $\abias^{\rm sats}=0.$ This consistent with the predictions made in \citet{hearin_etal16} on purely theoretical grounds that galaxy assembly bias should generically weaken with increasing galaxy mass.
+\item Galaxy assembly bias generally weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $\abias^{\rm cens}=0$ and $\abias^{\rm sats}=0.$ This consistent with the well-established result that {\em halo assembly bias} weakens with increasing halo mass over the dynamic range relevant to these galaxy samples \citep[see, e.g., Figure 8 of][and references therein]{hearin_etal16}.
 \item Our posteriors and best-fit parameters summarized in Table \ref{table:parameters} supersede the values published in \citet{zehavi_etal11}, as direct-mock-population together with the Decorated HOD allows us to account for highly significant systematics that have heretofore been neglected from all HOD fits to SDSS data.

### 2016-06-07 ms.tex
more updates to intro and bib-file

--- 2016-06-06 ms.tex
@@
 \newcommand{\mvir}{M_{\rm vir}}
+\newcommand{\vmax}{v_{\rm max}}
 \newcommand{\rvir}{R_{\rm vir}}
@@
 \newcommand{\abias}{\mathcal{A}_{\rm bias}}
+
+%%%%% less than approximate and all that
+
+\def\gtsima{$\; \buildrel > \over \sim \;$}
+\def\ltsima{$\; \buildrel < \over \sim \;$}
+\def\prosima{$\; \buildrel \propto \over \sim \;$}
+\def\gsim{\lower.7ex\hbox{\gtsima}}
+\def\lsim{\lower.7ex\hbox{\ltsima}}
+\def\simgt{\lower.7ex\hbox{\gtsima}}
+\def\simlt{\lower.7ex\hbox{\ltsima}}
+\def\simpr{\lower.7ex\hbox{\prosima}}
+\def\la{\lsim}
+\def\ga{\gsim}
+\def\lta{\la}
+\def\gta{\ga}
 
@@
 \newcommand{\rp}{r_{\mathrm{p}}}
-\newcommand{\magr}{M_r}
-
-\newcommand{\bit}{\begin{itemize}}
-\newcommand{\eit}{\end{itemize}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
 
@@
 {
-Constraints on Assembly Bias from Galaxy Clustering
+Constraints on Assembly Bias from Galaxy Clustering. 
 }
@@
 {Andrew R. Zentner$^{1}$, Andrew P. Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
-Antonio Villareal$^{1}$, Johannes Lange$^{3}$, P. Rogers Nelson$^{4}$, Probably some others of unspecified origin\\ \\
+Antonio Villareal$^{1}$, Johannes U. Lange$^{3}$, P. Rogers Nelson$^{4}$\\ \\
 $^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ARZ: Important points:
-% -supersedes previous analyses even for standard HOD.
-% -cannot rule out assembly bias using galaxy clustering.
-% -some samples favor assembly bias.
+
 \begin{abstract}
-We constrain the newly-introduced Decorated HOD model using SDSS DR7 measurements of projected galaxy clustering, $\wprp,$ and number density, $n_{\rm d},$ made from r-band luminosity-threshold samples.
-The Decorated HOD is a model for the galaxy--halo connection that augments the traditional Halo Occupation Distribution (HOD) by allowing for the possibility of {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo properties besides virial mass $\mvir$ alone.
-We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples.
-Satellite assembly bias only becomes significant for the faintest sample we study, $\magr<-19.$ We find no evidence for assembly bias in the $\magr<-21$ sample.
-Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements.
+
+We fit SDSS DR7 data with models that include assembly bias.
+
+Important points:
+-supersedes previous analyses even for standard HOD.
+-cannot rule out assembly bias using galaxy clustering.
+-some samples favor assembly bias.
+
 \end{abstract}
@@
 
-Halo occupation modeling has frequently 
-been used to interpret large-scale structure measurements and exploit these measurements 
-to constrain galaxy formation models and cosmology \citep[e.g.,][]{yang03,tinker05,zehavi05a,
+For more than a decade, halo occupation modeling has been used to
+interpret large-scale structure measurements and exploit these
+measurements to constrain galaxy formation models and cosmology
+\citep[e.g.,][]{yang03,tinker05,zehavi05a,
   porciani06,vdBosch07,Zheng07,conroy_wechsler09,yang09b,zehavi_etal11,guo_etal11b,
-wake_etal11,yang11a,yang12,leauthaud_etal12,tinker_etal13,cacciato_etal13,
-more_etal13,guo_etal14,zu_mandelbaum15b}. The key assumptions underlying 
-halo occupation modeling are: (1) all galaxies reside in dark matter halos that are biased 
-tracers of the density field; and (2) galaxies occupy halos as a function of halo mass 
-only. It is now well known that halo bias depends upon halo properties other than mass
+  wake_etal11,yang11a,yang12,leauthaud_etal12,rod_puebla12,tinker_etal13,cacciato_etal13,
+  more_etal13,guo_etal14,zu_mandelbaum15b}. The key assumptions
+underlying halo occupation modeling are: (1) all galaxies reside in
+dark matter halos that are biased tracers of the density field; and
+(2) galaxies occupy halos as a function of halo masses only. It is now
+well known that halo bias depends upon halo properties other than mass
 \citep[e.g.][]{gao_etal05,wechsler06,gao_white07,zentner07,dalal_etal08,lacerna11},
-an effect called {\em halo assembly bias}. If galaxies occupy halos as a function of properties 
-that affect halo clustering, other than mass, then standard halo occupation methods will be subject to a 
-systematic error due to {\em galaxy assembly bias}. Several of us have previously shown that 
-this error can be significant in an analysis of galaxy clustering and can bias inferences 
-about many aspects of galaxy evolution \citep{zentner_etal14}. Consequently, we have 
-developed halo occupation models that enable galaxies to occupy halos in a manner 
-that depends upon several halo properties \citep{hearin_etal16}. In this paper, we 
-revisit the interpretation of luminosity-dependent galaxy clustering in the Sloan Digital Sky 
-Survey (SDSS) Data Release 7 (DR7) data, analyzed previously by \citet{zehavi_etal11}, in the context 
-both standard halo occupation models and these new models.
+an effect called halo assembly bias. If galaxies occupy halos as a
+function of properties other than halo mass, then standard halo
+occupation methods will be subject to a systematic error due to galaxy
+assembly bias. Several of us have previously shown that this error can
+be significant in an analysis of galaxy clustering and can bias
+inferences about many aspects of galaxy evolution
+\citep{zentner_etal14}. Consequently, we have developed halo
+occupation models that enable galaxies to occupy halos in a manner
+that depends upon several halo properties \citep{hearin_etal16}.  See
+also \citet{Yao_etalXX} for a similar approach. In this paper, we
+revisit the interpretation of luminosity-dependent galaxy clustering
+in the Sloan Digital Sky Survey (SDSS) Data Release 7 (DR7) data,
+analyzed previously by \citet{zehavi_etal11}, in the context both
+standard halo occupation models and these new models.
 
-Some history here, blah blah blah, Frank loves this stuff. Therefore, I'm sure this part of the introduction 
-will get quite lengthy.
+The ultimate goal of halo occupation modeling is to characterize the
+galaxy-dark matter connection by constraining the probability
+distribution $P(X_{\rm g}|Y_{\rm h})$. Here $X_{\rm g} = {x_1, x_2,
+  ...x_n}$ is a set of $n$ galaxy properties, and $Y_{\rm h} = {y_1,
+  y_2,...,y_m}$ a set of $m$ halo properties. Accurate knowledge of
+this probability distribution yields invaluable insight to the
+processes of galaxy formation, and allows one to make accurate
+predictions for the clustering of galaxies as function of any property
+$x_i$. Most halo occupation studies to date have restricted themselves
+to only one halo property, namely halo mass.  This includes all Halo
+Occupation Distribution (HOD) models, which aim to constrain
+$P(N|\mvir)$, the probability that a halo of mass $M$ contains $N$
+galaxies of some specified properties
+\citep[e.g.,][]{kauffmann_etal97,jing98,benson01,berlind02}, and all
+Conditional Luminosity Function (CLF) models, which aim to constrain
+$\Phi(L|M)$, the luminosity (or stellar mass) function of galaxies in
+haloes of mass $M$ \citep[e.g.,][]{yang03,vdBosch03a,cooray06}. The
+HOD and CLF models are mainly used in combination with the halo model,
+which describes the non-linear matter field in terms of halo building
+blocks \citep[e.g.,][]{seljak00,cooray02}, to predict the clustering
+of galaxies as function of luminosity or stellar mass.  Although
+entirely analytical, and therefore fast, the downside of this method
+is that it is extremely challenging to construct a model that is
+accurate at the few percent level. The main issues are halo exclusion
+\citep[see][]{smith_etal07,vdBosch13}, scale dependence of the
+halo bias \citep[see][]{tinker05}, and the halo assembly bias mentioned
+above.
 
-Our work is important for several reasons. Our work is a re-analysis of the SDSS DR7 data 
-the overcomes shortcomings of previous analyses. In particular, we use direct population of galaxies 
-in a cosmological simulation so that delicate issues present in analytic modeling, such as scale-dependent 
-halo bias, are treated exactly.  The simulation we use is based on the latest Planck cosmological parameters, 
-updating previous work. Furthermore, many important differences between this work and the previous 
-work of \citet{zehavi_etal11} were caused by insufficiently large Monte Carlo Markov Chain (MCMC) sampling 
-by \citet[][Z. Zheng \& I. Zehavi, Private Communication]{zehavi_etal11}. Therefore, our analysis 
-{\em supersedes previous analyses even in the case of standard halo occupation models}.
+These issues are trivially avoided by directly populating dark matter
+haloes in numerical simulations with galaxies. This can be done using
+either a parameterized model for the halo occupation statistics
+\citep[e.g.,][]{Yang_etal04,moster10;behroozi10,behroozi13} or by
+rank-order matching galaxy properties (i.e., luminosity or stellar
+mass) to halo properties (i.e., halo mass). The latter method is known
+as subhalo abundance matching (SHAM).  Although many SHAM studies use
+halo mass as the halo property of choice
+\citep[e.g.,][]{vale_ostriker04,vale_ostriker06,conroy07,conroy_wechsler09},
+a number of studies have used alternative halo properties, such as the
+maximum circular velocity, $\vmax$, or its peak value over the halo's
+history, $V_{\rm peak}$
+\citep[e.g.][]{tasitsiomi_etal04,conroy06,marin_etal08,reddick_etal13}
 
-Furthermore, our work demonstrates explicitly that significant assembly bias in 
-$M_r$-selected samples from SDSS DR7 cannot be ruled out based on a standard 
-analysis of galaxy clustering alone. In fact, we find that the clustering of galaxies in 
-several luminosity threshold samples 
-{\em favors galaxy assembly bias to a degree that is statistically significant}. 
-As suggested by the previous work of \citet{zentner_etal14}, 
-this conclusion could have important consequences for the 
-interpretation of both extant and forthcoming galaxy survey data.
+Since, at fixed halo mass, $\vmax$ is correlated with halo
+concentration, and thus with halo assembly time, the resulting
+occupation models have assembly bias build in
+\citep[see][]{Zentner_etal14}; i.e., at fixed halo mass, galaxy
+properties will be correlated with halo assembly
+time. \citet{lehmann_etal15} took this one step further, and explored
+SHAM models in which the halo property varies between $M$ and $\vmax$
+via a continuously-valued parameter. Using SDSS clustering
+measurements to constrain their model, they conclude that galaxy
+luminosity reveals a significant dependence on halo
+concentration. Since the latter is strongly correlated with halo
+formation time \citep[e.g.,][]{wechsler02,zhao_etal09,ludlow_etal13},
+their conclusions argue for non-zero assembly bias in the galaxy
+population.
 
-Our paper is organized as follows. In Section~\ref{section:methods}, we discuss our implementation 
-of halo occupation models and our assumptions in our parameter inference analysis. We present 
-results for both standard halo occupation analysis and analysis in the context of models with 
-galaxy assembly bias in Section~\ref{section:results}. We summarize our results and draw 
+In addition to these studies that have focussed on constraining the
+relation between a {\it primary} galaxy property (e.g., luminosity or
+stellar mass) and a {\it primary} halo property (e.g., $M$ or
+$\vmax$), there have also been a number of studies that relate
+{\it secondary} galaxy properties (e.g., color or specific star
+formation rate) to a {\it secondary} halo property (e.g., halo
+formation time or concentration). The archetype of these model is the
+`age-matching' model developed by \citet{HW13a}, in which galaxy color
+is rank-order matched, at fixed stellar mass, to some quantity related
+to the assembly history of the galaxy's (sub)halo.
+Paranjape \etal 2015...
+
+Another approach that 
+This was taken one step further by Hearin ccc, who developed an
+extension of SHAM, called age-matching. In age-matching a
+
+Our work is important for several reasons. Our work is a re-analysis
+of the SDSS DR7 data that overcomes shortcomings of previous
+analyses. In particular, we use direct population of galaxies in a
+cosmological simulation so that delicate issues present in analytic
+modeling, such as scale-dependent halo bias, are treated exactly.  The
+simulation we use is based on the latest Planck cosmological
+parameters, updating previous work. Furthermore, many important
+differences between this work and the previous analysis by
+\citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
+Chains used by Zehavi \etal where too small and had therefore not
+converged (Z. Zheng \& I. Zehavi, Private Communication).  Therefore,
+our analysis {\em supersedes previous analyses even in the case of
+  standard halo occupation models}.
+
+Furthermore, our work demonstrates explicitly that significant
+assembly bias in $M_r$-selected samples from SDSS DR7 cannot be ruled
+out based on a standard analysis of galaxy clustering only. In fact,
+in agreement with \citet{lehmann_etal15}, we find that several samples
+{\em favor galaxy assembly bias to a degree that is statistically
+  significant}. As demonstrated by \citet{zentner_etal14}, this
+conclusion could have important consequences for the interpretation of
+both extant and forthcoming data.
+
+Our paper is organized as follows. In Section~\ref{section:methods},
+we discuss our implementation of halo occupation models and our
+assumptions in our parameter inference analysis. We present results
+for both standard halo occupation analysis and analysis in the context
+of models with galaxy assembly bias in
+Section~\ref{section:results}. We summarize our results and draw
 conclusions in Section~\ref{section:conclusions}.
@@
 To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
-We explore halo occupation distribution models (HOD) models in this work 
-\citep[e.g.][]{seljak00,ma_fry00,scoccimarro01a,berlind02}, though other 
-techniques that can be used to interpret such data, such as the conditional luminosity function 
-\citep[CLF, e.g.,][]{yang03,vdBosch13}, exist. In this section, we review the ``standard" HOD 
-model used in the present work which assumes that there is no galaxy assembly bias. We refer to 
-such a model as ``standard" because all HOD analyses of galaxy clustering to date have assumed no 
-galaxy assembly bias. In the following section, we describe 
-the Decorated HOD model described in \citet{hearin_etal16}. In both cases, we will only 
-review the salient features of our methodology briefly; 
-interested readers can always refer to {\tt halotools.readthedocs.io} and 
-\citet{hearin_etal16} for further details.
+In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal16}.
+In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.
 
 \subsubsection{Simulation}
+All of our analyses are based on the Bolshioi-Planck simulation \citep{riebe_etal11}. 
+Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ and with a box size of $250$ ${\rm Mpc}/h$ and a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.
 
-All of our analyses are based on the Bolshioi-Planck simulation \citep{riebe_etal11}. 
-Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ within a cubic box
-$250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ 
-Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.
-
-We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter 
-halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}.
-In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot
-of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius 
-density contrast given in \citet{bryan_norman98}. When populating this catalog with mock galaxies, we only use 
-present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.
+We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}.
+In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius density contrast given in \citet{bryan_norman98}.
+When populating this catalog with mock galaxies, we only use present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.
 
@@
 
-In standard HOD models, central galaxies and satellite galaxies are treated separately, so 
-the model is specified by two probability distributions, one for each type of galaxy. 
-The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ 
-the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, 
-respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo has only 
-either zero or one central galaxy. Consequently, the occupation statistics of central galaxies are 
-specified by the first moment of $P(\ncen|\mvir)$, which we model as 
-%
+In standard HOD models, there are two types of galaxies: centrals and satellites.
+The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively.
+$P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo has only either zero or one central galaxy.
+So occupation statistics of central galaxies are specified by the first moment of $P(\ncen|\mvir)$, which we model as
+
 \begin{equation}
@@
         \frac{1}{2}\left( 1 +
-        \mathrm{erf}\left( \frac{\log (\mvir) -
-        \log (M_{\rm min})}{\sigma_{\log M}} \right) \right)
+        \mathrm{erf}\left( \frac{\log_{10}\mvir -
+        \log_{10}M_{\rm min}}{\sigma_{\log_{10}M}} \right) \right)
 \end{equation}
-%
 For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \rangle(\mvir);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(\mvir)$ are left devoid of centrals.
-The parameter $\log (M_{\rm min})$ specifies the halo mass at which the halo has a 50\% probability of hosting a 
-central galaxy, while the parameter $\sigma_{\log M}$ specifies the rate at which $\langle N_{\mathrm{cen}} \rangle (\mvir)$ 
-transitions from zero to unity, with smaller values of $\sigma_{\log M}$ corresponding to a more rapid transition.
 
-We model the distribution $P(\nsat|\mvir)$ as a Poisson distribution with first moment given by a power law, 
-%
+We model the distribution $P(\nsat|\mvir)$ to be a Poisson distribution with first moment given by a power law, 
 \begin{equation}
@@
 \end{equation}
-%
-The parameter $M_0$ allows the power-law to be truncated more rapidly at low masses and we 
-set $\langle N_{\rm sat}\rangle (\mvir) = 0$ for $\mvir < M_0$.
-
-The five parameters of the standard HOD models are varied in standard analyses are $\log (M_{\rm min})$, 
-$\sigma_{\log M}$, $\alpha$, $\log (M_1)$, and $\log (M_0)$, though, as we show below, central galaxies usually 
-outnumber satellite galaxies in by a factor of several, so $\log (M_{\rm min})$ and $\sigma_{\log M}$ usually 
-vary along a narrow degeneracy that fixes the total galaxy number density to the observed value. There are 
-many particular choices that can be made for the functional forms of $\langle N_{\rm cen}\rangle (\mvir)$ and 
-$\langle N_{\rm sat}\rangle (\mvir)$. We have made choices that mimic the standard SDSS DR7 analysis of 
-\citet{zehavi_etal11}, to expedite comparisons with their results.
 
@@
 
-Central galaxies in the standard HOD models reside at the halo center, 
-moving with the same velocity as the host halo peculiar velocity. We model 
-the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ 
-of the halo center, with a spherically symmetric NFW profile \citep{nfw97}. 
-The concentration $c$ of each halo's satellite galaxy profile is taken to be 
-the same as the concentration of the dark matter particles in the 
-halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, 
-because halos with very large values for the concentration tend to be poorly 
-described by an NFW profile, for example due to a recent merger.}
+Central galaxies in the standard HOD models reside at the halo center, moving with the same velocity as the host halo peculiar velocity.
+We model the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ of the halo center, with a spherically symmetric NFW profile \citep{nfw97}.
+The concentration $c$ of each halo's satellite galaxy profile is taken to be the same as the concentration of the dark matter particles in the halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, because halos with very large values for the concentration tend to be poorly described by an NFW profile, for example due to a recent merger.}
 
-We model the radial velocity distribution of satellite galaxies as a Gaussian with 
-first moment equal to the host halo velocity and second moment equal to the 
-solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
+We model the velocities of satellite galaxies to be a Gaussian whose first moment is the host halo velocity and whose second moment is the solution to the isotropic Jeans equation for an NFW profile \citep{more09b},
 \begin{equation}
@@
 where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$
-We assume that velocities are isotropic, setting peculiar velocities in the simulation $z$-dimension  
-equal to random draws from the above distribution. We place mock galaxies 
-into redshift-space by replacing each galaxy's $z$-coordinate with $z \rightarrow z + V_{\rm z}/H_0.$
 
@@
 
-In addition to the standard occupation statistics described in the previous section, 
-in this paper we also use the decorated HOD formalism to connect galaxies t
-o dark matter halos in a manner that has simultaneous dependence on both $\mvir$ and halo concentration. 
-Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our ``baseline" first occupation moments. 
-At fixed $\mvir,$ halos are divided into one of two categories, those of high- and low-concentration, 
-depending on whether the concentration of the halo places it above or below the rank-order percentile 
-$f_{\rm split},$ which we keep fixed to $f_{\rm split}=0.5$ throughout the paper for simplicity. 
-High-concentration halos have a different first occupation moment relative to low-concentration 
-halos of the same mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq \langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the first moment of high- and low-concentration halos is modulated by $\abias,$ the novel parameter of the decorated HOD governing assembly bias.
-Values of $\abias=\pm1$ correspond to the maximum strength of assembly bias allowable by the constraint that the model preserves the marginalized first moment, $\langle\ngal|\mvir\rangle;$ thus regardless of the value of $\abias,$ in the decorated HOD the marginalized first moment of centrals and satellites are {\em unchanged from the baseline value defined by Equations \ref{eq:ncen} and \ref{eq:nsat}}.
-Decorated HOD models all have the same HODs, when averaged over all halos at fixed mass, as standard HOD models. The only 
-change in Decorated HOD models is whether or not an additional property also modulates halo occupation at fixed halo mass. A 
-value of $\abias = 0$ indicates no galaxy assembly bias whatsoever. We refer the reader to \citet{hearin_etal16} for 
-further details about the decorated HOD.
-
-In the present work, we fix our model to the simplest class of galaxy assembly bias models, though a recipe for 
-generalizing to more complicated models can be found in \citet{hearin_etal16}. In particular, we split halos into 
-two populations as specified in the previous paragraph. We then populate halos with satellite galaxies specified 
-by an assembly bias parameter $-1 \le A_{\rm sat} \le 1$ and central galaxies with a distinct assembly bias 
-parameter $-1 \le A_{\rm cen} \le 1$. These two additional parameters are varied in our analyses that include 
-assembly bias, making the number of parameters that vary in these analyses seven. As we show below, 
-these additional parameters are in many instances poorly constrained by clustering data of the quality of 
-SDSS DR7 alone, so exploring more complex models of assembly bias does not yet seem justified.
+In addition to the standard occupation statistics described in the
+previous section, in this paper we also use the decorated HOD
+formalism to connect galaxies to dark matter halos in a manner that
+has simultaneous dependence on both $\mvir$ and halo
+concentration. Briefly, we use Equations \ref{eq:ncen} and
+\ref{eq:nsat} as our ``baseline" first occupation moments. At fixed
+$\mvir,$ halos are divided into one of two categories, those of high-
+and low-concentration, depending on whether the concentration of the
+halo places it above or below the rank-order percentile $f_{\rm
+  split},$ which we keep fixed to $f_{\rm split}=0.5$ throughout the
+paper. High-concentration halos have a different first occupation
+moment relative to low-concentration halos of the same mass,
+$\langle\ngal|\mvir, c_{\rm high}\rangle \neq \langle\ngal|\mvir,
+c_{\rm low}\rangle.$ The difference between the first moment of high-
+and low-concentration halos is modulated by $\abias,$ the novel
+parameter of the decorated HOD governing assembly bias. Values of
+$\abias=\pm1$ correspond to the maximum strength of assembly bias
+allowable by the constraint that the model preserves the marginalized
+first moment, $\langle\ngal|\mvir\rangle;$ thus regardless of the
+value of $\abias,$ in the decorated HOD the marginalized first moment
+of centrals and satellites are unchanged from the baseline value
+defined by Equations \ref{eq:ncen} and \ref{eq:nsat}. We refer the
+reader to \citet{hearin_etal16} for further details about the
+decorated HOD.
 
@@
 Assembly bias is quantified by the parameters $A_{\rm cen}$ ($A_{\rm sat}$) for central (satellite) galaxies. The secondary 
-property that we assume to determine the galaxy HOD is halo concentration. $A_{\rm cen,sat}=0$ means that there is no 
-assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that galaxy abundance is maximally 
-correlated (anticorrelated) with halo concentration at fixed $\mvir.$ Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 
-If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified in the table, then the model used to interpret the data 
+property that we assume to determine the galaxy HOD is halo formation time. $A_{\rm cen,sat}=0$ means that there is no 
+assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that halo formation time is maximally 
+correlated (anticorrelated) with halo formation time. Thus the parameters range over $-1 \le A_{\rm cen,sat} \le 1$. 
+If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified, then the model used to interpret the data 
 does not include assembly bias. In our analyses, quoted parameter values with errors correspond to the median 
@@
 
-A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
-find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
-we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
-\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
-with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
-$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
-results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
-\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
-$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
-it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
-value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. 
-Therefore, on these intuitive grounds alone it seems likely that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.
+A second noteworthy difference between the present work and that of
+\citet{zehavi_etal11} is that we find many parameters to be notably
+more poorly constrained. At the lower luminosity thresholds, for
+example, we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with
+several times lower precision than \citet{zehavi_etal11}. We do not
+show our constraints on $\log (M_0)$ as they are very poor, with
+1-sigma constraints $\gta 1$~dex for all samples. In several cases,
+the constraint on $\log (M_0)$ is determined by the prior given in
+Table~\ref{table:priors}. This is in stark contrast to several of the
+results of \citet{zehavi_etal11}. For example, for the threshold
+sample with $M_r < -19.5$ ($M_r < -20.5$), \citet{zehavi_etal11} quote
+$\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer
+$\log (M_0) = 11.38^{+0.95}_{-1.57}$
+($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}),
+it is sensible that the parameter $\log (M_0)$ should be unconstrained
+at the lower end, because the value of $M_0$ does not alter the
+predicted satellite number once $M_0 \ll M_1$. Therefore, it seems
+likely that the tighter constraints quoted by \citet{zehavi_etal11}
+must be an error.
 
-Additionally, we have confirmed with a subset of the authors of \citet{zehavi_etal11} 
+We have confirmed with a subset of the authors of \citet{zehavi_etal11} 
 that the number of MCMC samples they included in their analysis was 
@@
 on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
-(Z. Zheng \& I. Zehavi, private communication). The analysis of \citet{zehavi_etal11} 
+(Z. Zheng \& I. Zehavi, Private Communication). The analysis of \citet{zehavi_etal11} 
 used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
@@
 correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 
-average, and $\alpha$ is the power-law index describing the dependence of average satellite 
-number on halo mass. Increasing $M_1$ {\em decreases} the number of satellites in massive halos 
-by increasing the mass scale where the power law abundance becomes operative. An increase in $\alpha$ can partly 
+average and $\alpha$ is the power-law index describing the dependence of average satellite 
+number on halo mass. Increasing $M_1$ decreases the number of satellites in large halos 
+by placing satellites preferentially in halos of larger mass. An increase in $\alpha$ can partly 
 compensate for an increase in $M_1$ by increasing the rate at which average satellite number 
-grows with halo mass.
+grows with halo mass, leading to a larger number of satellites in high-mass halos.
 
@@
 \includegraphics[width=15.0cm]{Mr19ABTri.pdf}
-\caption{
-Two-dimensional marginalized constraints on decorated HOD parameters inferred from fits 
-to $\wprp(\rp)$ data for the $M_r<-19$ sample. The contours and histograms along the diagonal 
-panels are as in Fig.~\ref{fig:Mr20triangle}. The decorated HOD models include a 
-two-parameter model for assembly bias. The HOD parameter $\log (M_0)$ is extremely 
-poorly constrained by the data and has been suppressed for clarity. Likewise, as in 
-Fig.~\ref{fig:Mr20triangle}, $\sigma_{\log M}$ and $\log (M_{\rm min})$ share a 
-narrow degeneracy, so we have suppressed $\sigma_{\log M}$ in order to make 
-constraints on other parameters more easily visible.
-}
+\caption{ Two-dimensional marginalized constraints on decorated HOD
+  parameters inferred from fits to $\wprp(\rp)$ data for the $M_r<-19$
+  sample. The contours and histograms along the diagonal panels are as
+  in Fig.~\ref{fig:Mr20triangle}. The decorated HOD models include a
+  two-parameter model for assembly bias. The HOD parameter $\log
+  (M_0)$ is extremely poorly constrained by the data and has been
+  suppressed for clarity. Likewise, as in Fig.~\ref{fig:Mr20triangle},
+  $\sigma_{\log M}$ and $\log (M_{\rm min})$ share a narrow
+  degeneracy, so we have suppressed $\sigma_{\log M}$ in order to make
+  constraints on other parameters more easily visible.  }
 \label{fig:Mr19ABtriangle}
@@
 
-We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering,  $\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}.
-Our work is especially novel in that we provide the first quantitative constraints on assembly bias derived from the Decorated HOD, an extension to the traditional HOD introduced in \citet{hearin_etal16} developed for exactly this purpose.
-We enumerate our most important conclusions below. 
-\ben
-\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
-\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we sample. 
-\een
-As $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, it is likely that further improvements on assembly bias constraints at low-redshift will require additional observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
-
 %------------------------------------------------
@@
 
-The authors gratefully acknowledge the Gauss Centre for Supercomputing e.V.
-(www.gauss-centre.eu) and the Partnership for Advanced Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the MultiDark simulation project by providing computing time on the GCS Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ, www.lrz.de).
-The Bolshoi simulations have been performed within the Bolshoi project of the University of California High-Performance AstroComputing Center (UC-HiPACC) and were run at the NASA Ames Research Center.
+The authors gratefully acknowledge the Gauss Centre for Supercomputing
+e.V. (www.gauss-centre.eu) and the Partnership for Advanced
+Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the
+MultiDark simulation project by providing computing time on the GCS
+Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ,
+www.lrz.de). The Bolshoi simulations have been performed within the
+Bolshoi project of the University of California High-Performance
+AstroComputing Center (UC-HiPACC) and were run at the NASA Ames
+Research Center. FvdB is supported by the US National Science
+Foundation through grant AST 1516962. {\bf AZ; add yours as well.}
 

### 2016-06-07 ms.tex
more updates to intro and bib-file

--- 2016-06-06 ms.tex
@@
 
-A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
-find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
-we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
-\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
-with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
-$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
-results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
-\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
-$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
-it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
-value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. 
-Therefore, on these intuitive grounds alone it seems likely that the tighter constraints quoted by \citet{zehavi_etal11} must be an error.
+A second noteworthy difference between the present work and that of
+\citet{zehavi_etal11} is that we find many parameters to be notably
+more poorly constrained. At the lower luminosity thresholds, for
+example, we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with
+several times lower precision than \citet{zehavi_etal11}. We do not
+show our constraints on $\log (M_0)$ as they are very poor, with
+1-sigma constraints $\gta 1$~dex for all samples. In several cases,
+the constraint on $\log (M_0)$ is determined by the prior given in
+Table~\ref{table:priors}. This is in stark contrast to several of the
+results of \citet{zehavi_etal11}. For example, for the threshold
+sample with $M_r < -19.5$ ($M_r < -20.5$), \citet{zehavi_etal11} quote
+$\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer
+$\log (M_0) = 11.38^{+0.95}_{-1.57}$
+($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}),
+it is sensible that the parameter $\log (M_0)$ should be unconstrained
+at the lower end, because the value of $M_0$ does not alter the
+predicted satellite number once $M_0 \ll M_1$. Therefore, it seems
+likely that the tighter constraints quoted by \citet{zehavi_etal11}
+must be an error.
 

### 2016-06-07 ms.tex
and yet more
this time describing observational evidence for assembly bias

--- 2016-06-07 ms.tex
@@
   y_2,...,y_m}$ a set of $m$ halo properties. Accurate knowledge of
-this probability distribution yields invaluable insight to the
+this probability distribution yields invaluable insight regarding the
 processes of galaxy formation, and allows one to make accurate
@@
 $x_i$. Most halo occupation studies to date have restricted themselves
-to only one halo property, namely halo mass.  This includes all Halo
+to only one halo property, namely halo mass.  This includes Halo
 Occupation Distribution (HOD) models, which aim to constrain
@@
 galaxies of some specified properties
-\citep[e.g.,][]{kauffmann_etal97,jing98,benson01,berlind02}, and all
+\citep[e.g.,][]{kauffmann_etal97,jing98,benson01,berlind02}, and
 Conditional Luminosity Function (CLF) models, which aim to constrain
@@
 accurate at the few percent level. The main issues are halo exclusion
-\citep[see][]{smith_etal07,vdBosch13}, scale dependence of the
-halo bias \citep[see][]{tinker05}, and the halo assembly bias mentioned
+\citep[see][]{smith_etal07,vdBosch13}, scale dependence of the halo
+bias \citep[see][]{tinker05}, and the halo assembly bias mentioned
 above.
@@
 population.
+
+Additional support for the presence of assembly bias has come from a
+variety of studies that have shown, or suggested, that the large-scale
+environment (i.e., clustering strength) of dark matter haloes {\it of
+  fixed mass} is correlated with the star formation rate of their
+central
+galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
+However, a recent study by \citet{lin_mandelbaum_etal15} argues that
+most of the these differences in clustering strength can be explained
+as due to differences in halo mass or contamination by satellite
+galaxies. \citet{lin_mandelbaum_etal15} therefore argue that there is
+no significant evidence for assembly bias in galaxy-scale halos
+\citep[see also][]{paranjape15}.
+
+\citet{yang_etal06a}, who showed that the clustering strength of
+galaxy groups (i.e., dark matter haloes) of fixed mass is correlated
+with the star formation rate of their central galaxy. Similar
+conclusions have been reached by a number of independent
+studies\citep[][]{blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,hearin_etal14}. However,
+\citet{lin_mandelbaum_etal15} have argued that these differences in
+clustering strength can all be explained as due to differences in halo
+mass or contamination by satellite galaxies and concluded that there
+is no significant evidence for assembly bias in galaxy-scale halos
+\citep[see also][]{paranjape15}.
+
+In addition, Hearin etal have argued that the large-scale conformity
+in galaxy star formation rates observed by Kauffmann etal is another
+`smoking-gun' signature of assembly bias (but see Parajape etal 2015).
+
+halos with quenched centrals are
+more strongly clustered than halos of the same mass that host star
+forming centrals \citep[see
+  also][]{blanton_berlind07,wang_etal08,wang_etal13}
+
+Using galaxy-group cross correlations, Ref. [61] has shown that halos
+with quenched centrals are more strongly clustered than halos of the
+same mass that host star forming centrals. This first observational
+evidence for galaxy assembly bias has been confirmed using larger data
+sets [62, 63]. F
+
+Further evidence for assembly bias from group catalogs
+has come from Ref. [64], who found that the color/SFR of satellite
+galaxies depend on the color/SFR of the group’s central galaxy, again
+at fixed halo mass, a phenomenon dubbed galactic conformity.  More
+recently, Ref. [65] demonstrated that correlations between the SFRs of
+central galaxies and their neighboring galaxies persist out to many
+Mpc, far beyond the virial radii of their host halos.  Quenched
+central galaxies preferentially reside in large-scale environments
+replete with quenched galaxies. Both these conformity signals indicate
+manifest violations of the Mass-Only ansatz [66].  A different
+approach was taken by Ref. [67], who shuffled the colors and
+luminosities of galaxies in groups of similar mass, preserving for
+each galaxy its group-centric distance. This procedure preserves the
+halo occupation N|Mh, but erases the relationship between the
+galaxies and the larger-scale environments of the groups in which they
+reside. The Mass-Only ansatz predicts that the real and shuffled group
+catalogs should reveal identical clustering. Contrarily, the
+clustering in the two catalogs differ at the ∼ 5% (∼ 10%) level on
+scales larger
+                                     % (smaller) than ∼ 1 h
 

### 2016-06-07 ms.tex
additional changes in intro
Still need to add some sentences promoting a
smooth transition between what I wrote and what Andrew wrote…..

--- 2016-06-07 ms.tex
@@
 galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
-However, a recent study by \citet{lin_mandelbaum_etal15} argues that
-most of the these differences in clustering strength can be explained
-as due to differences in halo mass or contamination by satellite
-galaxies. \citet{lin_mandelbaum_etal15} therefore argue that there is
-no significant evidence for assembly bias in galaxy-scale halos
-\citep[see also][]{paranjape15}.
-
-\citet{yang_etal06a}, who showed that the clustering strength of
-galaxy groups (i.e., dark matter haloes) of fixed mass is correlated
-with the star formation rate of their central galaxy. Similar
-conclusions have been reached by a number of independent
-studies\citep[][]{blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,hearin_etal14}. However,
-\citet{lin_mandelbaum_etal15} have argued that these differences in
-clustering strength can all be explained as due to differences in halo
-mass or contamination by satellite galaxies and concluded that there
-is no significant evidence for assembly bias in galaxy-scale halos
-\citep[see also][]{paranjape15}.
-
-In addition, Hearin etal have argued that the large-scale conformity
-in galaxy star formation rates observed by Kauffmann etal is another
-`smoking-gun' signature of assembly bias (but see Parajape etal 2015).
-
-halos with quenched centrals are
-more strongly clustered than halos of the same mass that host star
-forming centrals \citep[see
-  also][]{blanton_berlind07,wang_etal08,wang_etal13}
-
-Using galaxy-group cross correlations, Ref. [61] has shown that halos
-with quenched centrals are more strongly clustered than halos of the
-same mass that host star forming centrals. This first observational
-evidence for galaxy assembly bias has been confirmed using larger data
-sets [62, 63]. F
-
-Further evidence for assembly bias from group catalogs
-has come from Ref. [64], who found that the color/SFR of satellite
-galaxies depend on the color/SFR of the group’s central galaxy, again
-at fixed halo mass, a phenomenon dubbed galactic conformity.  More
-recently, Ref. [65] demonstrated that correlations between the SFRs of
-central galaxies and their neighboring galaxies persist out to many
-Mpc, far beyond the virial radii of their host halos.  Quenched
-central galaxies preferentially reside in large-scale environments
-replete with quenched galaxies. Both these conformity signals indicate
-manifest violations of the Mass-Only ansatz [66].  A different
-approach was taken by Ref. [67], who shuffled the colors and
-luminosities of galaxies in groups of similar mass, preserving for
-each galaxy its group-centric distance. This procedure preserves the
-halo occupation N|Mh, but erases the relationship between the
-galaxies and the larger-scale environments of the groups in which they
-reside. The Mass-Only ansatz predicts that the real and shuffled group
-catalogs should reveal identical clustering. Contrarily, the
-clustering in the two catalogs differ at the ∼ 5% (∼ 10%) level on
-scales larger
-                                     % (smaller) than ∼ 1 h
-
-In addition to these studies that have focussed on constraining the
-relation between a {\it primary} galaxy property (e.g., luminosity or
-stellar mass) and a {\it primary} halo property (e.g., $M$ or
-$\vmax$), there have also been a number of studies that relate
-{\it secondary} galaxy properties (e.g., color or specific star
-formation rate) to a {\it secondary} halo property (e.g., halo
-formation time or concentration). The archetype of these model is the
-`age-matching' model developed by \citet{HW13a}, in which galaxy color
-is rank-order matched, at fixed stellar mass, to some quantity related
-to the assembly history of the galaxy's (sub)halo.
-Paranjape \etal 2015...
-
-Another approach that 
-This was taken one step further by Hearin ccc, who developed an
-extension of SHAM, called age-matching. In age-matching a
+However, \citet{lin_mandelbaum_etal15} claim that most of the these
+differences in clustering strength can be explained as due to
+differences in halo mass or contamination by satellite galaxies, and
+therefore argue that there is no significant evidence for assembly
+bias in galaxy-scale halos \citep[see also][]{paranjape15}.  On the
+other hand, \citet{miyatake_etal15} and \citet{more_etal16} recently
+presented strong evidence for the presence of assembly bias in massive
+clusters; in particular, they find that clusters with a more
+concentrated distribution of satellite galaxies are less strongly
+clustered than their equal-mass counterparts whose satellite galaxies
+are less centrally concentrated. To summarize, while there is strong
+evidence for the presence of assembly bias on the scale of clusters,
+there is not concensus yet as to whether assembly bias plays also a
+role in less massive haloes.
 

### 2016-06-07 calculate_hods_from_chains.py
Finished first draft of command-line script for calculating HODs by sampling the best-fit chains provided by @andrew-zentner and then repeatedly populating mocks. The results are output to an hdf5 file that is now also part of the repo. These hdf5 files can be used to make the plots suggested by @vdbosch69 in Issue #11

@@ -1,0 +1,192 @@
+#!/usr/bin/env python
+""" This script is executable from the command-line and can be used to generate
+the plot of our best-fit HODs.
+"""
+import argparse
+import os
+import numpy as np
+from astropy.table import Table
+from halotools.empirical_models import (AssembiasZheng07Cens,
+        AssembiasZheng07Sats, TrivialPhaseSpace, NFWPhaseSpace, HodModelFactory)
+from halotools.empirical_models import PrebuiltHodModelFactory
+from halotools.sim_manager import CachedHaloCatalog
+import h5py
+
+# Determine the directory where the chain files are stored
+parser = argparse.ArgumentParser()
+parser.add_argument("chain_dirname", type=str,
+    help="Absolute path to the directory containing the hdf5 files storing the chains")
+parser.add_argument("-num_iterations", type=int, default=50,
+    help="Number of times to repeatedly populate mocks to calculate the HOD."
+    "Default is 50.")
+parser.add_argument("-min_mass", type=int, default=11.5,
+    help="Minimum mass to use in the logarithmically spaced mass bins used to calculate the HOD. "
+    "Default is 11.5")
+parser.add_argument("-max_mass", type=int, default=14.5,
+    help="Minimum mass to use in the logarithmically spaced mass bins used to calculate the HOD. "
+    "Default is 14.5")
+parser.add_argument("-num_mass_bins", type=int, default=20,
+    help="Number of logarithmically-spaced mass bins used to calculate the HOD. "
+    "Default is 20")
+parser.add_argument("-output_dirname", type=str, default='./',
+    help="Directory where astropy tables storing the tabulated HODs will be stored. "
+    "Default is the directory where the script is located.")
+
+args = parser.parse_args()
+chain_dirname = os.path.abspath(args.chain_dirname)
+num_iterations = args.num_iterations
+min_mass = args.min_mass
+max_mass = args.max_mass
+num_mass_bins = args.num_mass_bins
+output_dirname = os.path.abspath(args.output_dirname)
+
+mass_bins = np.logspace(min_mass, max_mass, num_mass_bins)
+mass_bin_midpoints = (mass_bins[1:] + mass_bins[:-1])/2.
+################################################################################
[…]

### 2016-06-08 calculate_hods_from_chains.py
Fixed bug in calculation of HOD from mock. Needed to recast the output of  as a float array before dividing the galaxy counts by it. CC @andrew-zentner

@@ -71,20 +71,17 @@ def retrieve_random_param_dict(chain, delta_chi2_cutoff=1):
     idx_chi2_cuotff = np.searchsorted(chain['chi2'].data, chain['chi2'][0]+delta_chi2_cutoff)
     idx_random = np.random.randint(0, idx_chi2_cuotff)
     assert chain['chi2'][idx_random] <= chain['chi2'].min() + 1
-
     d = {}
     d['logMmin'] = chain['logMmin'][idx_random]
     d['logM0'] = chain['logM0'][idx_random]
     d['sigma_logM'] = chain['sigmalogM'][idx_random]
     d['logM1'] = chain['logM1'][idx_random]
     d['alpha'] = chain['alpha'][idx_random]
-
     try:
         d['mean_occupation_centrals_assembias_param1'] = chain['Acen'][idx_random]
         d['mean_occupation_satellites_assembias_param1'] = chain['Asat'][idx_random]
     except KeyError:
         pass
-
     return d
 
 
@@ -125,15 +122,15 @@ np.seterr(divide='ignore', invalid='ignore')  # ignore divide by zero in e.g. DD
 
 
 def calculate_hod(halo_table, galaxy_table):
-    halo_counts = np.histogram(halo_table['halo_mvir'].data, mass_bins)[0]
+    halo_counts = np.histogram(halo_table['halo_mvir'].data, mass_bins)[0].astype('f4')
 
     central_mask = galaxy_table['gal_type'] == 'centrals'
     central_counts = np.histogram(galaxy_table['halo_mvir'][central_mask].data,
-        mass_bins)[0]
+        mass_bins)[0].astype('f4')
 
     satellite_mask = galaxy_table['gal_type'] == 'satellites'
     satellite_counts = np.histogram(galaxy_table['halo_mvir'][satellite_mask].data,
-        mass_bins)[0]
+        mass_bins)[0].astype('f4')
 
     return mass_bins, central_counts/halo_counts, satellite_counts/halo_counts
 

### 2016-06-08 calculate_hods_from_chains.py
Updated code generating HOD results.

@@ -19,13 +19,13 @@ parser.add_argument("chain_dirname", type=str,
 parser.add_argument("-num_iterations", type=int, default=50,
     help="Number of times to repeatedly populate mocks to calculate the HOD."
     "Default is 50.")
-parser.add_argument("-min_mass", type=int, default=11.5,
+parser.add_argument("-min_mass", type=int, default=11,
     help="Minimum mass to use in the logarithmically spaced mass bins used to calculate the HOD. "
     "Default is 11.5")
-parser.add_argument("-max_mass", type=int, default=14.5,
+parser.add_argument("-max_mass", type=int, default=14.75,
     help="Minimum mass to use in the logarithmically spaced mass bins used to calculate the HOD. "
     "Default is 14.5")
-parser.add_argument("-num_mass_bins", type=int, default=20,
+parser.add_argument("-num_mass_bins", type=int, default=30,
     help="Number of logarithmically-spaced mass bins used to calculate the HOD. "
     "Default is 20")
 parser.add_argument("-output_dirname", type=str, default='./',
@@ -187,3 +187,4 @@ print("...working on calculation of HOD for standard case")
 write_result_to_disk(std_model, wp20_std_chain, output_fname_std)
 print("...working on calculation of HOD for assembly-biased case")
 write_result_to_disk(ab_model, wp20_ab_chain, output_fname_ab)
+print("\a")

### 2016-06-08 ms.tex
Rebased commit on master to resolve conflicts

@@
 \newcommand{\mvir}{M_{\rm vir}}
-\newcommand{\vmax}{v_{\rm max}}
+\newcommand{\vmax}{V_{\rm max}}
 \newcommand{\rvir}{R_{\rm vir}}
@@
 \begin{abstract}
-We constrain the newly-introduced Decorated HOD model using SDSS DR7 measurements of projected galaxy clustering, $\wprp,$ and number density, $n_{\rm d},$ made from r-band luminosity-threshold samples.
-The Decorated HOD is a model for the galaxy--halo connection that augments the traditional Halo Occupation Distribution (HOD) by allowing for the possibility of {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo properties besides virial mass $\mvir$ alone.
-We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples.
-Satellite assembly bias only becomes significant for the faintest sample we study, $\magr<-19.$ We find no evidence for assembly bias in the $\magr<-21$ sample.
-Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements.
+  We constrain the newly-introduced Decorated HOD model using SDSS DR7
+  measurements of projected galaxy clustering, $\wprp,$ and number
+  density, $n_{\rm d},$ made from r-band luminosity-threshold
+  samples. The Decorated HOD is a model for the galaxy--halo
+  connection that augments the traditional Halo Occupation
+  Distribution (HOD) by allowing for the possibility of {\em assembly
+    bias}: galaxy luminosity may be correlated with dark matter halo
+  properties besides virial mass $\mvir$ alone. We demonstrate that it
+  is not possible to rule out assembly bias using DR7 measurements of
+  $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$
+  favor strong levels of central galaxy assembly bias:
+  high-concentration halos are more likely to host a central galaxy
+  relative to low-concentration halos of the same $\mvir.$ We rule out
+  zero assembly bias with high significance for these
+  samples. Satellite assembly bias only becomes significant for the
+  faintest sample we study, $\magr<-19.$ We find no evidence for
+  assembly bias in the $\magr<-21$ sample. Because the Decorated HOD
+  subsumes the traditional HOD, and additionally because of errors
+  made in the original analysis of these samples, our results differ
+  from and supersede existing HOD constraints from low-redshift
+  clustering measurements.
 \end{abstract}
@@
 galaxy-dark matter connection by constraining the probability
-distribution $P(X_{\rm g}|Y_{\rm h})$. Here $X_{\rm g} = {x_1, x_2,
-  ...x_n}$ is a set of $n$ galaxy properties, and $Y_{\rm h} = {y_1,
-  y_2,...,y_m}$ a set of $m$ halo properties. Accurate knowledge of
+distribution $P(X_{\rm g}|Y_{\rm h})$. Here $X_{\rm g} = \{x_1, x_2,
+  ...x_n\}$ is a set of $n$ galaxy properties, and $Y_{\rm h} = \{y_1,
+  y_2,...,y_m\}$ a set of $m$ halo properties. Accurate knowledge of
 this probability distribution yields invaluable insight regarding the
@@
 either a parameterized model for the halo occupation statistics
-\citep[e.g.,][]{Yang_etal04,moster10;behroozi10,behroozi13} or by
+\citep[e.g.,][]{Yang_etal04,moster10,behroozi10,behroozi13} or by
 rank-order matching galaxy properties (i.e., luminosity or stellar
@@
 occupation models have assembly bias build in
-\citep[see][]{Zentner_etal14}; i.e., at fixed halo mass, galaxy
+\citep[see][]{zentner_etal14}; i.e., at fixed halo mass, galaxy
 properties will be correlated with halo assembly
@@
 \citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
-Chains used by Zehavi \etal where too small and had therefore not
-converged (Z. Zheng \& I. Zehavi, Private Communication).  Therefore,
+Chains used by Zehavi et al. were too small and had therefore not
+converged (Z. Zheng \& I. Zehavi, private communication).  Therefore,
 our analysis {\em supersedes previous analyses even in the case of
@@
 Central galaxies in the standard HOD models reside at the halo center,
-moving with the same velocity as the host halo peculiar velocity. We model 
-the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ 
-of the halo center, with a spherically symmetric NFW profile \citep{nfw97}. 
-The concentration $c$ of each halo's satellite galaxy profile is taken to be 
-the same as the concentration of the dark matter particles in the 
-halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, 
-because halos with very large values for the concentration tend to be poorly 
+moving with the same velocity as the host halo peculiar velocity. We
+model the intra-halo spatial distribution of satellite galaxies to be
+located within $\rvir$ of the halo center, with a spherically
+symmetric NFW profile \citep{nfw97}.  The concentration $c$ of each
+halo's satellite galaxy profile is taken to be the same as the
+concentration of the dark matter particles in the halo.\footnote{We
+  set a maximum value of $c=25$ to the NFW concentration, because
+  halos with very large values for the concentration tend to be poorly
   described by an NFW profile, for example due to a recent merger.}
 
-We model the radial velocity distribution of satellite galaxies as a Gaussian with 
-first moment equal to the host halo velocity and second moment equal to the 
-solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
+We model the radial velocity distribution of satellite galaxies as a
+Gaussian with first moment equal to the host halo velocity and second
+moment equal to the solution to the isotropic Jeans equation for an
+NFW profile \citep{more09b},
 \begin{equation}
@@
 \end{equation}
-where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$ 
-We assume that velocities are isotropic, setting the peculiar velocities in each Cartesian direction 
+where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and
+$V_{\rm vir}^{2} = G\mvir/\rvir.$ We assume that velocities are
+isotropic, setting the peculiar velocities in each Cartesian direction
 according to random draws from the above radial velocity distribution.
@@
 
-After populating a halo catalog with mock galaxies, we calculate the comoving number density of our mock galaxy sample as $n_{\rm g} = N_{\rm gal} / L_{\rm box}^3.$ We apply the distant-observer approximation and use the simulation z-axis as the line-of-sight direction, and the distance between points in the $xy$-plane to define the projected distance $\rp.$ We place mock galaxies into redshift-space by replacing each galaxy's $z$-coordinate with $z \rightarrow z + V_{\rm z}/H_0.$ We count pairs of points in each of our $\rp$ bins, rejecting pairs with $z-$distance exceeding $\pi_{\rm max}=60$ ${\rm Mpc/h.}$ We employ the \citet{landyszalay93} estimator to turn pair counts into a $\wprp$ prediction, as described in detail in {\tt halotools.readthedocs.io}.
+After populating a halo catalog with mock galaxies, we calculate the
+comoving number density of our mock galaxy sample as $n_{\rm g} =
+N_{\rm gal} / L_{\rm box}^3.$ We apply the distant-observer
+approximation and use the simulation z-axis as the line-of-sight
+direction, and the distance between points in the $xy$-plane to define
+the projected distance $\rp.$ We place mock galaxies into
+redshift-space by replacing each galaxy's $z$-coordinate with $z
+\rightarrow z + V_{\rm z}/H_0.$ We count pairs of points in each of
+our $\rp$ bins, rejecting pairs with $z-$distance exceeding $\pi_{\rm
+  max}=60$ ${\rm Mpc/h.}$ We employ the \citet{landyszalay93}
+estimator to turn pair counts into a $\wprp$ prediction, as described
+in detail in {\tt halotools.readthedocs.io}.
 
@@
 
-In addition to the standard occupation statistics described in the previous section, 
-in this paper we also use the decorated HOD formalism to connect galaxies t
-o dark matter halos in a manner that has simultaneous dependence on both $\mvir$ and halo concentration. 
-Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our ``baseline" first occupation moments. 
-At fixed $\mvir,$ halos are divided into one of two categories, those of high- and low-concentration, 
-depending on whether the concentration of the halo places it above or below the rank-order percentile 
-$f_{\rm split},$ which we keep fixed to $f_{\rm split}=0.5$ throughout the paper for simplicity. 
-High-concentration halos have a different first occupation moment relative to low-concentration 
-halos of the same mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq \langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the first moment of high- and low-concentration halos is modulated by $\abias,$ the novel parameter of the decorated HOD governing assembly bias.
-Values of $\abias=\pm1$ correspond to the maximum strength of assembly bias allowable by the constraint that the model preserves the marginalized first moment, $\langle\ngal|\mvir\rangle;$ thus regardless of the value of $\abias,$ in the decorated HOD the marginalized first moment of centrals and satellites are {\em unchanged from the baseline value defined by Equations \ref{eq:ncen} and \ref{eq:nsat}}.
-Decorated HOD models all have the same HODs, when averaged over all halos at fixed mass, as standard HOD models. The only 
-change in Decorated HOD models is whether or not an additional property also modulates halo occupation at fixed halo mass. A 
-value of $\abias = 0$ indicates no galaxy assembly bias whatsoever. We refer the reader to \citet{hearin_etal16} for 
-further details about the decorated HOD.
+In addition to the standard occupation statistics described in the
+previous section, in this paper we also use the decorated HOD
+formalism to connect galaxies t o dark matter halos in a manner that
+has simultaneous dependence on both $\mvir$ and halo concentration.
+Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our
+``baseline" first occupation moments.  At fixed $\mvir,$ halos are
+divided into one of two categories, those of high- and
+low-concentration, depending on whether the concentration of the halo
+places it above or below the rank-order percentile $f_{\rm split},$
+which we keep fixed to $f_{\rm split}=0.5$ throughout the paper for
+simplicity.  High-concentration halos have a different first
+occupation moment relative to low-concentration halos of the same
+mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq
+\langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the
+first moment of high- and low-concentration halos is modulated by
+$\abias,$ the novel parameter of the decorated HOD governing assembly
+bias. Values of $\abias=\pm1$ correspond to the maximum strength of
+assembly bias allowable by the constraint that the model preserves the
+marginalized first moment, $\langle\ngal|\mvir\rangle;$ thus
+regardless of the value of $\abias,$ in the decorated HOD the
+marginalized first moment of centrals and satellites are {\em
+  unchanged from the baseline value defined by Equations \ref{eq:ncen}
+  and \ref{eq:nsat}}.  Decorated HOD models all have the same HODs,
+when averaged over all halos at fixed mass, as standard HOD
+models. The only change in Decorated HOD models is whether or not an
+additional property also modulates halo occupation at fixed halo
+mass. A value of $\abias = 0$ indicates no galaxy assembly bias
+whatsoever. We refer the reader to \citet{hearin_etal16} for further
+details about the decorated HOD.
 
-In the present work, we fix our model to the simplest class of galaxy assembly bias models, though a recipe for 
-generalizing to more complicated models can be found in \citet{hearin_etal16}. In particular, we split halos into 
-two populations as specified in the previous paragraph. We then populate halos with satellite galaxies specified 
-by an assembly bias parameter $-1 \le A_{\rm sat} \le 1$ and central galaxies with a distinct assembly bias 
-parameter $-1 \le A_{\rm cen} \le 1$. These two additional parameters are varied in our analyses that include 
-assembly bias, making the number of parameters that vary in these analyses seven. As we show below, 
-these additional parameters are in many instances poorly constrained by clustering data of the quality of 
-SDSS DR7 alone, so exploring more complex models of assembly bias does not yet seem justified.
+In the present work, we fix our model to the simplest class of galaxy
+assembly bias models, though a recipe for generalizing to more
+complicated models can be found in \citet{hearin_etal16}. In
+particular, we split halos into two populations as specified in the
+previous paragraph. We then populate halos with satellite galaxies
+specified by an assembly bias parameter $-1 \le A_{\rm sat} \le 1$ and
+central galaxies with a distinct assembly bias parameter $-1 \le
+A_{\rm cen} \le 1$. These two additional parameters are varied in our
+analyses that include assembly bias, making the number of parameters
+that vary in these analyses seven. As we show below, these additional
+parameters are in many instances poorly constrained by clustering data
+of the quality of SDSS DR7 alone, so exploring more complex models of
+assembly bias does not yet seem justified.
 

### 2016-06-08 ms.tex
Made number of small corrections to intro

@@
 occupation models that enable galaxies to occupy halos in a manner
-that depends upon several halo properties \citep{hearin_etal16}.  See
-also \citet{Yao_etalXX} for a similar approach. In this paper, we
-revisit the interpretation of luminosity-dependent galaxy clustering
-in the Sloan Digital Sky Survey (SDSS) Data Release 7 (DR7) data,
-analyzed previously by \citet{zehavi_etal11}, in the context both
-standard halo occupation models and these new models.
+that depends upon several halo properties \citep{hearin_etal16}.  In
+this paper, we revisit the interpretation of luminosity-dependent
+galaxy clustering in the Sloan Digital Sky Survey (SDSS) Data Release
+7 (DR7) data, analyzed previously by \citet{zehavi_etal11}, in the
+context both standard halo occupation models and these new models.
 
@@
 via a continuously-valued parameter. Using SDSS clustering
-measurements to constrain their model, they conclude that galaxy
-luminosity reveals a significant dependence on halo
+measurements to constrain their model, they conclude that at fixed
+halo mass galaxy luminosity reveals a significant dependence on halo
 concentration. Since the latter is strongly correlated with halo
@@
 galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
-However, \citet{lin_mandelbaum_etal15} claim that most of the these
+However, \citet{lin_mandelbaum_etal15} claim that most of these
 differences in clustering strength can be explained as due to
@@
 bias in galaxy-scale halos \citep[see also][]{paranjape15}.  On the
-other hand, \citet{miyatake_etal15} and \citet{more_etal16} recently
+other hand, \citet{miyatake_etal16} and \citet{more_etal16} recently
 presented strong evidence for the presence of assembly bias in massive

### 2016-06-08 ms.tex
Updated text with new figure of direct HODs, resolving #11

--- 2016-06-07 ms.tex
@@
 
+%=-------------------------------------------------------------------------------------------------
+\begin{figure*}
+\begin{center}
+\includegraphics[width=8.0cm]{central_hod_comparison.pdf}
+\includegraphics[width=8.5cm]{satellite_hod_comparison.pdf}
+\caption{
+We show the first moments of the central and satellite occupation distributions 
+from the best-fit models to the $\magr<-20$ sample in the left and right 
+panels, respectively. The green curve shows the HOD of our best-fit model 
+that includes the effect of assembly bias; the red curve shows the HOD 
+of the best-fit model in which assembly bias is assumed to be zero; 
+the dashed black curve shows the best-fit HODs from \citet{zehavi_etal11}. 
+The green error band around the decorated HOD results shows the variance 
+in the HOD from randomly sampling one hundred points in parameter space 
+with $\chi^{2}_{\rm model} - \chi^{2}_{\rm min} < 1.$
+}
+\label{fig:directhodcomparison}
+\end{center}
+\end{figure*}
+%----------------------------------------------------------------------------------------------------
+
 Focusing attention on the parameters describing galaxy assembly bias, it is 

### 2016-06-10 ms.tex
removed obsolete draft comments. removed period from end of title

@@
 {
-Constraints on Assembly Bias from Galaxy Clustering. 
+Constraints on Assembly Bias from Galaxy Clustering
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ARZ: Important points:
-% -supersedes previous analyses even for standard HOD.
-% -cannot rule out assembly bias using galaxy clustering.
-% -some samples favor assembly bias.
 \begin{abstract}
@@
 dark matter halos that are biased tracers of the density field; and
-(2) galaxies occupy halos as a function of halo masses only. It is now
-well known that halo bias depends upon halo properties other than mass
+(2) galaxies occupy halos as a function of halo mass $\mvir$ only.
+
+It is now well known that halo bias depends upon halo properties other than $\mvir$
 \citep[e.g.][]{gao_etal05,wechsler06,gao_white07,zentner07,dalal_etal08,lacerna11},
 an effect called halo assembly bias. If galaxies occupy halos as a
-function of properties other than halo mass, then standard halo
+function of halo properties other than $\mvir,$ then standard halo
 occupation methods will be subject to a systematic error due to galaxy
-assembly bias. Several of us have previously shown that this error can
+assembly bias. 
+Several of us have previously shown that this error can
 be significant in an analysis of galaxy clustering and can bias
 inferences about many aspects of galaxy evolution
-\citep{zentner_etal14}. Consequently, we have developed halo
-occupation models that enable galaxies to occupy halos in a manner
-that depends upon several halo properties \citep{hearin_etal16}.  In
-this paper, we revisit the interpretation of luminosity-dependent
+\citep{zentner_etal14}.
+
+There is increasing observational evidence that galaxy assembly bias is 
+present in the real Universe. 
+Using an approach based on subhalo abundance matching, 
+\citet{lehmann_etal15} showed that the clustering of low-redshift 
+galaxies favors models in which stellar mass depends upon a 
+combination of $\mvir$ and halo concentration.
+\citet{miyatake_etal16} and \citet{more_etal16} have 
+presented evidence for the presence of assembly bias in massive
+clusters; in particular, they find that clusters with a more
+concentrated distribution of satellite galaxies exhibit a weaker large-scale bias 
+relative to clusters of the same mass with satellite galaxies that
+are less centrally concentrated. 
+Additional support for the presence of assembly bias has come from a
+variety of studies that have shown, or suggested, that the large-scale
+environment of dark matter halos of fixed mass 
+is correlated with the star formation rate of their central galaxies 
+\citep{yang_etal06a, blanton_berlind07,wang_etal08,wang_etal13,hearin_etal14}.
+
+Despite this growing evidence, the empirical modeling community 
+has not yet reached a consensus on the question of galaxy assembly bias. 
+For example, \citet{lin_mandelbaum_etal15} claim that 
+some of the above evidence for assembly bias can be explained by
+differences in halo mass between the galaxy samples under consideration.
+\citet{paranjape15} urges caution that contamination by satellite galaxies 
+can masquerade as a false signal of assembly bias. 
+\citet{tinker08b} argue that measurements of void statistics place strong 
+bounds on the possible strength of the signal.
+
+In much of the literature on this topic, 
+the character of the supporting evidence
+suffers from a severe shortcoming. 
+Until very recently, the only models that have been fit to 
+observational clustering measurements have been traditional models 
+in which assembly bias is assumed from the outset to be zero. 
+Models that include assembly bias such as semi-analytic models 
+are typically too computationally expensive 
+for anything besides a ``one-off" comparison \citep[e.g.,][]{croton_etal07}, prohibiting 
+any conclusive statement to be made about the strength of the signal.
+
+Motivated by this shortcoming, we have developed a new class of 
+empirical models that enable galaxies to occupy halos in a manner
+that has {\em simultaneous} dependence 
+upon multiple halo properties \citep{hearin_etal16}, 
+{\em including continuously variable levels of assembly bias}.
+Crucially, our implementation is of sufficient computational efficiency 
+to permit a proper likelihood analysis of the model parameter space. 
+Armed with this new methodology, in this paper 
+we revisit the interpretation of luminosity-dependent
 galaxy clustering in the Sloan Digital Sky Survey (SDSS) Data Release
@@
 
-The ultimate goal of halo occupation modeling is to characterize the
-galaxy-dark matter connection by constraining the probability
-distribution $P(X_{\rm g}|Y_{\rm h})$. Here $X_{\rm g} = \{x_1, x_2,
-  ...x_n\}$ is a set of $n$ galaxy properties, and $Y_{\rm h} = \{y_1,
-  y_2,...,y_m\}$ a set of $m$ halo properties. Accurate knowledge of
-this probability distribution yields invaluable insight regarding the
-processes of galaxy formation, and allows one to make accurate
-predictions for the clustering of galaxies as function of any property
-$x_i$. Most halo occupation studies to date have restricted themselves
-to only one halo property, namely halo mass.  This includes Halo
-Occupation Distribution (HOD) models, which aim to constrain
-$P(N|\mvir)$, the probability that a halo of mass $M$ contains $N$
-galaxies of some specified properties
-\citep[e.g.,][]{kauffmann_etal97,jing98,benson01,berlind02}, and
-Conditional Luminosity Function (CLF) models, which aim to constrain
-$\Phi(L|M)$, the luminosity (or stellar mass) function of galaxies in
-haloes of mass $M$ \citep[e.g.,][]{yang03,vdBosch03a,cooray06}. The
-HOD and CLF models are mainly used in combination with the halo model,
-which describes the non-linear matter field in terms of halo building
-blocks \citep[e.g.,][]{seljak00,cooray02}, to predict the clustering
-of galaxies as function of luminosity or stellar mass.  Although
-entirely analytical, and therefore fast, the downside of this method
-is that it is extremely challenging to construct a model that is
-accurate at the few percent level. The main issues are halo exclusion
-\citep[see][]{smith_etal07,vdBosch13}, scale dependence of the halo
-bias \citep[see][]{tinker05}, and the halo assembly bias mentioned
-above.
-
-These issues are trivially avoided by directly populating dark matter
-haloes in numerical simulations with galaxies. This can be done using
-either a parameterized model for the halo occupation statistics
-\citep[e.g.,][]{Yang_etal04,moster10,behroozi10,behroozi13} or by
-rank-order matching galaxy properties (i.e., luminosity or stellar
-mass) to halo properties (i.e., halo mass). The latter method is known
-as subhalo abundance matching (SHAM).  Although many SHAM studies use
-halo mass as the halo property of choice
-\citep[e.g.,][]{vale_ostriker04,vale_ostriker06,conroy07,conroy_wechsler09},
-a number of studies have used alternative halo properties, such as the
-maximum circular velocity, $\vmax$, or its peak value over the halo's
-history, $V_{\rm peak}$
-\citep[e.g.][]{tasitsiomi_etal04,conroy06,marin_etal08,reddick_etal13}
-
-Since, at fixed halo mass, $\vmax$ is correlated with halo
-concentration, and thus with halo assembly time, the resulting
-occupation models have assembly bias build in
-\citep[see][]{zentner_etal14}; i.e., at fixed halo mass, galaxy
-properties will be correlated with halo assembly
-time. \citet{lehmann_etal15} took this one step further, and explored
-SHAM models in which the halo property varies between $M$ and $\vmax$
-via a continuously-valued parameter. Using SDSS clustering
-measurements to constrain their model, they conclude that at fixed
-halo mass galaxy luminosity reveals a significant dependence on halo
-concentration. Since the latter is strongly correlated with halo
-formation time \citep[e.g.,][]{wechsler02,zhao_etal09,ludlow_etal13},
-their conclusions argue for non-zero assembly bias in the galaxy
-population.
-
-Additional support for the presence of assembly bias has come from a
-variety of studies that have shown, or suggested, that the large-scale
-environment (i.e., clustering strength) of dark matter haloes {\it of
-  fixed mass} is correlated with the star formation rate of their
-central
-galaxies\citep[][]{yang_etal06a,blanton_berlind07,wang_etal08,tinker_etal12,wang_etal13,HW13a,hearin_etal13b,hearin_etal14,watson_etal14}.
-However, \citet{lin_mandelbaum_etal15} claim that most of these
-differences in clustering strength can be explained as due to
-differences in halo mass or contamination by satellite galaxies, and
-therefore argue that there is no significant evidence for assembly
-bias in galaxy-scale halos \citep[see also][]{paranjape15}.  On the
-other hand, \citet{miyatake_etal16} and \citet{more_etal16} recently
-presented strong evidence for the presence of assembly bias in massive
-clusters; in particular, they find that clusters with a more
-concentrated distribution of satellite galaxies are less strongly
-clustered than their equal-mass counterparts whose satellite galaxies
-are less centrally concentrated. To summarize, while there is strong
-evidence for the presence of assembly bias on the scale of clusters,
-there is not concensus yet as to whether assembly bias plays also a
-role in less massive haloes.
-
-Our work is important for several reasons. Our work is a re-analysis
-of the SDSS DR7 data that overcomes shortcomings of previous
+Our work is a re-analysis of the SDSS DR7 data that 
+overcomes numerous shortcomings of previous
 analyses. In particular, we use direct population of galaxies in a
@@
 simulation we use is based on the latest Planck cosmological
-parameters, updating previous work. Furthermore, many important
+parameters \citep{planck13}, updating previous work. 
+Furthermore, many important
 differences between this work and the previous analysis by
 \citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
-Chains used by Zehavi et al. were too small and had therefore not
+Chains used in \citet{zehavi_etal11} were too small and had not
 converged (Z. Zheng \& I. Zehavi, private communication).  Therefore,
-our analysis {\em supersedes previous analyses even in the case of
+{\em our analysis supersedes previous work even in the case of
 standard halo occupation models}.
 
-Furthermore, our work demonstrates explicitly that significant
-assembly bias in $M_r$-selected samples from SDSS DR7 cannot be ruled
+Most importantly, our work demonstrates explicitly that significant
+assembly bias in $\magr$-selected samples from SDSS DR7 cannot be ruled
 out based on a standard analysis of galaxy clustering only. In fact,
@@
   significant}. As demonstrated by \citet{zentner_etal14}, this
-conclusion could have important consequences for the interpretation of
+conclusion has important consequences for the interpretation of
 both extant and forthcoming data.
@@
 Our paper is organized as follows. In Section~\ref{section:methods},
-we discuss our implementation of halo occupation models and our
-assumptions in our parameter inference analysis. We present results
-for both standard halo occupation analysis and analysis in the context
-of models with galaxy assembly bias in
-Section~\ref{section:results}. We summarize our results and draw
+we discuss our implementation of halo occupation models and the
+parameter inference methodology. We present results
+from both traditional and assembly-biased halo occupation analyses 
+in Section~\ref{section:results}. We summarize our results and draw
 conclusions in Section~\ref{section:conclusions}.

### 2016-06-10 compile_script.sh
Added shell script to automatically fix offensive British spellings, wipe the repo of temporary files, and repeatedly compile the latex document after running bibtex.

@@ -1,0 +1,8 @@
+perl -pi -w -e 's/haloe/halo/g;' ms.tex
+perl -pi -w -e 's/colour/color/g;' ms.tex
+git clean -dfx
+pdflatex ms.tex
+bibtex ms.bib
+pdflatex ms.tex
+pdflatex ms.tex
+pdflatex ms.tex

### 2016-06-12 compile_script.sh
Fixed auto-compile shell script. Should work now, @vdbosch69.

@@ -1,8 +1,13 @@
 perl -pi -w -e 's/haloe/halo/g;' ms.tex
 perl -pi -w -e 's/colour/color/g;' ms.tex
-git clean -dfx
-pdflatex ms.tex
-bibtex ms.bib
-pdflatex ms.tex
-pdflatex ms.tex
-pdflatex ms.tex
+rm *.aux
+rm *.log
+rm *.synctex.gz
+rm *.bbl
+rm *.blg
+rm *.out
+pdflatex ms
+bibtex ms
+pdflatex ms
+pdflatex ms
+pdflatex ms

### 2016-06-13 ms.tex
Added info on wp measurements, covariances, and likelihoods.

@@
   measurements of projected galaxy clustering, $\wprp,$ and number
-  density, $n_{\rm d},$ made from r-band luminosity-threshold
+  density, $n_{\rm g},$ made from r-band luminosity-threshold
   samples. The Decorated HOD is a model for the galaxy--halo
@@
   is not possible to rule out assembly bias using DR7 measurements of
-  $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$
+  $\wprp$ and $n_{\rm g}.$ Moreover, galaxy samples $\magr<-20, -20.5$
   favor strong levels of central galaxy assembly bias:
@@
 techniques that can be used to interpret such data, such as the conditional luminosity function 
-\citep[CLF, e.g.,][]{yang03,vdBosch13}, exist. In this section, we review the ``standard" HOD 
-model used in the present work which assumes that there is no galaxy assembly bias. We refer to 
+\citep[CLF, e.g.,][]{yang03,vdBosch13}, exist. In this subsection, we review the ``standard" HOD 
+model used in the present work, which assumes that there is no galaxy assembly bias. We refer to 
 such a model as ``standard" because all HOD analyses of galaxy clustering to date have assumed no 
-galaxy assembly bias. In the following section, we describe 
+galaxy assembly bias. In the following subsection, we describe 
 the Decorated HOD model described in \citet{hearin_etal16}. In both cases, we will only 
@@
 
-All of our analyses are based on the Bolshioi-Planck simulation \citep{riebe_etal11}. 
-Bolshoi-Planck was run with cosmological parameters based on \citet{planck13}, $\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 0.307, \Omega_{\rm b} = 0.048, h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ within a cubic box
+All of our analyses are based on the Bolshioi-Planck (BolshioP) simulation \citep{riebe_etal11}. 
+BolshoiP was run with cosmological parameters based on \citet{planck13}, 
+$\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 1 - \Omega_{\Lambda} = 0.307, \Omega_{\rm b} = 0.048, 
+h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ within a cubic box 
 $250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$ 
-Further information about the Bolshoi-Planck simulation is available at \url{https://www.cosmosim.org}.
+Further information about the BolshoiP simulation is available at \url{https://www.cosmosim.org}.
 
@@
 
-The five parameters of the standard HOD models are varied in standard analyses are $\log (M_{\rm min})$, 
+The five parameters of HOD models that are varied in standard analyses are $\log (M_{\rm min})$, 
 $\sigma_{\log M}$, $\alpha$, $\log (M_1)$, and $\log (M_0)$, though, as we show below, central galaxies usually 
-outnumber satellite galaxies in by a factor of several, so $\log (M_{\rm min})$ and $\sigma_{\log M}$ usually 
+outnumber satellite galaxies by a factor of several, so $\log (M_{\rm min})$ and $\sigma_{\log M}$ usually 
 vary along a narrow degeneracy that fixes the total galaxy number density to the observed value. There are 
@@
 comoving number density of our mock galaxy sample as $n_{\rm g} =
-N_{\rm gal} / L_{\rm box}^3.$ We apply the distant-observer
+N_{\rm gal} / L_{\rm box}^3$, where $N_{\rm gal}$ is the total number of 
+galaxies in the mock sample. We apply the distant-observer
 approximation and use the simulation z-axis as the line-of-sight
@@
 the projected distance $\rp.$ We place mock galaxies into
-redshift-space by replacing each galaxy's $z$-coordinate with $z
-\rightarrow z + V_{\rm z}/H_0.$ We count pairs of points in each of
-our $\rp$ bins, rejecting pairs with $z-$distance exceeding $\pi_{\rm
-  max}=60$ ${\rm Mpc/h.}$ We employ the \citet{landyszalay93}
+redshift-space by replacing each galaxy's $z$-coordinate with 
+$z_{\rm RS} = z + V_{\rm z}/H_0.$ We count pairs of points in each of
+our $\rp$ bins, rejecting pairs with $z_{\rm RS}-$ distance exceeding 
+$\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection 
+depth chosen by \citet{zehavi_etal11}. We employ the \citet{landyszalay93}
 estimator to turn pair counts into a $\wprp$ prediction, as described
@@
 previous section, in this paper we also use the decorated HOD
-formalism to connect galaxies t o dark matter halos in a manner that
-has simultaneous dependence on both $\mvir$ and halo concentration.
+formalism to connect galaxies to dark matter halos in a manner that
+has simultaneous dependence on both $\mvir$ and {\em halo concentration}.
 Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our
@@
   unchanged from the baseline value defined by Equations \ref{eq:ncen}
-  and \ref{eq:nsat}}.  Decorated HOD models all have the same HODs,
+  and \ref{eq:nsat}}. In other words, {\em decorated HOD models all have the same HODs,
 when averaged over all halos at fixed mass, as standard HOD
-models. The only change in Decorated HOD models is whether or not an
+models}. The only change in Decorated HOD models is whether or not an
 additional property also modulates halo occupation at fixed halo
@@
 specified by an assembly bias parameter $-1 \le A_{\rm sat} \le 1$ and
-central galaxies with a distinct assembly bias parameter $-1 \le
-A_{\rm cen} \le 1$. These two additional parameters are varied in our
+central galaxies with a distinct assembly bias parameter 
+$-1 \le A_{\rm cen} \le 1$. These two additional parameters are varied in our
 analyses that include assembly bias, making the number of parameters
@@
 of the quality of SDSS DR7 alone, so exploring more complex models of
-assembly bias does not yet seem justified.
+assembly bias does not yet seem justified in such analyses.
 
@@
 
+We constrain HOD parameters based on SDSS DR7 measurements of the projected 
+galaxy two-point functions, $w_{\rm p}(r_{\rm p})$, and galaxy number densities, $n_{\rm g}$, 
+for luminosity threshold samples published in \citet{zehavi_etal11}. We use the full covariance 
+matrix of the projected correlation function available at 
+{\tt astroweb.cwru.edu/izehavi/dr7\_covar/table8}. We assume a likelihood of the 
+form $\mathcal{L} \propto e^{-\chi^2/2}$, where
+%
+\begin{equation}
+\label{eq:chisquare}
+\chi^2 = \Delta w_{{\rm p},i} \, [C^{-1}]_{ij} \, \Delta w_{{\rm p},j} + \frac{(n_{\rm g}^{\rm mock} - n_{\rm g}^{\rm meas})^2}{\sigma_{\rm n}^2}, 
+\end{equation}
+%
+$\Delta w_{{\rm p},i} = w_{\rm p}^{\rm mock}(r_{{\rm p},i}) - w_{\rm p}^{\rm meas}(r_{{\rm p},i})$ is the difference 
+between the projected two-point function predicted by the mock catalog and the measured value in the i$^{\rm th}$ 
+separation bin (of 12 bins total), $C^{-1}$ is the inverse of the covariance matrix of the measurements, 
+and the last term in Eq.~(\ref{eq:chisquare}) is the contribution from the difference between the predicted and measured 
+galaxy number density. The error on the galaxy number density assumes Poisson statistics for both the measured and predicted 
+galaxy number densities.
+
 To infer parameters for the HOD and Decorated HOD models described in the previous subsections, 
-we performed a Markov Chain Monte Carlo (MCMC) sampling of the posteriors using the 
+we performed a Markov Chain Monte Carlo (MCMC) sampling of the posterior distribution using the 
 affine-invariant ensemble sampler of \citet{goodman_weare10} as implemented in the 
@@
 priors have a negligible influence on the posterior aside from $\log M_0$. 
-We find that $\log M_0$ is often very poorly constrained by clustering data.
+We find that $\log M_0$ is often very poorly constrained by clustering data and 
+priors on $\log M_0$ can have a non-negligible influence on inferred parameters.
 
@@
 {\bf Left:} The $M_r<-19$ threshold sample projected correlation function with diagonal elements of 
-covariance (points with errorbars). The grey lines are 25 randomly-selected HOD models that yield 
+covariance (points with errorbars). The grey lines are 50 randomly-selected HOD models that yield 
 $\Delta \chi^2 <1$ compared to the best-fitting model. {\bf Right:} Same as the left panel but using a 

### 2016-06-13 ms.tex
Added more flesh to Introduction pointing out pros and cons of direct mock population, as suggested by @vdbosch69

@@
 
-Our work is a re-analysis of the SDSS DR7 data that 
-overcomes numerous shortcomings of previous
-analyses. In particular, we use direct population of galaxies in a
-cosmological simulation so that delicate issues present in analytic
-modeling, such as scale-dependent halo bias, are treated exactly.  The
-simulation we use is based on the latest Planck cosmological
+This work presents a re-analysis of the SDSS DR7 data that 
+overcomes numerous shortcomings of previous analyses. 
+Our analysis improvements stem primarily from our 
+directly populating mock galaxy catalogs into a cosmological simulation, 
+whereas previous analyses relied upon analytical fitting functions 
+with parameters calibrated against a suite of simulations. 
+In direct mock population, delicate issues present in analytic
+modeling, such as scale-dependent halo bias and halo exclusion, are treated exactly.  
+Our approach also provides a natural framework for studying models of assembly bias, 
+since we can use the exact clustering properties of simulated halos as a function of 
+any arbitrary halo properties in the catalog. With direct mock population, 
+systematic uncertainty in the model is limited to 
+the sample variance of the simulated box, 
+errors related to insufficient numerical resolution, 
+and numerical inaccuracies of halo-finding (e.g., over-merging).
+
+In addition to improvements from direct mock population, 
+the simulation we use is based on the latest Planck cosmological
 parameters \citep{planck13}, updating previous work. 
@@
 \citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
-Chains used in \citet{zehavi_etal11} were too small and had not
-converged (Z. Zheng \& I. Zehavi, private communication).  Therefore,
+Chains used in \citet{zehavi_etal11} did not sufficiently sample the 
+posterior distribution (Z. Zheng \& I. Zehavi, private communication).  Therefore,
 {\em our analysis supersedes previous work even in the case of

### 2016-06-13 ms.tex
Small edits to section 3.1

--- 2016-06-13 ms.tex
@@
 \citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
-Chains used in \citet{zehavi_etal11} were too small and had not
-converged (Z. Zheng \& I. Zehavi, private communication).  Therefore,
+Chains used in \citet{zehavi_etal11} were not converged 
+(Z. Zheng, private communication). Therefore,
 {\em our analysis supersedes previous work even in the case of
@@
 show the projected correlation function data along with predictions for $\wprp(\rp)$ from 50 randomly-selected 
-models from the MCMC chains. Note that the significant covariance in the data makes it difficult to 
+models from the MCMC chains within $\Delta \chi^2 \le 1$ of the best-fit model. 
+Note that the significant covariance in the data makes it difficult to 
 determine the quality of fit from visual inspection of these figures.
@@
 analysis. Firstly, in our re-analysis of the projected clustering data, we generally find all mass scales to 
-be slightly higher than in the work of \citet{zehavi_etal11}. This difference is largely due to the slightly 
-different cosmologies adopted in this work. The most important difference 
-are in the values of $\Omega_{\rm M}$, and $\sigma_8$.  
+be slightly higher than in the work of \citet{zehavi_etal11}. This difference is primarily due to the slightly 
+different cosmological model used in this work as compared to that of \citet{zehavi_etal11}. 
+The most important differences are in the values of $\Omega_{\rm M}$, and $\sigma_8$.  
 \citet{zehavi_etal11} assumed $\Omega_{\rm M}=0.25$ and $\sigma_8=0.8$, 
@@
 Slightly larger mass scales are necessary in an analysis with higher $\Omega_{\rm M}$ and $\sigma_8$ in order 
-to maintain galaxy number densities with larger halo number densities.
+to maintain galaxy number densities fixed with larger halo number densities.
 
@@
 Additionally, we have confirmed with a subset of the authors of \citet{zehavi_etal11} 
-that the number of MCMC samples they included in their analysis was 
-insufficient in a number of cases and that this can lead to a significant underestimation of the uncertainties 
-on the inferred parameters, especially $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
-(Z. Zheng \& I. Zehavi, private communication). The analysis of \citet{zehavi_etal11} 
+that the MCMC chains used in a number of their analyses may not have been 
+properly converged and that this may have led to a significant underestimation of the 
+uncertainties on the inferred parameters, especially $\log (M_0)$, $\log (M_{\rm min})$, 
+and $\sigma_{\log M}$ (Z. Zheng, private communication). The analysis of \citet{zehavi_etal11} 
 used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence. 
-Additionally, we have recreated qualitatively similar behavior by considering only small subsets of our 
-full MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution 
+The cause of the problem is likely a restrictive proposal distribution that causes the chain to 
+diffuse through the posterior distribution only very slowly. We have recreated qualitatively similar 
+behavior by considering only small subsets of our full MCMC chains. Consequently, insufficient 
+sampling of the posterior seems to be the likely resolution 
 of the discrepancies between our work and that of \citet{zehavi_etal11}.
@@
 degenerate with each other such that most of the posterior probability lies in a narrow band 
-along which $\log (M_{\rm min})$ and $\sigma_{\log M}$ are positively correlated, as shown in 
-Fig.~\ref{fig:Mr20triangle}. In the following plots, we suppress the parameter $\sigma_{\log M}$,  
+along which $\log (M_{\rm min})$ and $\sigma_{\log M}$ are positively correlated. 
+In the following plots, we exclude the parameter $\sigma_{\log M}$,  
 in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is 
@@
 we have explored the posteriors of the parameters with significantly more samples (roughly two orders of magnitude), 
-thereby mitigating errors on inferred parameters and their errors induced by insufficient sampling of the 
-posterior.
+thereby mitigating errors on inferred parameters caused by insufficient sampling of the 
+posterior by \citet{zehavi_etal11}.
 

### 2016-06-13 ms.tex
Edited section 3.1

@@
 \citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
-Chains used in \citet{zehavi_etal11} were not converged 
-(Z. Zheng, private communication). Therefore,
+Chains used in \citet{zehavi_etal11} did not sufficiently sample the 
+posterior distribution (Z. Zheng \& I. Zehavi, private communication).  Therefore,
 {\em our analysis supersedes previous work even in the case of

### 2016-06-13 ms.tex
Edited 3.2

@@
 in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above and 
-in \citet{hearin_etal16}.
+in more detail in \citet{hearin_etal16}.
 
@@
 of the predicted two-point functions to match the measured two-point functions across the 
-transition form the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$. 
+transition from the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$. 
 This is most apparent for the $M_r < -20$ threshold sample shown in Fig.~\ref{fig:Mr20samples}. 
@@
 In cases where the posterior on a parameter is monotonic within the physical parameter 
-range, we quote an upper or lower limit on the parameter. One- and two-dimensional 
-visualizations of the posteriors from our analysis are shown in Figure~\ref{fig:Mr19ABtriangle}, 
-Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle}.
+range, we quote an upper or lower limit on the parameter. Examples of one- and two-dimensional 
+visualizations of the posteriors from our analyses are shown in Figure~\ref{fig:Mr19ABtriangle}, 
+Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle} for the 
+$M_r<-19$, $M_r<-20$, and $M_r<-21$ samples respectively.
 
@@
 
-Table~\ref{table:parameters} and Figures~\ref{fig:Mr19ABtriangle}-\ref{fig:Mr21triangle} 
+Table~\ref{table:parameters} and Figures~\ref{fig:Mr19ABtriangle}--\ref{fig:Mr21ABtriangle} 
 all make several simple, generic points. Introducing additional parameter 
@@
 of SDSS DR7 measurements cannot rule out, or strongly restrict galaxy assembly 
-bias in many cases. Nonetheless, it is apparent that the presence of assembly bias 
+bias in many cases. This is the case, for example, for the $M_r<-21$ sample with posteriors 
+shown in Fig.~\ref{fig:Mr21ABtriangle}. In this case, both $A_{\rm cen}$ and 
+$A_{\rm sat}$ have posteriors that peak near zero, but are very broad. 
+Nonetheless, it is apparent that the presence of galaxy assembly bias 
 can alter the inferred HOD, or more generally, the inferred relationship between 
@@
 parameters between models with and without galaxy assembly bias. Other threshold 
-samples exhibit significant changes particularly for $\alpha$, and to a lesser degree 
+samples exhibit significant differences particularly for $\alpha$, and to a lesser degree 
 for $\log (M_{\rm min})$ and $\sigma_{\log M}$.
@@
 confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer 
-galaxies to reside in halos of larger concentration at fixed halo mass. This particular threshold 
-sample is the most significant outlier in this regard. Nevertheless, there are hints of assembly 
+galaxies to reside in halos of larger concentration at fixed halo mass. Figure~\ref{fig:directhodcomparison} 
+compares the inferred HODs for the $M_r<-20$ sample in a standard HOD analysis with the 
+inferred HOD from our decorated HOD analysis that includes parameters to describe 
+assembly bias. This is an explicit example of the degree to which the inferred relationship 
+between galaxies and halos can be altered by assembly bias.
+
+Though the evidence for assembly bias is the most significant for the $M_r<-20$ sample, there are hints of assembly 
 bias in other samples. Satellite galaxies show a marginal preference for occupying halos of 

### 2016-06-13 ms.tex
Edited section 4.

@@
 
-Though the evidence for assembly bias is the most significant for the $M_r<-20$ sample, there are hints of assembly 
-bias in other samples. Satellite galaxies show a marginal preference for occupying halos of 
-higher concentration in the $M_r < -19$ threshold sample. The $M_r < -19$ sample exhibits 
-weak preference for a positive correlation of galaxy occupation with halo concentration at fixed 
+Though the evidence for assembly bias is the most significant for the $M_r<-20$ sample, 
+there are hints of galaxy assembly bias in other samples. Satellite galaxies show a marginal preference 
+for occupying halos of higher concentration in the $M_r < -19$ threshold sample. The $M_r < -19.5$ 
+sample exhibits weak preference for a positive correlation of galaxy occupation with halo concentration at fixed 
 mass for both satellite galaxies and central galaxies. Continuing upward with luminosity, 
@@
 for the $M_r < -21$ threshold sample, for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$ 
-are consistent with zero will within 1$\sigma$. These data suggest that assembly bias 
-may be present in the real universe.
+are consistent with zero well within 1$\sigma$.
 
@@
 
-We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering,  $\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}.
-Our work is especially novel in that we provide the first quantitative constraints on assembly bias derived from the Decorated HOD, an extension to the traditional HOD introduced in \citet{hearin_etal16} developed for exactly this purpose.
-We enumerate our most important conclusions below. 
+We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering, 
+$\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}. 
+The novelty of our work is that we have performed these analyses using the 
+decorated Halo Occupation Distribution (HOD) formalism, which allows for galaxy 
+assembly bias and was introduced by \citet{hearin_etal16} precisely for this purpose. 
+In this work, we provide the first quantitative constraints on 
+assembly bias derived from the Decorated HOD. We enumerate our most important conclusions below. 
+%
 \ben
+%
 \item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$ 
+%
 \item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we study.
-Both the $\magr<-20, -20.5$ samples prefer relatively strong central galaxy assembly bias, while at lower luminosities, the $\magr<-19$ sample favors satellite assembly bias.
-\item Galaxy assembly bias generally weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $\abias^{\rm cens}=0$ and $\abias^{\rm sats}=0.$ This consistent with the well-established result that {\em halo assembly bias} weakens with increasing halo mass over the dynamic range relevant to these galaxy samples \citep[see, e.g., Figure 8 of][and references therein]{hearin_etal16}.
-\item Our posteriors and best-fit parameters summarized in Table \ref{table:parameters} supersede the values published in \citet{zehavi_etal11}, as direct-mock-population together with the Decorated HOD allows us to account for highly significant systematics that have heretofore been neglected from all HOD fits to SDSS data.
-We note that our findings update the original \citet{zehavi_etal11} results {\em even for our fits in which assembly bias has been fixed to zero}, since the original results derive from unconverged MCMC chains that do not sufficiently sample the HOD model posteriors.
+Both the $\magr<-20, -20.5$ samples prefer relatively strong central galaxy assembly bias.
+The $\magr<-19$ sample favors satellite assembly bias.
+Assembly bias in these samples improves the capability of the model to describe galaxy clustering near
+the one-halo to two-halo transition at $r_{\rm p} \sim 2 \, h^{-1}\mathrm{Mpc}$.
+%
+\item The evidence for galaxy assembly bias weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cens}=0$ and $A_{\rm sats}=0.$ This is consistent with the well-established result that
+{\em halo assembly bias} weakens with increasing halo mass over the dynamic range relevant to these galaxy samples 
+\citep[see, e.g., Figure 8 of][and references therein]{hearin_etal16}. 
+%
+\item Our posteriors and best-fit parameters summarized in 
+Table \ref{table:parameters} supersede the values published in \citet{zehavi_etal11}, 
+as direct-mock-population together with the Decorated HOD allows us to account for 
+highly significant systematics that have heretofore been neglected from all HOD fits to SDSS data. 
+We note that our findings update the original \citet{zehavi_etal11} results 
+{\em even for our fits to standard HODs without assembly bias}, because 
+the original results were derived from MCMC chains that did not sufficiently sample the HOD model posteriors. 
+%
 \een
-We conclude by noting that since $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, it is likely that further improvements on assembly bias constraints at low-redshift will require additional observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
+%
+We conclude by noting that since $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7, 
+it is likely that further improvements on assembly bias constraints at low-redshift will require additional 
+observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc. 
+I need to think of a more clever ending.
 
@@
 
+We thank Zheng Zheng for his cooperation in diagnosing the 
+differences between the present analysis and the SDSS DR7 
+analysis presented in \citet{zehavi_etal11}. 
 The authors gratefully acknowledge the Gauss Centre for Supercomputing
@@
 AstroComputing Center (UC-HiPACC) and were run at the NASA Ames
-Research Center. FvdB is supported by the US National Science
-Foundation through grant AST 1516962. {\bf AZ; add yours as well.}
+Research Center. The work of ARZ was supported by the US National Science 
+Foundation via grant AST 1517563. FvdB is supported by the US National Science
+Foundation through grant AST 1516962. APH is funded through his own 
+awesomeness.
 

### 2016-06-15 ms.tex
Noted that Delta chi^2=5.89 is the 1-sigma region for a 5D fit and changed the plots to show samples within Delta chi^2 < 5.89.

@@
 assembly bias while $A_{\rm cen,sat}=1$ ($A_{\rm cen,sat}=-1$) means that galaxy abundance is maximally 
-correlated (anticorrelated) with halo concentration at fixed $\mvir.$ Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 
+correlated (anticorrelated) with halo concentration at fixed $\mvir.$ 
+Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 
 If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified in the table, then the model used to interpret the data 
@@
 covariance (points with errorbars). The grey lines are 50 randomly-selected HOD models that yield 
-$\Delta \chi^2 <1$ compared to the best-fitting model. {\bf Right:} Same as the left panel but using a 
+$\Delta \chi^2 < 5.89$ compared to the best-fitting model. For a Gaussian posterior distribution, 
+$\Delta \chi^2 = 5.89$ would contain 68\% of the probability in the full five-dimensional parameter 
+space. {\bf Right:} Same as the left panel but using a 
 fit to a Decorated HOD model that contain parameters to describe the strength of assembly bias.

### 2016-06-15 ms.tex
Added minor footnote describing Figure 1.

@@
 Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
-analyses. The parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
+analyses. Look for the purple banana \footnote{'til they put us in the truck.} in the upper-left panel of 
+Fig.~\ref{fig:Mr20triangle}. This panel illustrates that the 
+parameters $\log (M_1)$ and $\alpha$ are degenerate with each other and positively 
 correlated. The parameter $M_1$ is the mass scale at which a halo has one satellite on 

### 2016-06-15 ms.tex
Minor edit.
Added non-AB posteriors in AB triangle plots.

@@
 Two degeneracies are manifest in Fig.~\ref{fig:Mr20triangle} that are common to all of our 
-analyses. Look for the purple banana \footnote{'til they put us in the truck.} in the upper-left panel of 
+analyses. Look for the purple banana\footnote{'til they put us in the truck.} in the upper-left panel of 
 Fig.~\ref{fig:Mr20triangle}. This panel illustrates that the 
@@
   sample. The contours and histograms along the diagonal panels are as
-  in Fig.~\ref{fig:Mr20triangle}. The decorated HOD models include a
+  in Fig.~\ref{fig:Mr20triangle}. The dashed line in the panels along the diagonal 
+  show the posteriors on these parameters from the standard analysis without 
+  any parameterization of galaxy assembly bias. The decorated HOD models include a
   two-parameter model for assembly bias. The HOD parameter $\log

### 2016-06-15 ms.tex
Moved the purple banana to the panel that resembles a banana a bit better.

--- 2016-06-15 ms.tex
@@
 
-As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
-share a relatively narrow degeneracy as well. This degeneracy is largely induced by the 
-measured number density of the sample. Increasing $\log (M_{\rm min})$ decreases galaxy 
+Look for the purple banana\footnote{'Til they put us in the truck.} in the third panel from the left in the bottom row of 
+Figure~\ref{fig:Mr20triangle}. This panel illustrates that the parameters 
+$\log (M_{\rm min})$ and $\sigma_{\log M}$ share a relatively narrow degeneracy as well. 
+This degeneracy is largely induced by the measured 
+number density of the sample. Increasing $\log (M_{\rm min})$ decreases galaxy 
 number density, but this can be compensated by an increase in $\sigma_{\log M}$, which 

### 2016-06-15 ms.tex
Minor changes to wording in sections 1 and 2.

@@
   assembly bias in the $\magr<-21$ sample. Because the Decorated HOD
-  subsumes the traditional HOD, and additionally because of errors
-  made in the original analysis of these samples, our results differ
-  from and supersede existing HOD constraints from low-redshift
+  subsumes the traditional HOD, and additionally because the original 
+  \citet{zehavi_etal11} analysis did not sufficiently sample the posterior distributions, 
+ our results differ from and supersede existing HOD constraints from low-redshift
   clustering measurements.
@@
 This work presents a re-analysis of the SDSS DR7 data that 
-overcomes numerous shortcomings of previous analyses. 
-Our analysis improvements stem primarily from our 
+overcomes numerous shortcomings of previous studies. 
+The main improvements accomplished by our approach stem primarily from our 
 directly populating mock galaxy catalogs into a cosmological simulation, 
@@
 specified in Table~\ref{table:priors}. In the case of the assembly bias parameters 
-$A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$, the priors represent physical 
-boundaries. These parameters must satisfy $-1 \le A_{\mathrm{cen,sat}} \le 1$. 
+$A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$, the priors have strict  
+boundaries. Mathematically, these parameters must satisfy $-1 \le A_{\mathrm{cen,sat}} \le 1$. 
 Physical considerations require parameter $\sigma_{\log M} > 0$. All other 

### 2016-06-16 ms.tex
A few more minor grammatical changes

@@
 review the salient features of our methodology briefly;
-interested readers can always refer to {\tt halotools.readthedocs.io} and 
+interested readers can always refer to {\tt http://halotools.readthedocs.io} and
 \citet{hearin_etal16} for further details.
@@
 estimator to turn pair counts into a $\wprp$ prediction, as described
-in detail in {\tt halotools.readthedocs.io}.
+in detail in {\tt http://halotools.readthedocs.io}.
 
@@
 correlated (anti-correlated) with halo concentration. The model and its implementation
-in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above and 
+in {\tt Halotools} is discussed further in Section~\ref{subsection:decorated} above and
 in more detail in \citet{hearin_etal16}.

### 2016-06-16 ms.tex
Added funding statement for APH
Added ms.pdf to repository. Small grammatical changes to introduction.

@@
 \author[Zentner et al.]
-{Andrew R. Zentner$^{1}$, Andrew P. Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
-Antonio Villareal$^{1}$, Johannes U. Lange$^{3}$, P. Rogers Nelson$^{4}$\\ \\
+{Andrew R. Zentner$^{1}$, Andrew Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
+Antonio Villareal$^{1}$, Johannes U. Lange$^{3}$, Kuan Wang$^{1}$, and P. Rogers Nelson$^{4}$\\ \\
 $^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
@@
 (2) galaxies occupy halos as a function of halo mass $\mvir$ only. 
+In this paper, we present the first analysis of large-scale clustering using 
+a halo occupation model that violates the second assumption and permits 
+galaxies to occupy halos as a function of multiple halo properties.
 
-It is now well known that halo bias depends upon halo properties other than $\mvir$
+It is now well known that the strength of halo clustering, the halo bias, 
+depends upon halo properties other than $\mvir$
 \citep[e.g.][]{gao_etal05,wechsler06,gao_white07,zentner07,dalal_etal08,lacerna11},
-an effect called halo assembly bias. If galaxies occupy halos as a
+an effect called {\em halo assembly bias}. If galaxies occupy halos as a
 function of halo properties other than $\mvir,$ then standard halo
-occupation methods will be subject to a systematic error due to galaxy
-assembly bias.
-Several of us have previously shown that this error can
-be significant in an analysis of galaxy clustering and can bias
-inferences about many aspects of galaxy evolution
-\citep{zentner_etal14}.
+occupation methods will be subject to a systematic error due to 
+{\em galaxy assembly bias}. Several of us have previously shown 
+that this error can be significant in an analysis of galaxy clustering 
+and can bias inferences about many aspects of galaxy evolution \citep{zentner_etal14}.
 
@@
 presented evidence for the presence of assembly bias in massive
-clusters; in particular, they find that clusters with a more
-concentrated distribution of satellite galaxies exhibit a weaker large-scale bias
-relative to clusters of the same mass with satellite galaxies that
-are less centrally concentrated.
+clusters; in particular, they find that clusters with a more centrally concentrated 
+distribution of satellite galaxies cluster more weakly than clusters with more 
+diffuse satellite galaxy distributions at fixed cluster mass. Indeed, \citet{more_etal16} 
+suggest that the observed galaxy bias is considerably stronger than had been 
+expected based on $N$-body simulations coupled with simple models for the 
+galaxy--halo connection, such as subhalo abundance matching. 
 Additional support for the presence of assembly bias has come from a
@@
 \citet{tinker08b} argue that measurements of void statistics place strong
-bounds on the possible strength of the signal.
+bounds on the possible strength of the signal, though 
+\citet{zentner_etal14} constructed an explicit example refuting this 
+claim.
 
@@
 Models that include assembly bias such as semi-analytic models
-are typically too computationally expensive
-for anything besides a ``one-off" comparison \citep[e.g.,][]{croton_etal07}, prohibiting
-any conclusive statement to be made about the strength of the signal.
+are typically too computationally expensive to compare to data in a manner 
+that enables statistical constraints on model parameters. Such models are usually 
+compared to data on a case-by-case basis \citep[e.g.,][]{croton_etal07}, prohibiting
+any conclusive statement to be made about the strength of any assembly bias signal.
 
@@
 Foundation via grant AST 1517563. FvdB is supported by the US National Science
-Foundation through grant AST 1516962. APH is funded through his own
-awesomeness.
+Foundation through grant AST 1516962. APH is funded through the Yale Center 
+for Astronomy \& Astrophysics Prize fellowship.
 

### 2016-06-16 ms.tex
Completed editing the Introduction.

@@
 7 (DR7) data, analyzed previously by \citet{zehavi_etal11}, in the
-context both standard halo occupation models and these new models.
+context of both standard halo occupation models and these new models 
+that permit parameterized galaxy assembly bias.
 
@@
 overcomes numerous shortcomings of previous studies.
-The main improvements accomplished by our approach stem primarily from our
-directly populating mock galaxy catalogs into a cosmological simulation,
+The primary improvements of our approach stem from the fact that we 
+directly populate mock galaxy catalogs within a cosmological simulation,
 whereas previous analyses relied upon analytical fitting functions
@@
 In direct mock population, delicate issues present in analytic
-modeling, such as scale-dependent halo bias and halo exclusion, are treated exactly.
-Our approach also provides a natural framework for studying models of assembly bias,
-since we can use the exact clustering properties of simulated halos as a function of
-any arbitrary halo properties in the catalog. With direct mock population,
-systematic uncertainty in the model is limited to
-the sample variance of the simulated box,
-errors related to insufficient numerical resolution,
-and numerical inaccuracies of halo-finding (e.g., over-merging).
+modeling, such as scale-dependent halo bias and halo exclusion, 
+are treated exactly. 
+Our approach also provides a natural framework for studying 
+models of assembly bias, because we can use the exact clustering 
+properties of simulated halos as a function of
+any arbitrary halo properties in the catalog. It is not necessary to develop 
+new phenomenological models or fitting functions to deal with this additional 
+complexity. With direct mock population, systematic uncertainty in the 
+model is limited to the sample variance of the simulated box, errors related 
+to insufficient numerical resolution, and numerical inaccuracies of 
+halo-finding \citep[e.g., overmerging][]{klypin99a,rockstar}.
 
-In addition to improvements from direct mock population,
+In addition to improvements resulting from direct mock population,
 the simulation we use is based on the latest Planck cosmological
 parameters \citep{planck13}, updating previous work.
-Furthermore, many important
-differences between this work and the previous analysis by
-\citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
-Chains used in \citet{zehavi_etal11} did not sufficiently sample the
-posterior distribution (Z. Zheng \& I. Zehavi, private communication).  Therefore,
-{\em our analysis supersedes previous work even in the case of
+Furthermore, many important differences between this work 
+and the previous analysis by \citet{zehavi_etal11} result from 
+the fact that the Monte Carlo Markov Chains used in \citet{zehavi_etal11} did not 
+sufficiently sample the posterior distribution (Z. Zheng, private communication). 
+The result is that the constraints in \citet{zehavi_etal11} are overly restrictive, considerably so 
+in some cases, and potentially biased. 
+Therefore, {\em our analysis supersedes previous work even in the case of
 standard halo occupation models}.

### 2016-06-16 ms.tex
Edited section 2, adding many details and citing CorrFunc.

@@
 {Andrew R. Zentner$^{1}$, Andrew Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
-Antonio Villareal$^{1}$, Johannes U. Lange$^{3}$, Kuan Wang$^{1}$, and P. Rogers Nelson$^{4}$\\ \\
+Johannes U. Lange$^{3}$, and P. Rogers Nelson$^{4}$\\ \\
 $^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
@@
 (2) galaxies occupy halos as a function of halo mass $\mvir$ only. 
-In this paper, we present the first analysis of large-scale clustering using 
-a halo occupation model that violates the second assumption and permits 
-galaxies to occupy halos as a function of multiple halo properties.
+In this paper, we present the first analysis of galaxy clustering using 
+a halo occupation model that violates the second of these assumptions 
+and permits galaxies to occupy halos as a function of multiple halo properties.
 
@@
 
-To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
-We explore halo occupation distribution models (HOD) models in this work
+To generate predictions for galaxy clustering, 
+we populate dark matter halos with mock galaxies using the publicly-available, 
+open source, {\tt Halotools} software \citep{halotools}.
+We explore halo occupation distribution (HOD) models in this work
 \citep[e.g.][]{seljak00,ma_fry00,scoccimarro01a,berlind02}, though other
@@
 All of our analyses are based on the Bolshioi-Planck (BolshioP) simulation \citep{riebe_etal11}.
-BolshoiP was run with cosmological parameters based on \citet{planck13},
-$\Omega_{\Lambda} = 0.693, \Omega_{\rm m} = 1 - \Omega_{\Lambda} = 0.307, \Omega_{\rm b} = 0.048,
-h = 0.7, {\rm n_s}=0.96$ and $\sigma_8 = 0.82,$ within a cubic box
-$250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$
+BolshoiP was run with cosmological parameters based on \citet{planck13}:
+$\Omega_{\Lambda} = 0.693; \Omega_{\rm m} = 1 - \Omega_{\Lambda} = 0.307; \Omega_{\rm b} = 0.048;
+h = 0.7; {\rm n_s}=0.96$; and $\sigma_8 = 0.82$. BolshoiP simulated the formation of structure within a cubic 
+box $250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$
 Further information about the BolshoiP simulation is available at \url{https://www.cosmosim.org}.
@@
 density contrast given in \citet{bryan_norman98}. When populating this catalog with mock galaxies, we only use
-present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles.
+present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles. The minimum 
+peak halo mass considered in our analysis has $M_{\rm peak} \ge 4.05 \times 10^5\, h^{-1}\mathrm{M}_{\odot}$ 
+and this prevents us from analyzing samples with $M_r > -19$.
 
@@
 \label{eq:ncen}
-\langle N_{\mathrm{cen}} \rangle(\mvir) =
+\langle N_{\mathrm{cen}} \vert \mvir \rangle =
         \frac{1}{2}\left( 1 +
@@
 %
-For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \rangle(\mvir);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(\mvir)$ are left devoid of centrals.
+For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \vert \mvir \rangle;$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \vert \mvir \rangle$ are left devoid of centrals.
 The parameter $\log (M_{\rm min})$ specifies the halo mass at which the halo has a 50\% probability of hosting a
-central galaxy, while the parameter $\sigma_{\log M}$ specifies the rate at which $\langle N_{\mathrm{cen}} \rangle (\mvir)$
+central galaxy, while the parameter $\sigma_{\log M}$ specifies the rate at which $\langle N_{\mathrm{cen}} \vert \mvir \rangle$
 transitions from zero to unity, with smaller values of $\sigma_{\log M}$ corresponding to a more rapid transition.
@@
 \label{eq:nsat}
-\langle N_{\rm sat}\rangle(\mvir) = \left( \frac{\mvir - M_0}{M_1} \right)^{\alpha}.
+\langle N_{\rm sat}\vert \mvir \rangle = \left( \frac{\mvir - M_0}{M_1} \right)^{\alpha}.
 \end{equation}
@@
 The parameter $M_0$ allows the power-law to be truncated more rapidly at low masses and we
-set $\langle N_{\rm sat}\rangle (\mvir) = 0$ for $\mvir < M_0$.
+set $\langle N_{\rm sat}\vert \mvir \rangle = 0$ for $\mvir < M_0$.
 
@@
 vary along a narrow degeneracy that fixes the total galaxy number density to the observed value. There are
-many particular choices that can be made for the functional forms of $\langle N_{\rm cen}\rangle (\mvir)$ and
-$\langle N_{\rm sat}\rangle (\mvir)$. We have made choices that mimic the standard SDSS DR7 analysis of
-\citet{zehavi_etal11}, to expedite comparisons with their results.
+many particular choices that can be made for the functional forms of $\langle N_{\rm cen}\vert \mvir \rangle$ and
+$\langle N_{\rm sat}\vert \mvir \rangle$. We have made choices that mimic the standard SDSS DR7 analysis of
+\citet{zehavi_etal11}, to expedite comparisons with their results. However, our choice does deviate from 
+the choice of \citet{zehavi_etal11} in one respect. The mean satellite occupation of \citet{zehavi_etal11} 
+is that of Eq.~(\ref{eq:nsat}) multiplied by an overall factor of $\langle N_{\rm cen} \vert \mvir \rangle$. 
+We have chosen not to use this as our default because it can introduce difficulties in some analyses 
+\citep[see the discussion of blue galaxy samples in][]{zentner_etal14} and because, as we have verified 
+explicitly, the extra factor introduces only small quantitative changes to our results and no qualitative 
+changes.
 
@@
 $z_{\rm RS} = z + V_{\rm z}/H_0.$ We count pairs of points in each of
-our $\rp$ bins, rejecting pairs with $z_{\rm RS}-$ distance exceeding
-$\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection
-depth chosen by \citet{zehavi_etal11}. We employ the \citet{landyszalay93}
-estimator to turn pair counts into a $\wprp$ prediction, as described
-in detail in {\tt http://halotools.readthedocs.io}.
+our $\rp$ bins, rejecting pairs with line-of-sight distances in redshift space, $\Delta z_{\rm RS}$, 
+exceeding $\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection
+depth chosen by \citet{zehavi_etal11}. Having populated mocks, 
+we perform the computation of the projected two-point galaxy correlation 
+function, $w_{\rm p}(r_{\rm p})$ using the publicly-available {\tt CorrFunc} 
+package \citep{corrfunc} which has been extensively optimized for computational speed.
 
@@
 when averaged over all halos at fixed mass, as standard HOD
-models}. The only change in Decorated HOD models is whether or not an
+models with the same five standard HOD parameters}. 
+The only change in Decorated HOD models is whether or not an
 additional property also modulates halo occupation at fixed halo
@@
 and the last term in Eq.~(\ref{eq:chisquare}) is the contribution from the difference between the predicted and measured
-galaxy number density. The error on the galaxy number density assumes Poisson statistics for both the measured and predicted
-galaxy number densities.
+galaxy number density. The error on the galaxy number density assumes Poisson statistics for both the measured and predicted galaxy number densities.
 

### 2016-06-16 ms.tex
Significant edits to Section 3.1

@@
 
-We have performed parameter inference analyses in order to infer the underlying HOD of
+We have performed parameter inference analyses in order to infer the underlying HODs of
 galaxies from the projected galaxy two-point function $\wprp(\rp)$ as described in the preceding
@@
 Prior to discussing our results using models that include assembly bias, we present
-results of standard HOD analyses that include no model for assembly bias. The results of
-the standard HOD analyses and all other analyses are shown in the form of marginalized
-constraints on individual parameters in Table~\ref{table:parameters}. We compare our parameter
-constraints to the standard HOD analysis performed by \citet{zehavi_etal11} in Table~\ref{table:parameters}
-as well. An example of the inferred posteriors for the HOD parameters is shown in Figure~\ref{fig:Mr20triangle}.
+results of standard HOD analyses that include no treatment of assembly bias. 
+In our standard HOD analyses, the parameters $\log (M_{\rm min})$,
+$\sigma_{\log M}$, $\alpha$, $\log (M_1)$, and $\log (M_0)$ are permitted to vary. 
+The results of the standard HOD analyses and all other analyses are shown in the form of 
+marginalized constraints on individual parameters in Table~\ref{table:parameters}. Though the quality of 
+our fits, as measured by the minimum of $\chi^2$ per Degree of Freedom (DoF), varies from case to case, 
+all fits have a probability $\gtrsim 1\% $ of obtaining a higher value of $\chi^2$ by chance.
+An example of the inferred posteriors for the HOD parameters is shown in Figure~\ref{fig:Mr20triangle} for the sample with $\magr < -20$.
+We do
+not show the full posteriors for all five threshold samples in the interest of brevity.
 The left-hand panels of Figure~\ref{fig:Mr19samples}, Figure~\ref{fig:Mr20samples}, and Figure~\ref{fig:Mr21samples}
 show the projected correlation function data along with predictions for $\wprp(\rp)$ from 50 randomly-selected
-models from the MCMC chains within $\Delta \chi^2 \le 1$ of the best-fit model.
-Note that the significant covariance in the data makes it difficult to
-determine the quality of fit from visual inspection of these figures.
+models from the MCMC chains within $\Delta \chi^2 \le 5.89$ of the best-fit model. Under the assumption of 
+a Gaussian posterior distribution, $\Delta \chi^2 = 5.89$ contains 68\% of the posterior probability for a 
+five-parameter model. Note that the significant covariance in the data makes it difficult to
+determine the quality of fits from visual inspection of these figures.
 
@@
 
+Our parameter constraints can be compared to the standard HOD analysis performed by \citet{zehavi_etal11} 
+by examining the top two rows in each luminosity threshold grouping in Table~\ref{table:parameters}. 
 The inferred parameters from our standard analyses differ in several ways from the \citet{zehavi_etal11}
@@
 Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$
-If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified in the table, then the model used to interpret the data
+If the constraints on $A_{\rm cen}$ and $A_{\rm sat}$ are unspecified in the table, 
+then the model used to interpret the data
 does not include assembly bias. In our analyses, quoted parameter values with errors correspond to the median
@@
 
-Additionally, we have confirmed with a subset of the authors of \citet{zehavi_etal11}
+We have confirmed with one of the authors of \citet{zehavi_etal11}
 that the MCMC chains used in a number of their analyses may not have been
@@
 uncertainties on the inferred parameters, especially $\log (M_0)$, $\log (M_{\rm min})$,
-and $\sigma_{\log M}$ (Z. Zheng, private communication). The analysis of \citet{zehavi_etal11}
-used $10^4$ samples, whereas we find several $\times 10^6$ samples are often necessary for convergence.
-The cause of the problem is likely a restrictive proposal distribution that causes the chain to
-diffuse through the posterior distribution only very slowly. We have recreated qualitatively similar
-behavior by considering only small subsets of our full MCMC chains. Consequently, insufficient
-sampling of the posterior seems to be the likely resolution
+and $\sigma_{\log M}$. The analysis of \citet{zehavi_etal11}
+used $10^4$ samples, whereas we find that several $\times 10^5$ to $10^6$ 
+samples are often necessary for convergence. In all cases, our final results are from 
+$>10^6$ samples of the posterior. The cause of the problem is likely a 
+restrictive proposal distribution that causes the chain to
+diffuse through the posterior distribution only extremely slowly (Z. Zheng, Private Communication). 
+We have recreated qualitatively similar behavior considering only small subsets of our full 
+MCMC chains. Consequently, insufficient sampling of the posterior seems to be the likely resolution
 of the discrepancies between our work and that of \citet{zehavi_etal11}.
@@
 number on halo mass. Increasing $M_1$ {\em decreases} the number of satellites in massive halos
-by increasing the mass scale where the power law abundance becomes operative. An increase in $\alpha$ can partly
-compensate for an increase in $M_1$ by increasing the rate at which average satellite number
+by increasing the mass scale where the power law abundance becomes operative. 
+An increase in $\alpha$ can partly
+compensate for an increase in $M_1$ by increasing 
+the rate at which average satellite number
 grows with halo mass.
 
-Look for the purple banana\footnote{'Til they put us in the truck.} in the third panel from the left in the bottom row of
-Figure~\ref{fig:Mr20triangle}. This panel illustrates that the parameters
+Look for the purple banana\footnote{'Til they put us in the truck.} in the third panel from the left in 
+the bottom row of Figure~\ref{fig:Mr20triangle}. This panel illustrates that the parameters
 $\log (M_{\rm min})$ and $\sigma_{\log M}$ share a relatively narrow degeneracy as well.
@@
 differences between the present analysis and the SDSS DR7
-analysis presented in \citet{zehavi_etal11}.
+analysis presented in \citet{zehavi_etal11}. We thank Manodeep 
+Sinha for help installing and running the {\tt CorrFunc} package 
+as well as comments on an earlier draft of this manuscript.
 The authors gratefully acknowledge the Gauss Centre for Supercomputing

### 2016-06-16 ms.tex
Edited Section 3.2

@@
 We turn now to a discussion of our parameter inference analysis of projected galaxy clustering
-in Decorated HOD models that include a treatment of galaxy assembly bias. In this work,
+in decorated HOD models that include a treatment of galaxy assembly bias. In this work,
 we consider only the simplest model of galaxy assembly bias, introducing only two new
@@
 correlated (anti-correlated) with halo concentration. The model and its implementation
-in {\tt Halotools} is discussed further in Section~\ref{subsection:decorated} above and
-in more detail in \citet{hearin_etal16}.
+in {\tt Halotools} \cite{halotools} is discussed further in Section~\ref{subsection:decorated} above 
+and in more detail in \citet{hearin_etal16}.
 
@@
 of the predicted two-point functions to match the measured two-point functions across the
-transition from the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$.
+transition from the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near 
+$\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$, an effect that could be anticipated by the known 
+scale-dependence of galaxy assembly bias \citep{sunayama_etal16}. 
 This is most apparent for the $M_r < -20$ threshold sample shown in Fig.~\ref{fig:Mr20samples}.
@@
 are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}.
-In cases where the posterior on a parameter is monotonic within the physical parameter
-range, we quote an upper or lower limit on the parameter. Examples of one- and two-dimensional
-visualizations of the posteriors from our analyses are shown in Figure~\ref{fig:Mr19ABtriangle},
-Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle} for the
-$M_r<-19$, $M_r<-20$, and $M_r<-21$ samples respectively.
+In cases where the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ is a monotonic within 
+the physical parameter range, we quote an upper or lower limit on the parameter 
+(e.g., see the posterior distribution for $A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}). 
+Examples of one- and two-dimensional visualizations of the posteriors from our analyses are shown in 
+Figure~\ref{fig:Mr19ABtriangle}, Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle} 
+for the $M_r<-19$, $M_r<-20$, and $M_r<-21$ samples respectively.
 
@@
 all make several simple, generic points. Introducing additional parameter
-freedom associated with galaxy assembly bias generally increases the viable parameter
-space, even for the subset of standard HOD parameters. Constraints on the
-standard HOD parameters are generally less restrictive. This is exactly what is
-expected from the introduction of additional parameter freedom.
+freedom associated with galaxy assembly bias generally increases the volume of the 
+viable parameter space, even for the subset of five standard HOD parameters. 
+Constraints on the standard HOD parameters are generally less restrictive in models that 
+include assembly bias. This is exactly what is expected from the introduction of additional 
+parameter freedom.
 
@@
 assembly bias. This is an explicit example of the degree to which the inferred relationship
-between galaxies and halos can be altered by assembly bias.
+between galaxies and halos can be altered by assembly bias. In this case, the efficiency 
+of forming a sufficiently luminous galaxy is a function that increases slowly over nearly two 
+decades in halo mass in contrast to a standard analysis HOD where this efficiency rises 
+rapidly over roughly one third of a decade in $\mvir$. Taking these results at face value, 
+the reason that the HOD of central galaxies can vary slowly over several orders of magnitude 
+in $\mvir$ is that larger galaxies form more efficiently in high-concentration halos at fixed 
+mass.
 
@@
 for the $M_r < -21$ threshold sample, for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$
-are consistent with zero well within 1$\sigma$.
+are consistent with zero well within 1$\sigma$. The implications of all of these results are too numerous 
+to address in the present manuscript; however, we plan to address them in forthcoming publications.
 
@@
  }
- \label{table:priors}
+ \label{table:bic}
  \end{center}
@@
 %------------------------------------------------
-\bibliography{ms.bib}
+\bibliography{ms}
 

### 2016-06-16 ms.tex
Added discussion of Bayesian Information Criterion.

@@
 \usepackage[dvipsnames]{xcolor}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 \usepackage{yfonts}
 
-\usepackage{epsfig}  \usepackage{graphicx}   \usepackage{rotating}
+\usepackage{epsfig}  
+\usepackage{graphicx}  
+\usepackage{rotating}
 
@@
 box $250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$
-Further information about the BolshoiP simulation is available at \url{https://www.cosmosim.org}.
+Further information about the BolshoiP simulation is available at {\tt https://www.cosmosim.org}.
 
@@
 
+Beyond the fit results, it is also possible to ask whether or not the fits to the data warrant the use of 
+additional parameters (in this case, to describe assembly bias). This requires a metric that penalizes the 
+use of additional parameters. A commonly used metric is the Bayesian Information Criterion 
+\citep[BIC,][]{schwarz78}, defined as 
+%
+\begin{equation}
+\mathrm{BIC} = -2 \mathcal{L}_{\rm max} + k\, \ln N, 
+\end{equation}
+%
+where $\mathcal{L}_{\rm max}$ is the maximum of the likelihood, 
+$k$ is the number of paramters in the model and $N$ is the number of 
+data points. We compute the change in the BIC, $\Delta$BIC, by subtracting 
+the BIC for the analysis with assembly bias from the BIC in the standard analysis 
+in which there is no assembly bias. With this convention, $\Delta \mathrm{BIC} > 0$ 
+favors assembly bias, suggesting that the data warrant the additional parametric freedom. 
+Conversely, $\Delta \mathrm{BIC} < 0$ favors the standard analysis, 
+suggesting that the additional freedom in the model does not improve the description of the data 
+to a sufficiently great degree to support the added complexity. 
+A common convention is to refer to the preference as 
+{\em strong} when $\vert \Delta \mathrm{BIC}\vert \ge 5$.
+
+The values of $\Delta$BIC are given in Table~\ref{table:bic}. In the analysis of the $\magr < -21$ sample, 
+$\Delta \mathrm{BIC} < 0$, indicating that the additional parameters describing assembly bias are not 
+warranted by the data. For all other samples, $\Delta \mathrm{BIC} > 0$, showing a preference for 
+the models with assembly bias. The cases that most support the additional complexity 
+of the decorated HOD are $\magr < -19$ and $\magr < -20$, for which $\Delta$BIC 
+rises nearly to the level of a {\rm strong} preference.
+
 %------------------------------------------------

### 2016-06-16 ms.tex
Edited abstract. Removed hyperref because it is throwing an error.

@@
 \begin{abstract}
-  We constrain the newly-introduced Decorated HOD model using SDSS DR7
-  measurements of projected galaxy clustering, $\wprp,$ and number
-  density, $n_{\rm g},$ made from r-band luminosity-threshold
-  samples. The Decorated HOD is a model for the galaxy--halo
-  connection that augments the traditional Halo Occupation
-  Distribution (HOD) by allowing for the possibility of {\em assembly
-    bias}: galaxy luminosity may be correlated with dark matter halo
-  properties besides virial mass $\mvir$ alone. We demonstrate that it
-  is not possible to rule out assembly bias using DR7 measurements of
-  $\wprp$ and $n_{\rm g}.$ Moreover, galaxy samples $\magr<-20, -20.5$
-  favor strong levels of central galaxy assembly bias:
-  high-concentration halos are more likely to host a central galaxy
+  We constrain the newly-introduced decorated Halo Occupation Distribution (HOD) 
+  model using SDSS DR7 measurements of projected galaxy clustering, $\wprp (r_{\rm p})$ 
+  of galaxies in r-band luminosity-threshold samples. 
+  The decorated HOD is a model for the galaxy--halo
+  connection that augments the traditional HOD by allowing for the possibility of 
+  {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo
+  properties besides mass, $\mvir$. We demonstrate that it
+  is not possible to rule out galaxy assembly bias using DR7 measurements of galaxy 
+  clustering alone. Moreover, galaxy samples $\magr<-20, -20.5$
+  favor strong levels of central galaxy assembly bias. Our analyses favor models 
+  in which high-concentration halos are more likely to host a central galaxy
   relative to low-concentration halos of the same $\mvir.$ We rule out
   zero assembly bias with high significance for these
-  samples. Satellite assembly bias only becomes significant for the
+  samples. Satellite galaxy assembly bias is significant for the
   faintest sample we study, $\magr<-19.$ We find no evidence for
-  assembly bias in the $\magr<-21$ sample. Because the Decorated HOD
-  subsumes the traditional HOD, and additionally because the original
-  \citet{zehavi_etal11} analysis did not sufficiently sample the posterior distributions,
- our results differ from and supersede existing HOD constraints from low-redshift
-  clustering measurements.
+  assembly bias in the $\magr<-21$ sample. In addition to presenting the 
+  constraints on HOD models that accommodate assembly bias, our analysis 
+  includes numerous improvements over previous analyses of this data set and 
+  supersedes existing constraints even on standard HOD parameters.
 \end{abstract}

### 2016-06-17 ms.tex
Added note about arbitrary ngal error in Zehavi+11, Added note about Zehavi+11 using FoF halos whereas we use virial.

@@
   clustering alone. Moreover, galaxy samples $\magr<-20, -20.5$
-  favor strong levels of central galaxy assembly bias. Our analyses favor models 
+  favor strong levels of central galaxy assembly bias. These samples favor models 
   in which high-concentration halos are more likely to host a central galaxy
@@
   faintest sample we study, $\magr<-19.$ We find no evidence for
-  assembly bias in the $\magr<-21$ sample. In addition to presenting the 
+  assembly bias in the $\magr<-21$ sample. In addition to presenting the first 
   constraints on HOD models that accommodate assembly bias, our analysis 
   includes numerous improvements over previous analyses of this data set and 
-  supersedes existing constraints even on standard HOD parameters.
+  supersedes previously published results, even in the case of a standard HOD analysis.
 \end{abstract}
@@
 %
-For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ a central galaxy is assigned to the halo if the associated random number is less than $\langle N_{\mathrm{cen}} \vert \mvir \rangle;$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \vert \mvir \rangle$ are left devoid of centrals.
-The parameter $\log (M_{\rm min})$ specifies the halo mass at which the halo has a 50\% probability of hosting a
-central galaxy, while the parameter $\sigma_{\log M}$ specifies the rate at which $\langle N_{\mathrm{cen}} \vert \mvir \rangle$
-transitions from zero to unity, with smaller values of $\sigma_{\log M}$ corresponding to a more rapid transition.
+For every host halo in the catalog we draw a random number from a uniform 
+distribution $\mathcal{U}(0, 1);$ for a host halo of present-day virial mass $\mvir,$ 
+a central galaxy is assigned to the halo if the associated random number is less 
+than $\langle N_{\mathrm{cen}} \vert \mvir \rangle;$ halos with random values 
+exceeding  $\langle N_{\mathrm{cen}} \vert \mvir \rangle$ are left devoid of centrals.
+The parameter $\log (M_{\rm min})$ specifies the halo mass at which the halo 
+has a 50\% probability of hosting a
+central galaxy, while the parameter $\sigma_{\log M}$ specifies the rate at 
+which $\langle N_{\mathrm{cen}} \vert \mvir \rangle$
+transitions from zero to unity, with smaller values of $\sigma_{\log M}$ 
+corresponding to a more rapid transition.
 
@@
 and the last term in Eq.~(\ref{eq:chisquare}) is the contribution from the difference between the predicted and measured
-galaxy number density. The error on the galaxy number density assumes Poisson statistics for both the measured and predicted galaxy number densities.
+galaxy number density. In Eq.~(\ref{eq:chisquare}), the we adopt the Einstein summation convention and sum over the 
+dummy indices $i$ and $j$. The error on the galaxy number density assumes Poisson statistics for both the measured and predicted galaxy number densities.
 
@@
 Physical considerations require parameter $\sigma_{\log M} > 0$. All other
-priors have a negligible influence on the posterior aside from $\log M_0$.
-We find that $\log M_0$ is often very poorly constrained by clustering data and
-priors on $\log M_0$ can have a non-negligible influence on inferred parameters.
+priors have a negligible influence on the posterior aside from $\log M_0$ and 
+$\sigma_{\log M}$. We find that $\log M_0$ is often very poorly constrained by clustering data and
+priors on $\log M_0$ can have a non-negligible influence on inferred parameters. The parameter 
+$\sigma_{\log M}$ is poorly constrained for the $\magr < -19$ sample.
 
@@
 all fits have a probability $\gtrsim 1\% $ of obtaining a higher value of $\chi^2$ by chance. 
-An example of the inferred posteriors for the HOD parameters is shown in Figure~\ref{fig:Mr20triangle} for the sample with $\magr < -20$.
-We do
+An example of the inferred posteriors for the HOD parameters is shown in 
+Figure~\ref{fig:Mr20triangle} for the sample with $\magr < -20$. We do 
 not show the full posteriors for all five threshold samples in the interest of brevity.
@@
 Our parameter constraints can be compared to the standard HOD analysis performed by \citet{zehavi_etal11} 
-by examining the top two rows in each luminosity threshold grouping in Table~\ref{table:parameters}. 
+by examining the top two rows in each luminosity threshold grouping in Table~\ref{table:parameters}. In all 
+cases, we quote the medians of our posteriors as our central values and our, 
+generally asymmetric, errorbars, give the 16$^{\rm th}$ and 
+84$^{\rm th}$ percentiles of the posterior samples so as to correspond roughly with ``$1-\sigma$" errors. 
 The inferred parameters from our standard analyses differ in several ways from the \citet{zehavi_etal11}
@@
 Slightly larger mass scales are necessary in an analysis with higher $\Omega_{\rm M}$ and $\sigma_8$ in order
-to maintain galaxy number densities fixed with larger halo number densities.
+to maintain galaxy number densities fixed with larger halo number densities. A detailed comparison between our central 
+values and those of \citet{zehavi_etal11} is further confounded by the fact that we use a virial halo definition, 
+whereas the analytic model of \citet{zehavi_etal11} 
+has been calibrated to friend-of-friends halo masses (Z. Zheng, Private Communication).
 
@@
 at the lower end, because the value of $M_0$ does not alter the
-predicted satellite number once $M_0 \ll M_1$. Therefore, it seems
-likely that the tighter constraints quoted by \citet{zehavi_etal11}
-must be an error.
+predicted satellite number once $M_0 \ll M_1$. The tighter constaints are also 
+particularly puzzling given that \citet{zehavi_etal11} adopt an arbitrary 5\% error on 
+all galaxy number density measurements, an error that greatly exceeds the 
+Poisson error, typically $< 1\%$, that we adopt. This additional error 
+contribution also limits the value of comparing our $\chi^2$ values with those of 
+\citet{zehavi_etal11}, as the latter values will be artificially lower. 
+Therefore, it seems likely that the tighter constraints quoted by \citet{zehavi_etal11}
+must be caused by an error.
 
@@
 In this work, we provide the first quantitative constraints on
-assembly bias derived from the Decorated HOD. We enumerate our most important conclusions below.
+assembly bias derived from the Decorated HOD. 
+We enumerate our most important conclusions below.
 %

### 2016-06-17 ms.tex
Changes to Sections 1-2
Main changes:

adding summation sign to eq. (4)

adding more specifics about Decorated HOD implementation

correction of typos

--- 2016-06-16 ms.tex
@@
 complexity. With direct mock population, systematic uncertainty in the 
-model is limited to the sample variance of the simulated box, errors related 
-to insufficient numerical resolution, and numerical inaccuracies of 
-halo-finding \citep[e.g., overmerging][]{klypin99a,rockstar}.
+model is limited to the sample variance of the simulated box,
+numerical inaccuracies of halo-finding, and errors related 
+to insufficient numerical resolution \citep[e.g., overmerging; ][]{klypin99a,rockstar}.
 
@@
 
-All of our analyses are based on the Bolshioi-Planck (BolshioP) simulation \citep{riebe_etal11}.
+All of our analyses are based on the Bolshoi-Planck (BolshoiP) simulation \citep{riebe_etal11}.
 BolshoiP was run with cosmological parameters based on \citet{planck13}:
@@
         \frac{1}{2}\left( 1 +
-        \mathrm{erf}\left( \frac{\log (\mvir) -
-        \log (M_{\rm min})}{\sigma_{\log M}} \right) \right)
+        \mathrm{erf}\left[ \frac{\log (\mvir) -
+        \log (M_{\rm min})}{\sigma_{\log M}} \right] \right)
 \end{equation}
@@
 Gaussian with first moment equal to the host halo velocity and second
-moment equal to the solution to the isotropic Jeans equation for an
+moment equal to the solution of the isotropic Jeans equation for an
 NFW profile \citep{more09b},
@@
 exceeding $\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection
-depth chosen by \citet{zehavi_etal11}. Having populated mocks, 
+depth chosen by \citet{zehavi_etal11}, both in their analysis of the SDSS
+DR7 data and in their modeling. Finally, having populated mocks, 
 we perform the computation of the projected two-point galaxy correlation 
@@
 occupation moment relative to low-concentration halos of the same
-mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq
-\langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the
+mass,
+%
+\begin{eqnarray}
+\langle\ngal|\mvir, c_{\rm high}\rangle & = & \langle\ngal|\mvir \rangle + \delta\ngal \nonumber \\  
+\langle\ngal|\mvir, c_{\rm low}\rangle  & = & \langle\ngal|\mvir \rangle - \delta\ngal
+\end{eqnarray}
+%
+This difference, $\delta\ngal$, between the
 first moment of high- and low-concentration halos is modulated by
@@
 central galaxies with a distinct assembly bias parameter
-$-1 \le A_{\rm cen} \le 1$. These two additional parameters are varied in our
-analyses that include assembly bias, making the number of parameters
-that vary in these analyses seven. As we show below, these additional
+$-1 \le A_{\rm cen} \le 1$. For the value of $f_{\rm split}=0.5$ adopted here,
+we then have that
+%
+\begin{eqnarray}
+  \delta N_{\rm cen} & = & A_{\rm cen} \, {\rm MIN}\left\{\langle N_{\mathrm{cen}}|\mvir\rangle , 1- \langle N_{\mathrm{cen}}|\mvir\rangle\right\}\nonumber\\
+  \delta N_{\rm sat} & = & A_{\rm sat} \, \langle N_{\mathrm{sat}}|\mvir\rangle
+\end{eqnarray}
+%
+In our analyses that include assembly bias, we vary these two
+additional parameters, bringing the total number of parameters
+that vary in these analyses to seven. As we show below, these additional
 parameters are in many instances poorly constrained by clustering data
@@
 \label{eq:chisquare}
-\chi^2 = \Delta w_{{\rm p},i} \, [C^{-1}]_{ij} \, \Delta w_{{\rm p},j} + \frac{(n_{\rm g}^{\rm mock} - n_{\rm g}^{\rm meas})^2}{\sigma_{\rm n}^2},
+\chi^2 = \sum_{i,j} \Delta w_{{\rm p},i} \, [C^{-1}]_{ij} \, \Delta w_{{\rm p},j} + \frac{(n_{\rm g}^{\rm mock} - n_{\rm g}^{\rm meas})^2}{\sigma_{\rm n}^2},
 \end{equation}
@@
 To infer parameters for the HOD and Decorated HOD models described in the previous subsections,
-we performed a Markov Chain Monte Carlo (MCMC) sampling of the posterior distribution using the
+we perform a Markov Chain Monte Carlo (MCMC) sampling of the posterior distribution using the
 affine-invariant ensemble sampler of \citet{goodman_weare10} as implemented in the
@@
 best-fit Planck cosmology. Second, we perform our parameter inference analysis using direct population of halos
-identified in a numerical simulation of cosmological structure formation (BolshioP). This greatly mitigates modeling
+identified in a numerical simulation of cosmological structure formation (BolshoiP). This greatly mitigates modeling
 uncertainties associated with nonlinear density field evolution, scale-dependent halo bias, halo exclusion,

### 2016-06-17 ms.tex
Small changes to Section 3 and acknowledgements

@@
 \label{eq:chisquare}
-\chi^2 = \sum_{i,j} \Delta w_{{\rm p},i} \, [C^{-1}]_{ij} \, \Delta w_{{\rm p},j} + \frac{(n_{\rm g}^{\rm mock} - n_{\rm g}^{\rm meas})^2}{\sigma_{\rm n}^2},
+\chi^2 = \Delta w_{{\rm p},i} \, [C^{-1}]_{ij} \, \Delta w_{{\rm p},j} + \frac{(n_{\rm g}^{\rm mock} - n_{\rm g}^{\rm meas})^2}{\sigma_{\rm n}^2},
 \end{equation}
@@
 in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is
-determined by this simple degeneracy with $\log (M_{\rm min})$.
+determined by this simple degeneracy with $\log (M_{\rm min})$. Our constraints on $\sigma_{\log M}$ are listed in Table~\ref{tab:parameters}.
 
@@
 uncertainties associated with nonlinear density field evolution, scale-dependent halo bias, halo exclusion,
-or other effects that have been difficult to incorporate into analytical halo models with high precision. Third,
+or other effects that have been difficult to incorporate into analytical halo models with high precision
+\citep[e.g.,][and references therein]{vdBosch13}. Third,
 we have explored the posteriors of the parameters with significantly more samples (roughly two orders of magnitude),
@@
 correlated (anti-correlated) with halo concentration. The model and its implementation
-in {\tt Halotools} \cite{halotools} is discussed further in Section~\ref{subsection:decorated} above 
+in {\tt Halotools} is discussed further in Section~\ref{subsection:decorated} above 
 and in more detail in \citet{hearin_etal16}.
@@
 Figure~\ref{fig:Mr20samples}, and Figure~\ref{fig:Mr21samples}. The general trend that
-can be gleaned from these figures is that introducing assembly bias improves the ability
-of the predicted two-point functions to match the measured two-point functions across the
+can be gleaned from these figures is that introducing assembly bias improves the fit to
+the measured two-point functions across the
 transition from the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near 
@@
 clustering data. This is important as it implies that galaxy clustering of the precision
-of SDSS DR7 measurements cannot rule out, or strongly restrict galaxy assembly
+of SDSS DR7 measurements cannot rule out, or strongly restrict, galaxy assembly
 bias in many cases. This is the case, for example, for the $M_r<-21$ sample with posteriors
@@
 
-We thank Zheng Zheng for his cooperation in diagnosing the
+We thank Zheng Zheng for his help in diagnosing the
 differences between the present analysis and the SDSS DR7

### 2016-06-17 ms.tex
Removed reduncancy of summation sign.
Minor changes to equation.

@@
 marginalized first moment of centrals and satellites are {\em 
-  unchanged from the baseline value defined by Equations \ref{eq:ncen}
-  and \ref{eq:nsat}}. In other words, {\em decorated HOD models all have the same HODs,
+unchanged from the baseline value defined by Equations (\ref{eq:ncen}) 
+and (\ref{eq:nsat})}. In other words, {\em decorated HOD models all have the same HODs,
 when averaged over all halos at fixed mass, as standard HOD
@@
 \begin{eqnarray}
-  \delta N_{\rm cen} & = & A_{\rm cen} \, {\rm MIN}\left\{\langle N_{\mathrm{cen}}|\mvir\rangle , 1- \langle N_{\mathrm{cen}}|\mvir\rangle\right\}\nonumber\\
-  \delta N_{\rm sat} & = & A_{\rm sat} \, \langle N_{\mathrm{sat}}|\mvir\rangle
+%
+\delta N_{\rm cen} & = & A_{\rm cen} \, {\rm MIN} \left[ \langle N_{\mathrm{cen}} \vert \mvir \rangle ,
+1- \langle N_{\mathrm{cen}} \vert \mvir \rangle \right]  \nonumber \\ 
+\delta N_{\rm sat} & = & A_{\rm sat} \, \langle N_{\mathrm{sat}} \vert \mvir \rangle
 \end{eqnarray}

### 2016-06-17 ms.tex
Added Concluding Paragraph.

@@
   faintest sample we study, $\magr<-19.$ We find no evidence for
-  assembly bias in the $\magr<-21$ sample. In addition to presenting the first 
-  constraints on HOD models that accommodate assembly bias, our analysis 
+  assembly bias in the $\magr<-21$ sample. Assembly bias should be accounted for 
+  in galaxy clustering analyses or attempts to exploit galaxy clustering to constrain cosmology. 
+  In addition to presenting the first constraints on HOD models that accommodate assembly bias, our analysis 
   includes numerous improvements over previous analyses of this data set and 
@@
 %------------------------------------------------
+\section{Interpretation}
+\label{section:discussion}
+%------------------------------------------------
+
+%------------------------------------------------
 \section{Conclusions}
@@
 In this work, we provide the first quantitative constraints on
-assembly bias derived from the Decorated HOD. 
-We enumerate our most important conclusions below.
+assembly bias derived from the Decorated HOD. Projected galaxy clustering, 
+$\wprp(r_{\rm p})$ is already very well-measured within SDSS DR7, therefore it is likely 
+that further improvements on assembly bias constraints at low-redshift will require the use of additional 
+observables such as galaxy--galaxy lensing, group statistics, void statistics, or numerous other possibilities. 
+We are currently exploring many of those possibilities and will report on those results in a forthcoming publication.
+
+Our most important conclusions are as follows.
 %
@@
 %
-We conclude by noting that since $\wprp$ and $n_{\rm g}$ are already very well-measured in DR7,
-it is likely that further improvements on assembly bias constraints at low-redshift will require additional
-observational measurements, e.g., galaxy--galaxy lensing, group statistics, etc.
-I need to think of a more clever ending.
+
+Until such time as we have stringent constraints on the level of assembly bias in the 
+universe, accounting for the possibility of assembly bias is not optional in interpreting 
+galaxy clustering data. Precise statements about galaxy evolution derived from 
+galaxy clustering or attempts to exploit clustering to perform cosmological analyses 
+cannot be made robustly without accounting for assembly bias. Together with 
+the work of \citet{hearin_etal16} and the {\tt Halotools} software, we have provided 
+an explicit example of one way forward in such analyses. It is our hope that similar analyses 
+will be performed on forthcoming galaxy survey data and that these analyses will lead to a
+richer understanding of galaxy evolution and the relationship between galaxies and the halos 
+and environments in which they are found.
 

### 2016-06-17 ms.tex
few small changes

@@
 %
-$\Delta w_{{\rm p},i} = w_{\rm p}^{\rm mock}(r_{{\rm p},i}) - w_{\rm p}^{\rm meas}(r_{{\rm p},i})$ is the difference
-between the projected two-point function predicted by the mock catalog and the measured value in the i$^{\rm th}$
-separation bin (of 12 bins total), $C^{-1}$ is the inverse of the covariance matrix of the measurements,
-and the last term in Eq.~(\ref{eq:chisquare}) is the contribution from the difference between the predicted and measured
-galaxy number density. In Eq.~(\ref{eq:chisquare}), the we adopt the Einstein summation convention and sum over the 
-dummy indices $i$ and $j$. The error on the galaxy number density assumes Poisson statistics for both the measured and predicted galaxy number densities.
+(Einstein summation convention), $\Delta w_{{\rm p},i} = w_{\rm p}^{\rm
+  mock}(r_{{\rm p},i}) - w_{\rm p}^{\rm meas}(r_{{\rm p},i})$ is the
+difference between the projected two-point function predicted by the
+mock catalog and the measured value in the i$^{\rm th}$ separation bin
+(of 12 bins total), $C^{-1}$ is the inverse of the covariance matrix
+of the measurements, and the last term in Eq.~(\ref{eq:chisquare}) is
+the contribution from the difference between the predicted and
+measured galaxy number density. The error on the galaxy number density
+assumes Poisson statistics for both the measured and predicted galaxy
+number densities.
 
@@
 \citet{zehavi_etal11}, as the latter values will be artificially lower.
-Therefore, it seems likely that the tighter constraints quoted by \citet{zehavi_etal11}
-must be caused by an error.
 
@@
 in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is
-determined by this simple degeneracy with $\log (M_{\rm min})$. Our constraints on $\sigma_{\log M}$ are listed in Table~\ref{tab:parameters}.
+determined by this simple degeneracy with $\log (M_{\rm min})$. Our constraints on $\sigma_{\log M}$ are listed in Table~\ref{table:parameters}.
 

### 2016-06-17 ms.tex
Added interpretation section to flesh out some of the interpreative discussion that our paper is now missing. For me, this completes the paper.

--- 2016-06-17 ms.tex
@@
 $-20$ & Zentner+16 & $11.95^{+0.11}_{-0.6}$ & $0.37^{+0.23}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.19\\
-$-20$ & Zentner+16 & $12.23^{+0.33}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.20^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.28 (99\%) $ & $0.01^{+0.32}_{-0.26}$ & 1.16 \vspace*{5pt}\\
+$-20$ & Zentner+16 & $12.23^{+0.33}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.20^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%) $ & $0.01^{+0.32}_{-0.26}$ & 1.16 \vspace*{5pt}\\
 %$-20^d$ & Zentner+16 & $11.91^{+0.10}_{-0.03}$ & $0.26^{+0.25}_{-0.17}$ & $13.34^{+0.04}_{-0.05}$ & $1.25^{+0.05}_{-0.06}$ & $--$ & $--$ & 0.70 \\
@@
 Consider the $M_r < -20$ sample. The inferred value of $A_{\rm cen} > 0.28$ at 99\%
-confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ and thus strongly prefer
-galaxies to reside in halos of larger concentration at fixed halo mass. Figure~\ref{fig:directhodcomparison}
+confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ ($A_{\rm cen} > 0$ at $99.9\%$) 
+and thus strongly prefer galaxies to reside in halos of larger concentration at fixed halo mass. Figure~\ref{fig:directhodcomparison}
 compares the inferred HODs for the $M_r<-20$ sample in a standard HOD analysis with the
@@
 
+The results of the previous section suggest that halo mass is insufficient to predict 
+the galaxy content of a halo to the precision mandated by an analysis of SDSS DR7 
+clustering measurements (particularly the $\magr < -19$, $\magr < -20$, and $\magr < -20.5$ samples). 
+This should not be surprising, as the process of galaxy formation and evolution is complex and 
+there is little reason to suspect that many environmental factors determine galaxy properties. 
+Our results further suggest that halo concentration (or some other halo property correlated 
+with halo concentration) impacts the galaxy content of a halo, at least for galaxies of some 
+luminosities. In particular, the assembly bias inferred from the $\magr < -20$ and $\magr < -20.5$ 
+samples suggests that galaxies in roughly Milky Way-sized halos tend to be more luminous 
+if they reside in halos with higher-than-average concentrations.
+
+This can be interpreted in at least two ways that are not mutually exclusive within the context of the standard 
+model of structure formation. Our analysis cannot support either of these scenarios unambiguously, 
+but we considered these reasonable starting points for further consideration. 
+One possibility is simply that the growth and structure of the host 
+halo itself may drive this dependence. For example, halos of higher concentration at fixed 
+mass have deeper potential wells (specifically, higher escape velocities from the halo center). 
+Therefore, gravity more strongly binds the stellar and gaseous contents of such halos possibly 
+driving more rapid star formation or making the galaxies less susceptible to feedback mechanisms 
+that suppress star formation. Higher concentration halos have also formed earlier, on average. This 
+suggests that any physics that acts upon the baryonic content of the halo its high-density 
+environment may have been operative for a longer time, resulting in a larger, more luminous galaxy. 
+Halo assembly bias persists to large separations ($r \gg \mathrm{Mpc}$) and this picture can 
+accommodate galaxy assembly bias on such large scales.
+
+Another possibility is that halo-halo interactions in dense environments may drive, in part, 
+this preference for more luminous galaxies in higher-concentration halos. Recent work 
+on halo evolution suggests that a more physical definition of the size of a halo should be 
+$\sim 2-3$ times the traditional virial radius 
+\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,sunayama_etal16,more_etal16}. 
+This ``splashback radius" incorporates ``splashback" halos that have passed within the dense environment 
+of the central halo, but are traditionally classified as distinct halos despite being strongly 
+influenced by the environment of the central halo. \citet{wang_etal07}, \citet{wetzel_etal14},  
+\citet{sunayama_etal16}, all find that these ``splashback" halos are a significant cause 
+of halo assembly bias on scales $r \sim 1-3\, h^{-1}\mathrm{Mpc}$, where assembly bias is 
+most pronounced and strongly scale dependent. Consequently, decorated HOD models 
+exhibit this same feature \citet{hearin_etal16}. It is not a coincidence that the greatest 
+improvement of the decorated HOD in the description of galaxy clustering occurs on these same 
+length scales (see Fig.~\ref{fig:Mr19samples}-\ref{fig:Mr21samples} and the associated discussion).
+
+This ``splashback" hypothesis has further merit in that it has the same sense as suggested 
+by the data. Splashback halos have experienced mass loss and been spatially truncated 
+as a consequence of their interactions with a larger, nearby halo. Therefore, splashback halos 
+have masses that may be smaller than the masses of other halos that host similar galaxies \citet{dalal_etal08}. 
+Moreover, high concentrations due to tidal truncation are a hallmark of splashback 
+halos \citep{wang_etal07,dalal_etal08,sunayama_etal16}. This results in a picture in which there is a population 
+of halos, correlated on scales $r \sim 1-3\, h^{-1}\mathrm{Mpc}$, that have concentrations 
+that are high for their mass and galaxies that are overluminous for their mass. This is precisely the 
+sense of assembly bias suggested by our analysis. Galaxy assembly bias induced by these 
+splashback effects cannot explain larger-scale assembly bias.
+
 %------------------------------------------------

### 2016-06-17 ms.tex
Minor changes to Interpretation section. Plus one new paragraph added to Interpretation section.

@@
 This should not be surprising, as the process of galaxy formation and evolution is complex and 
-there is little reason to suspect that many environmental factors determine galaxy properties. 
+there is little reason to suspect that all environmental factors are determined by a single halo property. 
 Our results further suggest that halo concentration (or some other halo property correlated 
@@
 that suppress star formation. Higher concentration halos have also formed earlier, on average. This 
-suggests that any physics that acts upon the baryonic content of the halo its high-density 
+suggests that any physics that acts upon the baryonic content of the halo and its high-density 
 environment may have been operative for a longer time, resulting in a larger, more luminous galaxy. 
@@
 This ``splashback" hypothesis has further merit in that it has the same sense as suggested 
-by the data. Splashback halos have experienced mass loss and been spatially truncated 
+by the data. Splashback halos have experienced mass loss and have been spatially truncated 
 as a consequence of their interactions with a larger, nearby halo. Therefore, splashback halos 
-have masses that may be smaller than the masses of other halos that host similar galaxies \citet{dalal_etal08}. 
+have virial masses that may be smaller than the masses of other halos that host similar galaxies \citet{dalal_etal08}. 
 Moreover, high concentrations due to tidal truncation are a hallmark of splashback 
@@
 that are high for their mass and galaxies that are overluminous for their mass. This is precisely the 
-sense of assembly bias suggested by our analysis. Galaxy assembly bias induced by these 
+sense of assembly bias suggested by our analysis. {\bf APH: the following sentence kind of dangles.} Galaxy assembly bias induced by these 
 splashback effects cannot explain larger-scale assembly bias.
+
+Our formulation of the Decorated HOD is not designed to address 
+the finer-grained causes for this correlation. 
+Rather, what we have provided in this work is a robust boundary condition 
+that more detailed specific models such as semi-analytical models 
+and hydrodynamical simulations should satisfy. 
+However, we reiterate an important corollary to our findings. 
+Although SDSS projected clustering measurements favor strong levels of assembly bias, 
+the constraints on even our simple $\abias$ parameters are relatively weak. 
+This implies that {\em it is not possible to reliably constrain a finer-grained physical picture using 
+projected clustering and number density alone.} 
+In order to constrain models that are more complex than simple empirical models 
+such as the Decorated HOD,
+it is necessary to leverage additional constraining power of 
+observations beyond two-point clustering.
 

### 2016-06-17 ms.tex
Minor edits to Interpretation.

--- 2016-06-17 ms.tex
@@
 This should not be surprising, as the process of galaxy formation and evolution is complex and 
-there is little reason to suspect that many environmental factors determine galaxy properties. 
+there is little reason to suspect that all potentially-important factors are determined by a single halo property. 
 Our results further suggest that halo concentration (or some other halo property correlated 
@@
 mass have deeper potential wells (specifically, higher escape velocities from the halo center). 
-Therefore, gravity more strongly binds the stellar and gaseous contents of such halos possibly 
+Therefore, gravity more strongly binds the stellar and gaseous contents of such halos, possibly 
 driving more rapid star formation or making the galaxies less susceptible to feedback mechanisms 
 that suppress star formation. Higher concentration halos have also formed earlier, on average. This 
-suggests that any physics that acts upon the baryonic content of the halo its high-density 
+suggests that any physics that acts upon the baryonic content of the halo and its high-density 
 environment may have been operative for a longer time, resulting in a larger, more luminous galaxy. 
-Halo assembly bias persists to large separations ($r \gg \mathrm{Mpc}$) and this picture can 
-accommodate galaxy assembly bias on such large scales.
+Concentration-dependent halo assembly bias persists to very large separations 
+\citep[$r > 10\, h^{-1}\mathrm{Mpc}$, e.g.,][]{wechsler06} 
+and this picture can accommodate galaxy assembly bias on such large scales.
 
@@
 $\sim 2-3$ times the traditional virial radius 
-\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,sunayama_etal16,more_etal16}. 
+\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,sunayama_etal16,more_etal16}, 
+a scale on the order of $\sim \mathrm{Mpc}$. 
 This ``splashback radius" incorporates ``splashback" halos that have passed within the dense environment 
-of the central halo, but are traditionally classified as distinct halos despite being strongly 
+of a larger, central halo, but are traditionally classified as distinct halos despite being strongly 
 influenced by the environment of the central halo. \citet{wang_etal07}, \citet{wetzel_etal14},  
@@
 
-This ``splashback" hypothesis has further merit in that it has the same sense as suggested 
-by the data. Splashback halos have experienced mass loss and been spatially truncated 
-as a consequence of their interactions with a larger, nearby halo. Therefore, splashback halos 
-have masses that may be smaller than the masses of other halos that host similar galaxies \citet{dalal_etal08}. 
-Moreover, high concentrations due to tidal truncation are a hallmark of splashback 
-halos \citep{wang_etal07,dalal_etal08,sunayama_etal16}. This results in a picture in which there is a population 
+This ``splashback" hypothesis has further merit in that it has the same sense suggested 
+by the data. Splashback halos have experienced mass loss and have been spatially truncated. 
+Therefore, splashback halos have virial masses that may be smaller than the masses of other 
+halos that host similar galaxies \citet{dalal_etal08}. Meanwhile, high concentrations due 
+to tidal truncation are a hallmark of splashback halos 
+\citep{wang_etal07,dalal_etal08,sunayama_etal16}. 
+The implication is a population 
 of halos, correlated on scales $r \sim 1-3\, h^{-1}\mathrm{Mpc}$, that have concentrations 
 that are high for their mass and galaxies that are overluminous for their mass. This is precisely the 
-sense of assembly bias suggested by our analysis. Galaxy assembly bias induced by these 
+sense of assembly bias suggested by our analysis. 
+Galaxy assembly bias induced by these 
 splashback effects cannot explain larger-scale assembly bias.
+
+Our formulation of the Decorated HOD is not designed to address 
+the finer-grained causes for observed correlations. 
+Rather, what we have provided in this work is a robust boundary condition 
+that more detailed specific models, such as semi-analytical models 
+and hydrodynamical simulations, should satisfy. 
+However, we reiterate an important corollary to our findings. 
+Although SDSS projected clustering measurements favor strong levels of assembly bias, 
+the constraints on even our simple $\abias$ parameters are relatively weak. 
+This implies that {\em it may not be possible to constrain a finer-grained physical 
+picture using projected clustering at a level that is interesting.} 
+In order to constrain models that are more complex than simple empirical models 
+such as the Decorated HOD, it is necessary to leverage additional constraining power of 
+observations beyond two-point clustering.
 
@@
 galaxy clustering or attempts to exploit clustering to perform cosmological analyses 
-cannot be made robustly without accounting for assembly bias. Together with 
-the work of \citet{hearin_etal16} and the {\tt Halotools} software, we have provided 
+cannot be made robustly without accounting for assembly bias \citep[see][]{zentner_etal14}. 
+Together with the work of \citet{hearin_etal16} and the {\tt Halotools} software, we have provided 
 an explicit example of one way forward in such analyses. It is our hope that similar analyses 

### 2016-06-17 ms.tex
Added acknowledgment to Prince Rogers Nelson to help clue in the uneducated reader.
changes in Sect 4 from Frank

--- 2016-06-17 ms.tex
@@
 
-The one-dimensional marginalized constraints on all parameters from these analyses
-are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}.
-In cases where the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ is a monotonic within 
-the physical parameter range, we quote an upper or lower limit on the parameter 
-(e.g., see the posterior distribution for $A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}). 
-Examples of one- and two-dimensional visualizations of the posteriors from our analyses are shown in 
-Figure~\ref{fig:Mr19ABtriangle}, Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle} 
+The one-dimensional marginalized constraints on all parameters from
+these analyses are given in the lowest row of each luminosity
+threshold grouping in Table~\ref{table:parameters}.  In cases where
+the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ is
+a monotonic within the physical parameter range, we quote an upper or
+lower limit on the parameter (e.g., see the posterior distribution for
+$A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}).  Examples of one- and
+two-dimensional visualizations of the posteriors from our analyses are
+shown in Figure~\ref{fig:Mr19ABtriangle},
+Figure~\ref{fig:Mr20ABtriangle}, and Figure~\ref{fig:Mr21ABtriangle}
 for the $M_r<-19$, $M_r<-20$, and $M_r<-21$ samples respectively.
@@
 
-The results of the previous section suggest that halo mass is insufficient to predict 
-the galaxy content of a halo to the precision mandated by an analysis of SDSS DR7 
-clustering measurements (particularly the $\magr < -19$, $\magr < -20$, and $\magr < -20.5$ samples). 
-This should not be surprising, as the process of galaxy formation and evolution is complex and 
-there is little reason to suspect that many environmental factors determine galaxy properties. 
-Our results further suggest that halo concentration (or some other halo property correlated 
-with halo concentration) impacts the galaxy content of a halo, at least for galaxies of some 
-luminosities. In particular, the assembly bias inferred from the $\magr < -20$ and $\magr < -20.5$ 
-samples suggests that galaxies in roughly Milky Way-sized halos tend to be more luminous 
-if they reside in halos with higher-than-average concentrations.
-
-This can be interpreted in at least two ways that are not mutually exclusive within the context of the standard 
-model of structure formation. Our analysis cannot support either of these scenarios unambiguously, 
-but we considered these reasonable starting points for further consideration. 
-One possibility is simply that the growth and structure of the host 
-halo itself may drive this dependence. For example, halos of higher concentration at fixed 
-mass have deeper potential wells (specifically, higher escape velocities from the halo center). 
-Therefore, gravity more strongly binds the stellar and gaseous contents of such halos possibly 
-driving more rapid star formation or making the galaxies less susceptible to feedback mechanisms 
-that suppress star formation. Higher concentration halos have also formed earlier, on average. This 
-suggests that any physics that acts upon the baryonic content of the halo its high-density 
-environment may have been operative for a longer time, resulting in a larger, more luminous galaxy. 
-Halo assembly bias persists to large separations ($r \gg \mathrm{Mpc}$) and this picture can 
+The results of the previous section suggest that halo mass is
+insufficient to predict the galaxy content of a halo to the precision
+mandated by an analysis of SDSS DR7 clustering measurements
+(particularly the $\magr < -19$, $\magr < -20$, and $\magr < -20.5$
+samples).  This should not be surprising, as the process of galaxy
+formation and evolution is complex and there is little reason to
+suspect that many environmental factors impact galaxy properties.
+Our results further suggest that halo concentration (or some other
+halo property correlated with halo concentration) impacts the galaxy
+content of a halo, at least for galaxies of some luminosities. In
+particular, the assembly bias inferred from the $\magr < -20$ and
+$\magr < -20.5$ samples suggests that galaxies in roughly Milky
+Way-sized halos tend to be more luminous if they reside in halos with
+higher-than-average concentrations.
+
+Within the context of the standard model of structure formation, this
+can be interpreted in at least two ways that are not mutually
+exclusive. Although our analysis cannot support either of these
+scenarios unambiguously, they are reasonable starting points for
+further consideration.  One possibility is simply that the growth and
+structure of the host halo itself may drive this
+luminosity-concentration dependence. For example, halos of higher
+concentration at fixed mass have deeper potential wells (specifically,
+higher escape velocities from the halo center).  Therefore, gravity
+more strongly binds the stellar and gaseous contents of such halos
+possibly driving more rapid star formation or making the galaxies less
+susceptible to feedback mechanisms that suppress star
+formation. Higher concentration halos have also formed earlier, on
+average \citep[e.g.,][]{wechsler02}, which may also contribute to the
+galaxy ending up more luminous. Halo assembly bias persists to large
+separations ($r \gg \mathrm{Mpc}$) and this picture can therefore
 accommodate galaxy assembly bias on such large scales.
 
-Another possibility is that halo-halo interactions in dense environments may drive, in part, 
-this preference for more luminous galaxies in higher-concentration halos. Recent work 
-on halo evolution suggests that a more physical definition of the size of a halo should be 
-$\sim 2-3$ times the traditional virial radius 
-\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,sunayama_etal16,more_etal16}. 
-This ``splashback radius" incorporates ``splashback" halos that have passed within the dense environment 
-of the central halo, but are traditionally classified as distinct halos despite being strongly 
-influenced by the environment of the central halo. \citet{wang_etal07}, \citet{wetzel_etal14},  
-\citet{sunayama_etal16}, all find that these ``splashback" halos are a significant cause 
-of halo assembly bias on scales $r \sim 1-3\, h^{-1}\mathrm{Mpc}$, where assembly bias is 
-most pronounced and strongly scale dependent. Consequently, decorated HOD models 
-exhibit this same feature \citet{hearin_etal16}. It is not a coincidence that the greatest 
-improvement of the decorated HOD in the description of galaxy clustering occurs on these same 
-length scales (see Fig.~\ref{fig:Mr19samples}-\ref{fig:Mr21samples} and the associated discussion).
-
-This ``splashback" hypothesis has further merit in that it has the same sense as suggested 
-by the data. Splashback halos have experienced mass loss and been spatially truncated 
-as a consequence of their interactions with a larger, nearby halo. Therefore, splashback halos 
-have masses that may be smaller than the masses of other halos that host similar galaxies \citet{dalal_etal08}. 
-Moreover, high concentrations due to tidal truncation are a hallmark of splashback 
-halos \citep{wang_etal07,dalal_etal08,sunayama_etal16}. This results in a picture in which there is a population 
-of halos, correlated on scales $r \sim 1-3\, h^{-1}\mathrm{Mpc}$, that have concentrations 
-that are high for their mass and galaxies that are overluminous for their mass. This is precisely the 
-sense of assembly bias suggested by our analysis. Galaxy assembly bias induced by these 
-splashback effects cannot explain larger-scale assembly bias.
+Another possible explanation for having more luminous galaxies reside
+in higher concentration halos is halo-halo interactions.  Recent work
+on halo evolution suggests that a more physical definition of the size
+of a halo should be $\sim 2-3$ times the traditional virial radius
+\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,more_etal15,sunayama_etal16}.
+This ``splashback radius" incorporates ``splashback" halos that have
+passed within the dense environment of the central halo, but are
+traditionally classified as distinct halos despite being strongly
+influenced by the environment of the central
+halo. \citet{wang_etal09}, \citet{wetzel_etal14},
+\citet{sunayama_etal16}, all find that these ``splashback" halos are a
+significant cause of halo assembly bias on scales $r \sim 1-3\,
+h^{-1}\mathrm{Mpc}$, where assembly bias is most pronounced and
+strongly scale dependent. Consequently, decorated HOD models exhibit
+this same feature \citep{hearin_etal16}, and is not a coincidence that
+the greatest improvement of the decorated HOD in the description of
+galaxy clustering occurs on these same length scales (see
+Fig.~\ref{fig:Mr19samples}-\ref{fig:Mr21samples} and the associated
+discussion).
+
+This ``splashback" hypothesis has further merit in that it has the
+same sense as suggested by the data. Splashback halos have experienced
+mass loss as a consequence of their tidal interactions with a larger,
+nearby halo. As a consequence, splashback halos are expected to be
+less massive than `regular' host halos that host similar galaxies
+\citep{dalal_etal08}.  Moreover, high concentrations due to tidal
+truncation are a hallmark of splashback halos
+\citep{wang_etal07,dalal_etal08,sunayama_etal16}. This results in a
+picture in which there is a population of halos, correlated on scales
+$r \sim 1-3\, h^{-1}\mathrm{Mpc}$, that have concentrations that are
+high for their mass and galaxies that are overluminous for their
+mass. This is precisely the sense of assembly bias suggested by our
+analysis. Note, though, that this splashback effect cannot explain
+galaxy assembly bias on large, linear scales.
 

### 2016-06-17 ms.tex

@@
 
-The results of the previous section suggest that halo mass is
-insufficient to predict the galaxy content of a halo to the precision
-mandated by an analysis of SDSS DR7 clustering measurements
+The results of the previous section suggest that halo
+mass is insufficient to predict the galaxy content of a halo to the
+precision mandated by an analysis of SDSS DR7 clustering measurements
 (particularly the $\magr < -19$, $\magr < -20$, and $\magr < -20.5$
@@
 formation and evolution is complex and there is little reason to
-suspect that many environmental factors impact galaxy properties.
-Our results further suggest that halo concentration (or some other
-halo property correlated with halo concentration) impacts the galaxy
-content of a halo, at least for galaxies of some luminosities. In
-particular, the assembly bias inferred from the $\magr < -20$ and
-$\magr < -20.5$ samples suggests that galaxies in roughly Milky
-Way-sized halos tend to be more luminous if they reside in halos with
-higher-than-average concentrations.
+suspect that all potentially-important factors are determined by a
+single halo property. Our results further suggest that halo
+concentration (or some other halo property correlated with halo
+concentration) impacts the galaxy content of a halo, at least for
+galaxies of some luminosities. In particular, the assembly bias
+inferred from the $\magr < -20$ and $\magr < -20.5$ samples suggests
+that galaxies in roughly Milky Way-sized halos tend to be more
+luminous if they reside in halos with higher-than-average
+concentrations.
 
@@
 formation. Higher concentration halos have also formed earlier, on
-average \citep[e.g.,][]{wechsler02}, which may also contribute to the
-galaxy ending up more luminous. Halo assembly bias persists to large
-separations ($r \gg \mathrm{Mpc}$) and this picture can therefore
-accommodate galaxy assembly bias on such large scales.
+average \citep[e.g.,][]{wechsler02}. This suggests that any physics
+that acts upon the baryonic content of the halo and its high-density
+environment may have been operative for a longer time, resulting in a
+larger, more luminous galaxy.  Concentration-dependent halo assembly
+bias persists to very large separations \citep[$r > 10\, h^{-1}\mathrm{Mpc}$, e.g.,][]{wechsler06} and this picture can
+therefore accommodate galaxy assembly bias on such large scales.
 
@@
 less massive than `regular' host halos that host similar galaxies
-\citep{dalal_etal08}.  Moreover, high concentrations due to tidal
+\citep{dalal_etal08}.  Meanwhile, high concentrations due to tidal
 truncation are a hallmark of splashback halos
-\citep{wang_etal07,dalal_etal08,sunayama_etal16}. This results in a
-picture in which there is a population of halos, correlated on scales
-$r \sim 1-3\, h^{-1}\mathrm{Mpc}$, that have concentrations that are
-high for their mass and galaxies that are overluminous for their
-mass. This is precisely the sense of assembly bias suggested by our
-analysis. Note, though, that this splashback effect cannot explain
-galaxy assembly bias on large, linear scales.
+\citep{wang_etal07,dalal_etal08,sunayama_etal16}.  The implication is
+a population of halos, correlated on scales $r \sim 1-3\,
+h^{-1}\mathrm{Mpc}$, that have concentrations that are high for their
+mass and galaxies that are overluminous for their mass. This is
+precisely the sense of assembly bias suggested by our analysis.  Note,
+though, that this splashback effect cannot explain galaxy assembly
+bias on large, linear scales.
+
+Our formulation of the Decorated HOD is not designed to address 
+the finer-grained causes for observed correlations. 
+Rather, what we have provided in this work is a robust boundary condition 
+that more detailed specific models, such as semi-analytical models 
+and hydrodynamical simulations, should satisfy. 
+However, we reiterate an important corollary to our findings. 
+Although SDSS projected clustering measurements favor strong levels of assembly bias, 
+the constraints on even our simple $\abias$ parameters are relatively weak. 
+This implies that {\em it may not be possible to constrain a finer-grained physical 
+picture using projected clustering at a level that is interesting.} 
+In order to constrain models that are more complex than simple empirical models 
+such as the Decorated HOD, it is necessary to leverage additional constraining power of 
+observations beyond two-point clustering.
 
@@
 Sinha for help installing and running the {\tt CorrFunc} package 
-as well as comments on an earlier draft of this manuscript.
+as well as comments on an earlier draft of this manuscript. ARZ and 
+APH are grateful to Prince Rogers Nelson for inspiring our creativity. 
 The authors gratefully acknowledge the Gauss Centre for Supercomputing

### 2016-06-20 ms.tex
Updated constraints in table, updated triangle figure with latest runs, small edits.

@@
 $-21$ & Zehavi+11 & $12.78 \pm 0.10$ & $0.68 \pm 0.15$ & $13.80 \pm 0.03$ & $1.15 \pm 0.06$ & $--$ & $--$ & 3.1\\
-$-21$ & Zentner+16 & $12.92^{+0.07}_{-0.11}$ & $0.74^{+0.09}_{-0.16}$ & $13.93^{+0.04}_{-0.05}$ & $1.23^{+0.10}_{-0.12}$ & $--$ & $--$ & 1.59\\
+$-21$ & Zentner+16 & $12.92^{+0.08}_{-0.10}$ & $0.72^{+0.09}_{-0.14}$ & $13.95^{+0.03}_{-0.05}$ & $1.26^{+0.08}_{-0.11}$ & $--$ & $--$ & 1.59\\
 $-21$ & Zentner+16 & $12.83^{+0.11}_{-0.09}$ & $0.60^{+0.15}_{-0.17}$ & $13.93^{+0.05}_{-0.08}$ & $1.16^{+0.12}_{-0.14}$ & $0.29^{+0.44}_{-0.35}$ & $0.08^{+0.49}_{-0.36}$ & 1.34 \vspace*{5pt}\\
@@
 $-20$ & Zehavi+11 & $11.83 \pm 0.03$ & $0.25 \pm 0.11$ & $13.08 \pm 0.03$ & $1.00 \pm 0.05$ & $--$ & $--$ & 2.1\\
-$-20$ & Zentner+16 & $11.95^{+0.11}_{-0.6}$ & $0.37^{+0.23}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.19\\
-$-20$ & Zentner+16 & $12.23^{+0.33}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.20^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%) $ & $0.01^{+0.32}_{-0.26}$ & 1.16 \vspace*{5pt}\\
+$-20$ & Zentner+16 & $11.96^{+0.11}_{-0.06}$ & $0.38^{+0.22}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.88\\
+$-20$ & Zentner+16 & $12.24^{+0.29}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.19^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%) $ & $0.01^{+0.35}_{-0.27}$ & 1.09 \vspace*{5pt}\\
 %$-20^d$ & Zentner+16 & $11.91^{+0.10}_{-0.03}$ & $0.26^{+0.25}_{-0.17}$ & $13.34^{+0.04}_{-0.05}$ & $1.25^{+0.05}_{-0.06}$ & $--$ & $--$ & 0.70 \\
@@
 $-19$ & Zehavi+11 & $11.45 \pm 0.04$ & $0.19 \pm 0.13$ & $12.64 \pm 0.04$ & $1.02 \pm 0.02$ & $--$ & $--$ & 1.8 \\
-$-19$ & Zentner+16 & $11.72^{+0.33}_{-0.19}$ & $0.69^{+0.52}_{-0.46}$ & $12.78^{+0.04}_{-0.04}$ & $1.03^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.77\\
+$-19$ & Zentner+16 & $11.72^{+0.33}_{-0.19}$ & $0.70^{+0.51}_{-0.45}$ & $12.78^{+0.04}_{-0.04}$ & $1.03^{+0.04}_{-0.04}$ & $--$ & $--$ & 2.67\\
 $-19$ & Zentner+16 & $11.62^{+0.33}_{-0.13}$ & $0.53^{+0.57}_{-0.35}$ & $12.83^{+0.06}_{-0.07}$ & $1.02^{+0.04}_{-0.04}$ & $0.35^{+0.45}_{-0.66}$ & $>0.02 (84\%)$ & 2.01\\
@@
 threshold grouping in Table~\ref{table:parameters}.  In cases where
-the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ is
-a monotonic within the physical parameter range, we quote an upper or
-lower limit on the parameter (e.g., see the posterior distribution for
-$A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}).  Examples of one- and
+the posterior distribution of either $A_{\rm cen}$ or $A_{\rm sat}$ contains significant 
+probability at the limits of the parameter range (e.g., see the posterior distribution for
+$A_{\rm cen}$ in Fig.~\ref{fig:Mr20ABtriangle}), we quote one-sided 
+constraints.  Examples of one- and
 two-dimensional visualizations of the posteriors from our analyses are
@@
 larger, more luminous galaxy.  Concentration-dependent halo assembly
-bias persists to very large separations \citep[$r > 10\, h^{-1}\mathrm{Mpc}$, e.g.,][]{wechsler06} and this picture can
+bias persists to very large separations 
+\citep[$r > 10\, h^{-1}\mathrm{Mpc}$, e.g.,][]{wechsler06} and this picture can
 therefore accommodate galaxy assembly bias on such large scales.
@@
 truncation are a hallmark of splashback halos
-\citep{wang_etal07,dalal_etal08,sunayama_etal16}.  The implication is
+\citep{sunayama_etal16}.  The implication is
 a population of halos, correlated on scales $r \sim 1-3\,

### 2016-06-20 ms.tex
Softened statement about Bayesian Information Criterion.

@@
 -20.5 & 1.33 \\
--20 & 4.56\\
+-20 & 2.88\\
 -19.5 & 0.26\\
--19 & 4.37\\
+-19 & 3.78\\
 \hline
@@
 
-Beyond the fit results, it is also possible to ask whether or not the fits to the data warrant the use of 
-additional parameters (in this case, to describe assembly bias). This requires a metric that penalizes the 
-use of additional parameters. A commonly used metric is the Bayesian Information Criterion 
+In addition to fitting model parameters, it is possible to ask whether or not the fits to the data warrant the use of 
+additional parameters (in this case, the two parameters used to describe assembly bias). This requires a 
+metric that penalizes the use of additional parameters. A commonly-used metric is the 
+Bayesian Information Criterion 
 \citep[BIC,][]{schwarz78}, defined as 
@@
 the models with assembly bias. The cases that most support the additional complexity 
-of the decorated HOD are $\magr < -19$ and $\magr < -20$, for which $\Delta$BIC 
-rises nearly to the level of a {\rm strong} preference.
+of the decorated HOD are $\magr < -19$ and $\magr < -20$, for which $\Delta$BIC is 
+considerable, but in no case does the $\Delta$BIC rise to the conventional level for {\em strong} 
+preference.
 

### 2016-06-21 ms.tex
Made final edits to table captions, interpretation section, conclusion section.
Addressed Johannes' comments, part 1.

@@
   connection that augments the traditional HOD by allowing for the possibility of 
-  {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo
+  {\em galaxy assembly bias}: galaxy luminosity may be correlated with dark matter halo
   properties besides mass, $\mvir$. We demonstrate that it
@@
 from both traditional and assembly-biased halo occupation analyses
-in Section~\ref{section:results}. We summarize our results and draw
+in Section~\ref{section:results}. We discuss and interpret our results 
+in Section~\ref{section:discussion}. We summarize our results and draw
 conclusions in Section~\ref{section:conclusions}.
@@
 present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles. The minimum 
-peak halo mass considered in our analysis has $M_{\rm peak} \ge 4.05 \times 10^5\, h^{-1}\mathrm{M}_{\odot}$ 
+peak halo mass considered in our analysis has $M_{\rm peak} \ge 4.05 \times 10^{10}\, h^{-1}\mathrm{M}_{\odot}$ 
 and this prevents us from analyzing samples with $M_r > -19$.
@@
 %
-(Einstein summation convention), $\Delta w_{{\rm p},i} = w_{\rm p}^{\rm
-  mock}(r_{{\rm p},i}) - w_{\rm p}^{\rm meas}(r_{{\rm p},i})$ is the
+$\Delta w_{{\rm p},i} = w_{\rm p}^{\rm mock}(r_{{\rm p},i}) - w_{\rm p}^{\rm meas}(r_{{\rm p},i})$ is the
 difference between the projected two-point function predicted by the
 mock catalog and the measured value in the i$^{\rm th}$ separation bin
-(of 12 bins total), $C^{-1}$ is the inverse of the covariance matrix
-of the measurements, and the last term in Eq.~(\ref{eq:chisquare}) is
-the contribution from the difference between the predicted and
-measured galaxy number density. The error on the galaxy number density
-assumes Poisson statistics for both the measured and predicted galaxy
-number densities.
+(of 11 bins total), $C^{-1}$ is the inverse of the covariance matrix
+of the measurements, and repeated indices are summed over. 
+The last term in Eq.~(\ref{eq:chisquare}) is the contribution from the difference 
+between the predicted and measured galaxy number densities. 
+We consider only the eleven values of 
+$w_{\rm p}(r_{\rm p})$ given by \citet{zehavi_etal11} in bins logarithmically spaced between 
+$r_{\rm p}=0.17\, h^{-1}\mathrm{Mpc}$ and $r_{\rm p}=16.9\, h^{-1}\mathrm{Mpc}$. Though 
+\citet{zehavi_etal11} quote values at two larger separations, we find that considering those additional 
+data points adds considerably to the computational expense but alter our results insignificantly. 
+The error on the galaxy number density assumes Poisson statistics for both the measured and 
+predicted galaxy number densities.
 
@@
 our fits, as measured by the minimum of $\chi^2$ per Degree of Freedom (DoF), varies from case to case, 
-all fits have a probability $\gtrsim 1\% $ of obtaining a higher value of $\chi^2$ by chance. 
+all have a probability $\gtrsim 1\% $ of obtaining a higher value of $\chi^2$ by chance. 
 An example of the inferred posteriors for the HOD parameters is shown in 
@@
 value of the parameter and the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles. In cases for which the posterior
-is monotonic within the physical parameter space, we show one-sided percentiles.
+on $A_{\rm cen,sat}$ is significant at the boundary of the permissible parameter range (e.g., $A_{\rm cen}$ for $\magr < -20$), 
+we provide one-sided constraints.
 }
@@
 where $\mathcal{L}_{\rm max}$ is the maximum of the likelihood, 
-$k$ is the number of paramters in the model and $N$ is the number of 
+$k$ is the number of parameters in the model and $N$ is the number of 
 data points. We compute the change in the BIC, $\Delta$BIC, by subtracting 

### 2016-06-21 ms.tex
Addressed most of Johannes comments part 2. Still need to address histogram normalizatoin and remake HOD figure.

@@
   clustering alone. Moreover, galaxy samples $\magr<-20, -20.5$
-  favor strong levels of central galaxy assembly bias. These samples favor models 
+  favor strong levels of central galaxy assembly bias. These samples prefer scenarios  
   in which high-concentration halos are more likely to host a central galaxy

### 2016-06-21 ms.tex
Changed table and made small changes throughout to address Johannes' comments.

@@
 $-21$ & Zentner+16 & $12.92^{+0.08}_{-0.10}$ & $0.72^{+0.09}_{-0.14}$ & $13.95^{+0.03}_{-0.05}$ & $1.26^{+0.08}_{-0.11}$ & $--$ & $--$ & 1.59\\
-$-21$ & Zentner+16 & $12.83^{+0.11}_{-0.09}$ & $0.60^{+0.15}_{-0.17}$ & $13.93^{+0.05}_{-0.08}$ & $1.16^{+0.12}_{-0.14}$ & $0.29^{+0.44}_{-0.35}$ & $0.08^{+0.49}_{-0.36}$ & 1.34 \vspace*{5pt}\\
+$-21$ & Zentner+16 & $12.83^{+0.11}_{-0.09}$ & $0.60^{+0.15}_{-0.17}$ & $13.93^{+0.05}_{-0.08}$ & $1.16^{+0.12}_{-0.14}$ & $0.29^{+0.44}_{-0.35}$ & $0.08^{+0.49}_{-0.36}$ & 1.34 \vspace*{6pt}\\
 %
@@
 $-20.5$ & Zentner+16 & $12.25^{+0.07}_{-0.03}$ & $0.23^{+0.17}_{-0.15}$ & $13.59^{+0.02}_{-0.02}$ & $1.20^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.90\\
-$-20.5$ & Zentner+16 & $12.32^{+0.13}_{-0.08}$ & $0.45^{+0.21}_{-0.25}$ & $13.59^{+0.04}_{-0.04}$ & $1.14^{+0.05}_{-0.06}$ & $>0.08 (90\%)$ & $0.22^{+0.40}_{-0.31}$ & 1.40 \vspace*{5pt}\\
+$-20.5$ & Zentner+16 & $12.32^{+0.13}_{-0.08}$ & $0.45^{+0.21}_{-0.25}$ & $13.59^{+0.04}_{-0.04}$ & $1.14^{+0.05}_{-0.06}$ & $>0.08 (90\%)$ & $0.22^{+0.40}_{-0.31}$ & 1.40\\
+             &                     &                                         &                                        &                                        &                                      & $>0\, (92.3\%)$ &                                           &
+ \vspace*{8pt}\\
 %
@@
 $-20$ & Zentner+16 & $11.96^{+0.11}_{-0.06}$ & $0.38^{+0.22}_{-0.21}$ & $13.28^{+0.03}_{-0.04}$ & $1.16^{+0.04}_{-0.04}$ & $--$ & $--$ & 1.88\\
-$-20$ & Zentner+16 & $12.24^{+0.29}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.19^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%) $ & $0.01^{+0.35}_{-0.27}$ & 1.09 \vspace*{5pt}\\
+$-20$ & Zentner+16 & $12.24^{+0.29}_{-0.21}$ & $0.84^{+0.37}_{-0.31}$ & $13.19^{+0.06}_{-0.08}$ & $1.05^{+0.06}_{-0.08}$ & $ >0.29 (99\%)$ & $0.01^{+0.35}_{-0.27}$ & 1.09\\
+          &                     &                                         &                                       &                                         &                                      & $>0\, (99.9\%)$     &                                      & \vspace*{8pt}\\
 %$-20^d$ & Zentner+16 & $11.91^{+0.10}_{-0.03}$ & $0.26^{+0.25}_{-0.17}$ & $13.34^{+0.04}_{-0.05}$ & $1.25^{+0.05}_{-0.06}$ & $--$ & $--$ & 0.70 \\
@@
 $-19.5$ & Zentner+16 & $11.76^{+0.33}_{-0.11}$ & $0.51^{+0.51}_{-0.29}$ & $13.05^{+0.04}_{-0.08}$ & $1.12^{+0.04}_{-0.07}$ & $--$ & $--$ & 1.24\\
-$-19.5$ & Zentner+16 & $11.80^{+0.36}_{-0.16}$ & $0.63^{+0.53}_{-0.37}$ & $13.04^{+0.09}_{-0.12}$ & $1.06^{+0.07}_{-0.10}$ & $>-0.01 (84\%)$ & $>-0.16 (84\%)$ & 0.69 \vspace*{5pt}\\
+$-19.5$ & Zentner+16 & $11.80^{+0.36}_{-0.16}$ & $0.63^{+0.53}_{-0.37}$ & $13.04^{+0.09}_{-0.12}$ & $1.06^{+0.07}_{-0.10}$ & $>-0.01 (84\%)$ & $>-0.16 (84\%)$ & 0.69 \vspace*{6pt}\\
 %
@@
 $-19$ & Zentner+16 & $11.62^{+0.33}_{-0.13}$ & $0.53^{+0.57}_{-0.35}$ & $12.83^{+0.06}_{-0.07}$ & $1.02^{+0.04}_{-0.04}$ & $0.35^{+0.45}_{-0.66}$ & $>0.02 (84\%)$ & 2.01\\
+          &                      &                                       &                                        &                                         &                                      &                                       & $>0\, (85\%)$ & \\
 %$-19^d$ & Zentner+16 & $11.87^{+0.17}_{-0.27}$ & $1.10^{+0.30}_{-0.52}$ & $12.84^{+0.17}_{-0.23}$ & $1.11^{+0.15}_{-0.15}$ & $--$ & $--$ & 2.30 \\
@@
 on $A_{\rm cen,sat}$ is significant at the boundary of the permissible parameter range (e.g., $A_{\rm cen}$ for $\magr < -20$), 
-we provide one-sided constraints.
+we provide one-sided constraints. In the cases exhibiting the strongest assembly bias, we also quote the probability with 
+which the inferred value of $A_{\rm cen,sat}$ exceeds zero.
 }
@@
 from the best-fit models to the $\magr<-20$ sample in the left and right
-panels, respectively. The green curve shows the HOD of our best-fit model
-that includes the effect of assembly bias; the red curve shows the HOD
+panels, respectively. The solid, purple curve shows the HOD of our best-fit model
+that includes the effect of assembly bias; the solid, orange curve shows the HOD
 of the best-fit model in which assembly bias is assumed to be zero;
-the dashed black curve shows the best-fit HODs from \citet{zehavi_etal11}.
-The green error band around the decorated HOD results shows the variance
-in the HOD from randomly sampling one hundred points in parameter space
-with $\chi^{2}_{\rm model} - \chi^{2}_{\rm min} < 1.$
+the dashed, black curve shows the best-fit HODs from \citet{zehavi_etal11}.
+The light purple error band around the decorated HOD results contains 68\% of 
+the HODs from the samples of the posterior distribution at each mass bin. For 
+any individual sample, the values of the HOD at each mass point are correlated. 
 }
@@
 confidence. In this case the data strongly prefer $A_{\rm cen} > 0$ ($A_{\rm cen} > 0$ at $99.9\%$) 
-and thus strongly prefer galaxies to reside in halos of larger concentration at fixed halo mass. Figure~\ref{fig:directhodcomparison}
+and thus strongly prefer galaxies to reside in halos of larger concentration at fixed halo mass. 
+Figure~\ref{fig:directhodcomparison}
 compares the inferred HODs for the $M_r<-20$ sample in a standard HOD analysis with the
@@
 assembly bias. This is an explicit example of the degree to which the inferred relationship
-between galaxies and halos can be altered by assembly bias. In this case, the efficiency 
+between galaxies and halos can be altered by assembly bias. In the assembly-biased case, the efficiency 
 of forming a sufficiently luminous galaxy is a function that increases slowly over nearly two 
@@
 there are hints of galaxy assembly bias in other samples. Satellite galaxies show a marginal preference
-for occupying halos of higher concentration in the $M_r < -19$ threshold sample. The $M_r < -19.5$
-sample exhibits weak preference for a positive correlation of galaxy occupation with halo concentration at fixed
-mass for both satellite galaxies and central galaxies. Continuing upward with luminosity,
-the $M_r < -20.5$ sample exhibits a significant preference for central galaxy assembly bias.
-Lastly, there is no preference for either central galaxy or satellite galaxy assembly bias
-for the $M_r < -21$ threshold sample, for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$
-are consistent with zero well within 1$\sigma$. The implications of all of these results are too numerous 
+for occupying halos of higher concentration in the $M_r < -19$ threshold sample, with $A_{\rm sat}>0$ at 
+85\%. The $M_r < -19.5$ sample exhibits weak preference for a positive correlation of galaxy occupation 
+with halo concentration at fixed mass for both satellite galaxies and central galaxies. The low value of 
+$\chi^2$ in this case is also suggestive of possible over-fitting using these additional parameters (but see 
+the discussion in the subsequent paragraph). Continuing upward with luminosity,
+the $M_r < -20.5$ sample exhibits a significant preference for central galaxy assembly bias, 
+with $A_{\rm cen}>0$ at 92.3\%. Lastly, there is no preference for either central galaxy or 
+satellite galaxy assembly bias for the $M_r < -21$ threshold sample, 
+for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$
+are consistent with zero well within 1$\sigma$. The implications of all of these results, particularly for 
+quantities derived from HODs, are far too numerous 
 to address in the present manuscript; however, we plan to address them in forthcoming publications.
@@
 the Bayesian Information Criterion $\vert \Delta \mathrm{BIC}\vert \ge 5$ strongly favor one model
-over another.
+over another. None of the models we explore achieve this threshold.
 }

### 2016-06-22 ms.tex
Updated table. Changed triangle plots so that all histograms are normalized to the same total probability.

@@
 {Andrew R. Zentner$^{1}$, Andrew Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
-Johannes U. Lange$^{3}$, and P. Rogers Nelson$^{4}$\\ \\
+Johannes U. Lange$^{3}$, Antonio Villarreal$^{1}$, and P. Rogers Nelson$^{4}$\\ \\
 $^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
@@
 We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter
-halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}.
-In particular, we use the {\tt halotools\_alpha\_version2} version of the $z=0$ snapshot
+halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} 
+and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}. In particular, we use the {\tt halotools\_alpha\_version2} 
+version of the $z=0$ snapshot
 of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius
@@
 $-21$ & Zehavi+11 & $12.78 \pm 0.10$ & $0.68 \pm 0.15$ & $13.80 \pm 0.03$ & $1.15 \pm 0.06$ & $--$ & $--$ & 3.1\\
-$-21$ & Zentner+16 & $12.92^{+0.08}_{-0.10}$ & $0.72^{+0.09}_{-0.14}$ & $13.95^{+0.03}_{-0.05}$ & $1.26^{+0.08}_{-0.11}$ & $--$ & $--$ & 1.59\\
+$-21$ & Zentner+16 & $12.93^{+0.07}_{-0.10}$ & $0.74^{+0.09}_{-0.13}$ & $13.96^{+0.03}_{-0.05}$ & $1.27^{+0.08}_{-0.10}$ & $--$ & $--$ & 1.59\\
 $-21$ & Zentner+16 & $12.83^{+0.11}_{-0.09}$ & $0.60^{+0.15}_{-0.17}$ & $13.93^{+0.05}_{-0.08}$ & $1.16^{+0.12}_{-0.14}$ & $0.29^{+0.44}_{-0.35}$ & $0.08^{+0.49}_{-0.36}$ & 1.34 \vspace*{6pt}\\
@@
 space. {\bf Right:} Same as the left panel but using a
-fit to a Decorated HOD model that contain parameters to describe the strength of assembly bias.
+fit to a Decorated HOD model that contain parameters 
+to describe the strength of assembly bias.
 }
@@
   show the posteriors on these parameters from the standard analysis without
-  any parameterization of galaxy assembly bias. The decorated HOD models include a
-  two-parameter model for assembly bias. The HOD parameter $\log
-  (M_0)$ is extremely poorly constrained by the data and has been
+  any parameterization of galaxy assembly bias. In these panels, both histograms 
+  are normalized to the same total probability. The decorated HOD models include a
+  two-parameter model for assembly bias. The HOD parameter 
+  $\log (M_0)$ is extremely poorly constrained by the data and has been
   suppressed for clarity. Likewise, as in Fig.~\ref{fig:Mr20triangle},
@@
 The light purple error band around the decorated HOD results contains 68\% of 
-the HODs from the samples of the posterior distribution at each mass bin. For 
-any individual sample, the values of the HOD at each mass point are correlated. 
+all samples of the posterior within $\Delta \chi^2 \le 5.89$ of the best-fit model at 
+each bin of halo mass. For any individual model, 
+the values of the HOD at each mass point are obviously correlated and do 
+not vary independently from one mass bin to another. 
 }
@@
 inferred HOD from our decorated HOD analysis that includes parameters to describe
-assembly bias. This is an explicit example of the degree to which the inferred relationship
+assembly bias. The bands in purple rein in the region of HODs for models within 
+$\Delta chi^2 \le 5.89$ of the best-fit model. 
+This is an explicit example of the degree to which the inferred relationship
 between galaxies and halos can be altered by assembly bias. In the assembly-biased case, the efficiency 

### 2016-06-22 ms.tex
Franks comments addressed except for chi^2 question.

@@
   model using SDSS DR7 measurements of projected galaxy clustering, $\wprp (r_{\rm p})$ 
-  of galaxies in r-band luminosity-threshold samples. 
+  of galaxies in $r$-band luminosity-threshold samples. 
   The decorated HOD is a model for the galaxy--halo
@@
 are typically too computationally expensive to compare to data in a manner 
-that enables statistical constraints on model parameters. Such models are usually 
+that enables statistical constraints on model parameters 
+\citep[but see][for recent progress in this direction]{lu_etal11,lu_etal12,henriques_etal13,lu_etal14}. 
+Such models are usually 
 compared to data on a case-by-case basis \citep[e.g.,][]{croton_etal07}, prohibiting
@@
 version of the $z=0$ snapshot
-of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius
-density contrast given in \citet{bryan_norman98}. When populating this catalog with mock galaxies, we only use
-present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles. The minimum 
+of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are defined by the virial 
+radius density contrast given in \citet{bryan_norman98} and have virial masses $\mvir$ within their virial 
+radii. When populating this catalog with mock galaxies, we only use
+present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles, where $M_{\rm peak}$ is 
+the maximum mass a halo obtains during its evolution. We consider only host halos and not their 
+subhalos in this work. For host halos, $M_{\rm peak}$ is almost always nearly identical to the 
+present day virial mass of the halo, $\mvir$. The minimum 
 peak halo mass considered in our analysis has $M_{\rm peak} \ge 4.05 \times 10^{10}\, h^{-1}\mathrm{M}_{\odot}$ 
-and this prevents us from analyzing samples with $M_r > -19$.
+and this prevents us from analyzing samples with $M_r > -19$. Throughout the remainder of this 
+paper, we will refer only to the virial mass $\mvir$ of the halo to be in closer concordance with other 
+work on HOD analyses.
 
@@
 \citet{zehavi_etal11}, to expedite comparisons with their results. However, our choice does deviate from 
-the choice of \citet{zehavi_etal11} in one respect. The mean satellite occupation of \citet{zehavi_etal11} 
+\citet{zehavi_etal11} in one respect. The mean satellite occupation of \citet{zehavi_etal11} 
 is that of Eq.~(\ref{eq:nsat}) multiplied by an overall factor of $\langle N_{\rm cen} \vert \mvir \rangle$. 
@@
 galaxies in the mock sample. We apply the distant-observer
-approximation and use the simulation z-axis as the line-of-sight
+approximation and use the simulation $z$-axis as the line-of-sight
 direction, and the distance between points in the $xy$-plane to define
@@
 redshift-space by replacing each galaxy's $z$-coordinate with
-$z_{\rm RS} = z + V_{\rm z}/H_0.$ We count pairs of points in each of
+$z_{\rm RS} = z + V_{\rm z}/H_0$\footnote{A similar exercise is demonstrated 
+as part of the Halotools documentation at {\tt http://halotools.readthedocs.io}}. 
+Having populated mocks, 
+we perform the computation of the projected two-point galaxy correlation 
+function, $w_{\rm p}(r_{\rm p})$ using the publicly-available {\tt CorrFunc} 
+package \citep{corrfunc} which has been extensively optimized for computational speed.
+We count pairs of points in each of
 our $\rp$ bins, rejecting pairs with line-of-sight distances in redshift space, $\Delta z_{\rm RS}$, 
@@
 depth chosen by \citet{zehavi_etal11}, both in their analysis of the SDSS
-DR7 data and in their modeling. Finally, having populated mocks, 
-we perform the computation of the projected two-point galaxy correlation 
-function, $w_{\rm p}(r_{\rm p})$ using the publicly-available {\tt CorrFunc} 
-package \citep{corrfunc} which has been extensively optimized for computational speed.
+DR7 data and in their modeling.
 
@@
 in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is
-determined by this simple degeneracy with $\log (M_{\rm min})$. Our constraints on $\sigma_{\log M}$ are listed in Table~\ref{table:parameters}.
+determined by this simple degeneracy with $\log (M_{\rm min})$. 
+Our constraints on $\sigma_{\log M}$ are listed in Table~\ref{table:parameters}.
 
@@
 \caption{
-We show the first moments of the central and satellite occupation distributions
-from the best-fit models to the $\magr<-20$ sample in the left and right
-panels, respectively. The solid, purple curve shows the HOD of our best-fit model
+The first moments of the central (left panel) and satellite (right) 
+occupation distributions from the best-fit models to the 
+$\magr \le -20$ sample. The solid, purple curve shows the HOD of our best-fit model
 that includes the effect of assembly bias; the solid, orange curve shows the HOD
@@
 for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$
-are consistent with zero well within 1$\sigma$. The implications of all of these results, particularly for 
+are consistent with zero well within 1$\sigma$. While we give a brief discussion of these results 
+in the following section, the implications of all of these results, particularly for 
 quantities derived from HODs, are far too numerous 
-to address in the present manuscript; however, we plan to address them in forthcoming publications.
+to address comprehensively in the present manuscript; 
+however, we plan to address them in forthcoming publications.
 
@@
 influenced by the environment of the central
-halo. \citet{wang_etal09}, \citet{wetzel_etal14},
+halo. \citet{wang_etal09}, \citet{wetzel_etal14}, and 
 \citet{sunayama_etal16}, all find that these ``splashback" halos are a
@@
 less massive than `regular' host halos that host similar galaxies
-\citep{dalal_etal08}.  Meanwhile, high concentrations due to tidal
-truncation are a hallmark of splashback halos
+\citep{dalal_etal08}.  Meanwhile, high concentrations 
+are a hallmark of splashback halos
 \citep{sunayama_etal16}. The implication is
@@
 observables such as galaxy--galaxy lensing, group statistics, void statistics, or numerous other possibilities. 
-We are currently exploring many of those possibilities and will report on those results in a forthcoming publication.
+We are currently exploring many of those possibilities and will report on those results in forthcoming publications.
 
@@
 %
-\item The evidence for galaxy assembly bias weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cens}=0$ and $A_{\rm sats}=0.$ This is consistent with the well-established result that
+\item The evidence for galaxy assembly bias weakens for brighter galaxy samples: 
+Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cen}=0$ and $A_{\rm sats}=0.$ 
+This is consistent with the well-established result that
 {\em halo assembly bias} weakens with increasing halo mass over the dynamic range relevant to these galaxy samples
@@
 Research Center. The work of ARZ was supported by the US National Science
-Foundation via grant AST 1517563. FvdB is supported by the US National Science
+Foundation via grant AST 1517563. FvdB and JUL are supported by the US National Science
 Foundation through grant AST 1516962. APH is funded through the Yale Center 

### 2016-06-22 ms.tex
small typo corrected.
Frank's final changes incorporated, including removing Prince from the author's list.

@@
 {Andrew R. Zentner$^{1}$, Andrew Hearin$^{2}$, Frank C. van den Bosch$^{3},$ \newauthor
-Johannes U. Lange$^{3}$, Antonio Villarreal$^{1}$, and P. Rogers Nelson$^{4}$\\ \\
+Johannes U. Lange$^{3}$, and Antonio Villarreal$^{1}$\\ \\
 $^1$Department of Physics and Astronomy \& Pittsburgh Particle Physics, Astrophysics, and Cosmology Center (PITT PACC),\\ University of Pittsburgh, Pittsburgh, PA 15260\\
@@
 $^3$Department of Astronomy, Yale University, P.O. Box 208101, New Haven, CT\\
-$^4$Paisley Park, Chanhassen, MN\\
 }
@@
 The primary improvements of our approach stem from the fact that we 
-directly populate mock galaxy catalogs within a cosmological simulation,
+populate directly halos within a cosmological simulation with mock galaxies, 
 whereas previous analyses relied upon analytical fitting functions
@@
 or other effects that have been difficult to incorporate into analytical halo models with high precision
-\citep[e.g.,][and references therein]{vdBosch13}. Third,
+\citep[e.g.,][and references the]{vdBosch13}. Third,
 we have explored the posteriors of the parameters with significantly more samples (roughly two orders of magnitude),
@@
   two-parameter model for assembly bias. The HOD parameter 
-  $\log (M_0)$ is extremely poorly constrained by the data and has been
-  suppressed for clarity. Likewise, as in Fig.~\ref{fig:Mr20triangle},
+  $\log (M_0)$ is extremely poorly constrained by the data and we omit it for 
+  clarity. Likewise, as in Fig.~\ref{fig:Mr20triangle},
   $\sigma_{\log M}$ and $\log (M_{\rm min})$ share a narrow
@@
 assembly bias. The bands in purple rein in the region of HODs for models within 
-$\Delta chi^2 \le 5.89$ of the best-fit model. 
+$\Delta \chi^2 \le 5.89$ of the best-fit model. 
 This is an explicit example of the degree to which the inferred relationship
@@
 %
-\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
+\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}$.
 %
@@
 \item The evidence for galaxy assembly bias weakens for brighter galaxy samples: 
-Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cen}=0$ and $A_{\rm sats}=0.$ 
+Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cen}=0$ and $A_{\rm sat}=0.$ 
 This is consistent with the well-established result that

### 2016-06-23 ms.tex
Added citation to MJ's work in progress and an acknowledgment for emcee and corner.

@@
 in agreement with \citet{lehmann_etal15}, we find that several samples
-{\em favor galaxy assembly bias to a degree that is statistically
-  significant}. As demonstrated by \citet{zentner_etal14}, this
-conclusion has important consequences for the interpretation of
-both extant and forthcoming data.
+{\em favor galaxy assembly bias to a degree that is statistically significant}. 
+As we were completing this work, we became aware of an independent study 
+using similar techniques and reaching broadly similar conclusions \citep{vakili_etal16}. 
+As demonstrated by \citet{zentner_etal14}, the assembly bias suggested by the 
+clustering of these samples has important consequences for the interpretation of
+both extant and forthcoming data as well as predictions for independent statistics 
+that make use of the HODs derived via clustering.
 
@@
 An example of the inferred posteriors for the HOD parameters is shown in 
-Figure~\ref{fig:Mr20triangle} for the sample with $\magr < -20$. We do 
+Figure~\ref{fig:Mr20triangle} for the sample with $\magr < -20$. Figure~\ref{fig:Mr20triangle} and 
+all similar plots in this paper were made using a slightly modified version of the 
+{\tt corner} software package \citep{corner}. We do 
 not show the full posteriors for all five threshold samples in the interest of brevity.
@@
 Sinha for help installing and running the {\tt CorrFunc} package 
-as well as comments on an earlier draft of this manuscript. ARZ and 
-APH are grateful to Prince Rogers Nelson for inspiring our creativity. 
+as well as comments on an earlier draft of this manuscript. We are grateful to 
+Dan Foreman-Mackey and all contributors to the {\tt emcee} and 
+{\tt corner} software packages which helped to greatly expedite this 
+work. ARZ and APH are grateful to Prince Rogers Nelson for inspiring our creativity. 
 The authors gratefully acknowledge the Gauss Centre for Supercomputing
